### 2022-09-02 doc/protocol.Rmd
update protocol to generate nice PDF for OSF submission

---
title: "Towards open collaboration in biomedical and health research: A scoping review"
shorttitle: "Scoping review of open collaboration"
date: "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"
author: 
  - name: Luke W. Johnston
    affiliation: 1
  - name: Daniel Ibsen
    affiliation: 1
  - name: Hannah Chatwin
    affiliation: 1
  - name: Mario Garcia
    affiliation: 1
affiliation:
  - id: 1
    institution: Steno Diabetes Center Aarhus, Denmark
  - id: 2
    institution: 
output: prereg::prereg_pdf
---

<!--TODO: Include badge link to OSF-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(stringr)
library(here)
source(here("R/search-terms.R"))
search_terms_inline <- str_replace_all(search_terms$general, "\\*", "\\\\\\*")
```

# Study information

## Title

`r rmarkdown::metadata$title`

## Description

Since scientific research now almost always requires working with other
people. With the increasing emphasis on and demand for science to be
more open, how we collaborate together is a key component to making
science more easily open from the start of any project. But how do we
collaborate in an open and transparent way? What are the best practices
and tools we can use? What is an ideal collaborative workflow and how
close or far are we from this ideal in reality? This project aims to
address some of these questions.

From our work in the health research field, we have experienced many
different ways of collaborating, but rarely in the form of open
collaboration. With the growing complexity and specialization in
scientific practices and methods, together with globalisation of health
and environmental issues, there is a great need for a paradigm shift in
research collaboration to be able to tackle these challenges.

We define open collaboration using the definition as found in Forte and
Lampe (2013):

> "*an online environment that (a) supports the collective production of
> an artifact (b) through a technologically mediated collaboration
> platform (c) that presents a low barrier to entry and exit and (d)
> supports the emergence of persistent but malleable social
> structures.*" This scoping review will focus on current practices of
> open collaboration and open science in relation to collaboration in
> the field of biomedical and health research.

## Hypotheses

This is a scoping review and does not have explicit hypotheses. Our
overarching aim of this scoping review is to identify current practices
of open collaboration in biomedical and health research.

The specific aims of this scoping review are to:

-   Provide an overview of current practices of or opinions about
    research collaboration that follow basic open principles (e.g.,
    transparency, accessibility)

-   Summarize existing online tools and resources available to improve
    open collaboration in research

# Design plan

## Study type

Scoping review on the literature around open collaboration.

## Blinding

No blinding is involved in this study, since this is a scoping review of
existing literature.

## Study design

This is a scoping review, so we are following the framework described by
Arksey and O'Malley
([DOI:10.1080/1364557032000119616](https://doi.org/10.1080/1364557032000119616))
and by Levac, Colquhoun, and O'Brien
([DOI:10.1186/1748-5908-5-69](https://doi.org/10.1186/1748-5908-5-69))
as well as the guidelines outlined in the PRISMA-ScR
([DOI:10.7326/M18-0850](https://doi.org/10.7326/M18-0850) statement.

# Sampling Plan

## Existing data

**Registration prior to creation of data**. As of the date of submission
of this research plan for preregistration, the data have not yet been
collected, created, or realized.

## Data collection procedures

We developed the initial search strategy in consultation with a research
librarian. We will collect the data via systematic searches of
databases, as well as some hand searches.

### Document selection

-   **Document types**:

    -   Open access journal articles published in peer-reviewed and
        non-peer-reviewed journals.
    -   Websites, blogs, and other online resources.
    -   Books

-   **Information sources and search terms**: We will use these
    information sources and databases:

    -   Formal publication repositories: SCOPUS, Web of Science, MEDLINE
        (via PubMed), and EMBASE
    -   Preprint repositories: medRxiv, bioRxiv, and arXiv
    -   Other dissemination repositories: Zenodo and figshare
    -   Reference lists from extracted articles

-   **Search terms**: Each repository has some small differences in how
    to use their search terms, but in general, the search term we will
    use looks like:

    > `r search_terms_inline`

-   **Inclusion criteria**: This includes any document where open
    collaboration practices are not the primary focus. We will be guided
    by the definition of open collaboration from Forte and Lampe (2013)
    mentioned above in determining whether the records are relevant.

    -   Any published document with reporting on current open
        collaboration practices.
    -   Any published document with advice, guidance, tools, and/or
        recommendations for improving open collaboration.
    -   Article language in English.

-   **Exclusion criteria**:

    -   Documents that do not report on specific open collaboration
        practices.

    -   5 years in the past, until approximately 2017-01-01, to capture
        current/most recent practices.

### Software and tools used

We will use R to search and retrieve results from the databases using
the following packages:

-   [easyPubMed](https://cran.r-project.org/web/packages/easyPubMed/vignettes/getting_started_with_easyPubMed.html)
    package for searching and retrieving from MEDLINE via PubMed.
-   [wosr](https://github.com/vt-arc/wosr) package for searching and
    retrieving from Web of Science.
-   [rscopus](https://github.com/muschellij2/rscopus) package for
    searching and retrieving from Scopus and EMBASE.
-   [medrxivr](https://github.com/ropensci/medrxivr) and
    [aRxiv](https://docs.ropensci.org/aRxiv/) packages for searching and
    retrieving from preprint repositories.
-   [zen4R](https://github.com/eblondel/zen4R) and
    [rfigshare](https://cran.r-project.org/web/packages/rfigshare/) for
    searching and retrieving from Zenodo and figshare.

## Sample size

We aim to identify at least 1000 articles in the initial first
literature extraction.

## Sample size rationale

The sample size is based on our available time and resources to work on
this project.

## Stopping rule

In terms of database searches, we aim to limit the search until the end
date (maximum 2022-11-31). Searches will be concluded when we reach
conceptual saturation (i.e., when it is determined that we are not
identifying any new concepts/resources). Depending on the quantity of
records retrieved, even after further filtering, we may randomly select
a large enough sample that each person can go through and manually
review them. In the interests of feasibility, a maximum for 4 books will
be selected and evaluated. Books will be selected based on a consensus
in the research group.

# Variables

## Measured variables

The primary "variables" of interest will be the article title, abstract,
topic list, and full length article. In addition to these variables, we
will also obtain article metadata, such as publication date, URL/DOI,
and author list.

# Analysis Plan

## Statistical models

Since this is a scoping review, the purpose is to explore a research
topic and we will not be conducting any statistical modeling.

All data obtained from all searches in online databases will be exported
into text files or CVS files for further processing including removal of
duplicates.

At least two of us will extract data using a standardized and tested
template. Data regarding the data source (e.g., author, title,
publication year), open collaboration practices, and any other relevant
information, will be extracted. Extracted data will be summarized with
the descriptive analytical method described by Arksey and O'Malley
(2005). The descriptive analytical method is aimed at identifying and
summarizing different open collaboration practices.

Results will be presented in a descriptive way and general topics that
we extract from the sources will be subjectively grouped into common
themes. We will not do any formal analyses aside from descriptively
listing the perspectives or practices for doing open collaborative
research.

# Other

## Anticipated duration

| Phase                               | Start      | End        |
|-------------------------------------|------------|------------|
| Overall                             | 2022-01-01 | 2023-12-31 |
| Research design and data collection | 2022-01-01 | 2022-11-31 |
| Screening resources                 | 2022-12-01 | 2023-06-01 |
| Analyses and manuscript writing     | 2023-06-01 | 2023-12-31 |

: Estimated timeline for project.

# References

##

```{=tex}
\vspace{-2pc}
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{-1in}
\setlength{\parskip}{8pt}
```
\noindent

### 2022-09-02 R/search-terms.R
add search terms as an R variable

@@ -1,0 +1,4 @@
+search_terms <- list(
+    general = "(open) AND (science OR research) AND (collaborat* OR team OR cooperat*) AND (technolog* OR tool OR framework OR guideline OR principles OR practices OR systems OR resources)",
+    pubmed = "(open[Title]) AND (science OR research) AND (collaborat* OR team OR cooperat*) AND (technolog* OR tool OR framework OR guideline OR principles OR practices OR systems OR resources) AND (y_5[Filter])"
+)

### 2022-09-02 doc/protocol.Rmd
my affiliations

@@
   - name: Luke W. Johnston
-    affiliation: 1
+    affiliation: "1,2"
   - name: Daniel Ibsen
@@
   - id: 2
-    institution: 
+    institution: Aarhus University, Denmark
 output: prereg::prereg_pdf

### 2022-09-02 doc/protocol.Rmd
Added institutional info and checked the protocol

--- 2022-09-02 doc/protocol.Rmd
@@
   - name: Mario Garcia
-    affiliation: 1
+    affiliation: 3
 affiliation:
@@
   - id: 2
-    institution: 
+    institution: Aarhus University, Denmark
+   - id: 3
+    institution: Copenhagen University, Denmark
 output: prereg::prereg_pdf

### 2022-09-05 doc/protocol.Rmd
Review protocol

--- 2022-09-02 doc/protocol.Rmd
@@
   - name: Hannah Chatwin
-    affiliation: 1
+    affiliation: 2
   - name: Mario Garcia
-    affiliation: 1
+    affiliation: 3
 affiliation:
@@
 
-Since scientific research now almost always requires working with other
+Scientific research now almost always requires working with other
 people. With the increasing emphasis on and demand for science to be
 more open, how we collaborate together is a key component to making
-science more easily open from the start of any project. But how do we
+science more open from the start of any project. But how do we
 collaborate in an open and transparent way? What are the best practices
@@
 
-Scoping review on the literature around open collaboration.
+Scoping review on literature relating to open collaboration.
 
@@
 
-    -   5 years in the past, until approximately 2017-01-01, to capture
+    -   Documents published >5 years in the past (defined as before 2017-01-01) to capture
         current/most recent practices.
@@
 
-We aim to identify at least 1000 articles in the initial first
-literature extraction.
+We aim to identify at least 1000 articles in the initial database search.
 
@@
 records retrieved, even after further filtering, we may randomly select
-a large enough sample that each person can go through and manually
+a sample that each person can go through and manually
 review them. In the interests of feasibility, a maximum for 4 books will
-be selected and evaluated. Books will be selected based on a consensus
+be selected and evaluated. Books will be selected based on consensus
 in the research group.
@@
 The primary "variables" of interest will be the article title, abstract,
-topic list, and full length article. In addition to these variables, we
+topic list, and full length article including content relating to open collaboration. In addition to these variables, we
 will also obtain article metadata, such as publication date, URL/DOI,

### 2022-10-07 doc/protocol.Rmd
alphabetical author listing

@@
 author: 
-  - name: Luke W. Johnston
-    affiliation: "1,2"
-  - name: Daniel Ibsen
-    affiliation: 1
   - name: Hannah Chatwin
@@
     affiliation: 3
+  - name: Daniel Ibsen
+    affiliation: 1
+  - name: Luke W. Johnston
+    affiliation: "1,2"
 affiliation:

### 2022-10-07 R/pubmed-search.R
minor edits

@@ -1,5 +1,4 @@
 # Pubmed search using easypubmed
-# last search was: 19/08/2022
 
 # Load libraries ----------------------------------------------------------------
 
@@ -48,9 +47,10 @@ pubmed_df <- pubmed_df %>%
 
 # Count number of papers -------------------------------------------------------
 
-nrow(open_collaboration_pubmed_df) #7339 papers identified
+# 7339 papers identified
+# Note: same search on pubmed gave 10.439 papers
+# nrow(open_collaboration_pubmed_df)
 
-#Note: same search on pubmed gave 10.439 papers
 
 # Save dataset -----------------------------------------------------------------
 

### 2022-10-07 R/extraction-zenodo.R
updated script to run extraction of zenodo

@@ -1,18 +1,22 @@
+# Zenodo extraction script
+
+# Load packages -----------------------------------------------------------
+
 library(zen4R)
 library(lubridate)
 library(glue)
 library(stringr)
+library(here)
+library(tibble)
+library(purrr)
+source(here("R/search-terms.R"))
+
+# Create Zenodo-specific search term --------------------------------------
 
 # For some reason Zenodo doesn't accept this publication_date query in the API
-five_years_past <- glue("publication_date:[{today()-years(5)} TO {today()}]")
+five_years_past <- glue("publication_date:[{today()-years(5)}TO{today()}]")
 
-topic_search_terms <- "
-    (open) AND
-    (science OR research) AND
-    (collaborat* OR team OR cooperat*) AND
-    (technolog* OR tool OR framework OR guideline OR principles OR practices OR systems OR resources)
-"
-
+# Zenodo specific limiters
 limiters <- "
     (access_right:open) AND
     (
@@ -24,17 +28,53 @@ limiters <- "
     )
 "
 
-search_term <- glue("{limiters} AND {topic_search_terms}") %>%
+# Structured search term to fit Zenodo requirements
+search_term <- glue("{search_terms$zenodo} AND {limiters}") %>%
     str_remove_all("\\n+") %>%
     str_squish() %>%
     str_remove_all("OR ")
 
+# Connect to Zenodo and run search ----------------------------------------
+
 # Requires token (PAT) from Zenodo to work
 zenodo <- ZenodoManager$new(
     url = "https://zenodo.org/api",
-    logger = "INFO",
+    logger = "DEBUG",
     token = askpass::askpass()
 )
 
-test <- zenodo$getRecords(q = search_term, size = 1000)
-test
+# zenodo$getCommunities()
+zenodo_records <- zenodo$getRecords(q = search_term, size = 1000)
+
+# Number of extracted items
+# length(zenodo_records)
+# zenodo_records[[1]]$exportAsJSON()
+
+# Process extracted Zenodo records ----------------------------------------
+
+extract_relevant_data <- function(record_list) {
+    creators <- record_list$metadata$creators %>%
+        map_chr( ~ .x$name) %>%
+        str_flatten(" and ") %>%
+        str_trim()
+
+    keywords <- record_list$metadata$keywords %>%
+        str_flatten("; ") %>%
+        str_trim()
+
+    list(
+        creators = creators,
+        title = record_list$metadata$title,
+        description = record_list$metadata$description,
[…]

### 2022-10-07 R/search-terms.R

@@ -1,4 +1,5 @@
 search_terms <- list(
     general = "(open) AND (science OR research) AND (collaborat* OR team OR cooperat*) AND (technolog* OR tool OR framework OR guideline OR principles OR practices OR systems OR resources)",
-    pubmed = "(open[Title]) AND (science OR research) AND (collaborat* OR team OR cooperat*) AND (technolog* OR tool OR framework OR guideline OR principles OR practices OR systems OR resources) AND (y_5[Filter])"
+    pubmed = "(open[Title]) AND (science OR research) AND (collaborat* OR team OR cooperat*) AND (technolog* OR tool OR framework OR guideline OR principles OR practices OR systems OR resources) AND (y_5[Filter])",
+    zenodo = "(title:open) AND (science OR research) AND (collaborat* OR team OR cooperat*) AND (technolog* OR tool OR framework OR guideline OR principles OR practices OR systems OR resources)"
 )

### 2022-11-03 R/pubmed-search.R
Updated pubmed search

@@ -1,6 +1,6 @@
 # Pubmed search using easypubmed
 
-# Load libraries ----------------------------------------------------------------
+# Load libraries ---------------------------------------------------------------
 
 library(easyPubMed)
 library(tidyverse)
@@ -9,7 +9,11 @@ library(purrr)
 library(readr)
 source(here("R/search-terms.R"))
 
-# Search pubmed using the easyPubMed package ------------------------------------
+# Search last updated ----------------------------------------------------------
+
+Sys.Date() #2022-11-03
+
+# Search pubmed using the easyPubMed package -----------------------------------
 
 ## making a list with the search terms
 
@@ -41,16 +45,19 @@ open_collaboration_pubmed_df <-
 
 # Cleaning dataset -------------------------------------------------------------
 
-pubmed_df <- pubmed_df %>%
+pubmed_df <- open_collaboration_pubmed_df %>%
     select(lastname, year, title, abstract, jabbrv, email, pmid) %>%
     mutate(database = "pubmed")
 
 # Count number of papers -------------------------------------------------------
 
-# 7339 papers identified
-# Note: same search on pubmed gave 10.439 papers
-# nrow(open_collaboration_pubmed_df)
+# 756 papers identified when copying the search on pubmed
 
+n_papers_web <- 756
+n_papers_r <-  as.numeric(nrow(pubmed_df))
+
+search_the_same <- n_papers_web == n_papers_r
+search_the_same
 
 # Save dataset -----------------------------------------------------------------
 

### 2022-11-03 doc/protocol.Rmd
added initial files for searches

@@
     institution: Copenhagen University, Denmark
-output: prereg::prereg_pdf
+output: 
+    prereg::prereg_pdf: default
+    md_document: default
 ---
@@
 `r rmarkdown::metadata$title`
+
+**Registration link:** <https://doi.org/10.17605/OSF.IO/K9DR5>
 
@@
 
-    -   Documents published >5 years in the past (defined as before 2017-01-01) to capture
-        current/most recent practices.
+    -   Documents published \>5 years in the past (defined as before
+        2017-01-01) to capture current/most recent practices.
 
@@
 
-We aim to identify at least 1000 articles in the initial database search.
+We aim to identify at least 1000 articles in the initial database
+search.
 
@@
 records retrieved, even after further filtering, we may randomly select
-a sample that each person can go through and manually
-review them. In the interests of feasibility, a maximum for 4 books will
-be selected and evaluated. Books will be selected based on consensus
-in the research group.
+a sample that each person can go through and manually review them. In
+the interests of feasibility, a maximum for 4 books will be selected and
+evaluated. Books will be selected based on consensus in the research
+group.
 
@@
 The primary "variables" of interest will be the article title, abstract,
-topic list, and full length article including content relating to open collaboration. In addition to these variables, we
-will also obtain article metadata, such as publication date, URL/DOI,
-and author list.
+topic list, and full length article including content relating to open
+collaboration. In addition to these variables, we will also obtain
+article metadata, such as publication date, URL/DOI, and author list.
 

### 2022-11-03 R/arxiv-search.R

@@ -1,0 +1,17 @@
+#arxiv search using aRxiv
+
+#Link: https://docs.ropensci.org/aRxiv/articles/aRxiv.html
+
+# Load libraries ---------------------------------------------------------------
+
+library(aRxiv)
+
+source(here("R/search-terms.R"))
+
+# Running search -----------------------------------------------------------------------
+
+#just a test but there are 3 interesting papers
+ax_search <- arxiv_search('ti:"open collaboration"')
+
+
+

### 2022-11-03 R/medrxiv-search.R

@@ -1,0 +1,19 @@
+# medRxiv search using medrxivr
+
+#Link: https://github.com/ropensci/medrxivr
+
+# Load libraries ---------------------------------------------------------------
+
+library(medrxivr)
+
+source(here("R/search-terms.R"))
+
+# Running search ---------------------------------------------------------------
+
+medrxiv_data <- mx_snapshot()
+
+medrxiv_search <- mx_search(data = medrxiv_data,
+                     query = search_terms$medrxiv,
+                     from_date = "2017-01-01",
+                     to_date = "2022-11-03",
+                     auto_caps = TRUE)

### 2022-11-03 R/pubmed-search.R

@@ -1,5 +1,7 @@
 # Pubmed search using easypubmed
 
+#Link: https://cran.r-project.org/web/packages/easyPubMed/vignettes/getting_started_with_easyPubMed.html
+
 # Load libraries ---------------------------------------------------------------
 
 library(easyPubMed)

### 2022-11-03 R/search-terms.R

@@ -1,4 +1,6 @@
 search_terms <- list(
     general = "(open) AND (science OR research) AND (collaborat* OR team OR cooperat*) AND (technolog* OR tool OR framework OR guideline OR principles OR practices OR systems OR resources)",
-    pubmed = "(open[Title]) AND (science OR research) AND (collaborat* OR team OR cooperat*) AND (technolog* OR tool OR framework OR guideline OR principles OR practices OR systems OR resources) AND (y_5[Filter])"
+    pubmed = "(open[Title]) AND (science OR research) AND (collaborat* OR team OR cooperat*) AND (technolog* OR tool OR framework OR guideline OR principles OR practices OR systems OR resources) AND (y_5[Filter])",
+    wos = "(TI=(open)) AND ((ALL=(science)) OR ALL=(research)) AND (((ALL=(collaborat*)) OR ALL=(team)) OR ALL=(cooperat*)) AND ((((((((ALL=(technolog*)) OR ALL=(tool)) OR ALL=(framework)) OR ALL=(guideline)) OR ALL=(principles)) OR ALL=(practices)) OR ALL=(systems)) OR ALL=(resources))",
+    medrxiv = "open collaboration"
 )

### 2022-11-03 R/wos-search.R

@@ -1,0 +1,29 @@
+# Web of Science search using wosr
+
+# Load libraries ---------------------------------------------------------------
+
+library(wosr)
+
+source(here("R/search-terms.R")) #forgot to add the 5-year restriction!!
+
+# Input username and password --------------------------------------------------
+
+#<NOT SURE HOW WE WILL DO THIS, I USUALLY ACCESS THROUGH AU LIBRARY>
+
+Sys.setenv(WOS_USERNAME = "your_username", WOS_PASSWORD = "your_password")
+
+# Get session ID
+sid <- auth()
+
+# Running the search -----------------------------------------------------------
+
+## Seeing how many results
+query_wos(search_terms$wos, sid = sid)
+#tested the search on the web and identified 7780 records
+
+## extracting data from the search
+wos_search <- pull_wos(search_terms$wos, sid = sid)
+
+# Data wrangling ---------------------------------------------------------------
+
+

### 2022-11-04 R/extraction-zenodo.R
move code over

@@ -1,80 +1,0 @@
-# Zenodo extraction script
-
-# Load packages -----------------------------------------------------------
-
-library(zen4R)
-library(lubridate)
-library(glue)
-library(stringr)
-library(here)
-library(tibble)
-library(purrr)
-source(here("R/search-terms.R"))
-
-# Create Zenodo-specific search term --------------------------------------
-
-# For some reason Zenodo doesn't accept this publication_date query in the API
-five_years_past <- glue("publication_date:[{today()-years(5)}TO{today()}]")
-
-# Zenodo specific limiters
-limiters <- "
-    (access_right:open) AND
-    (
-        resource_type.type:publication
-        resource_type.type:poster
-        resource_type.type:presentation
-        resource_type.type:lesson
-        resource_type.type:other
-    )
-"
-
-# Structured search term to fit Zenodo requirements
-search_term <- glue("{search_terms$zenodo} AND {limiters}") %>%
-    str_remove_all("\\n+") %>%
-    str_squish() %>%
-    str_remove_all("OR ")
-
-# Connect to Zenodo and run search ----------------------------------------
-
-# Requires token (PAT) from Zenodo to work
-zenodo <- ZenodoManager$new(
-    url = "https://zenodo.org/api",
-    logger = "DEBUG",
-    token = askpass::askpass()
-)
-
-# zenodo$getCommunities()
-zenodo_records <- zenodo$getRecords(q = search_term, size = 1000)
-
-# Number of extracted items
-# length(zenodo_records)
-# zenodo_records[[1]]$exportAsJSON()
-
-# Process extracted Zenodo records ----------------------------------------
-
-extract_relevant_data <- function(record_list) {
-    creators <- record_list$metadata$creators %>%
-        map_chr( ~ .x$name) %>%
-        str_flatten(" and ") %>%
-        str_trim()
-
-    keywords <- record_list$metadata$keywords %>%
-        str_flatten("; ") %>%
-        str_trim()
-
-    list(
-        creators = creators,
-        title = record_list$metadata$title,
-        description = record_list$metadata$description,
-        date = record_list$metadata$publication_date,
-        type = record_list$metadata$upload_type,
-        keywords = keywords,
-        doi = record_list$links$doi
-    )
-}
-
-zenodo_records_processed <- zenodo_records %>%
-    map(extract_relevant_data)
-
-# Save for use later processing
-yaml::write_yaml(zenodo_records_processed, file = here("data-raw/zenodo.yaml"))

### 2022-11-04 R/zenodo-search.R

@@ -1,20 +1,80 @@
-# Zenodo search using zen4R
+# Zenodo extraction script
 
-#Link: https://github.com/eblondel/zen4R/wiki
-
-# Load libraries ---------------------------------------------------------------
+# Load packages -----------------------------------------------------------
 
 library(zen4R)
-
+library(lubridate)
+library(glue)
+library(stringr)
+library(here)
+library(tibble)
+library(purrr)
 source(here("R/search-terms.R"))
 
-# Running search -----------------------------------------------------------------------
+# Create Zenodo-specific search term --------------------------------------
 
-## note that the token you use is private
+# For some reason Zenodo doesn't accept this publication_date query in the API
+five_years_past <- glue("publication_date:[{today()-years(5)}TO{today()}]")
 
+# Zenodo specific limiters
+limiters <- "
+    (access_right:open) AND
+    (
+        resource_type.type:publication
+        resource_type.type:poster
+        resource_type.type:presentation
+        resource_type.type:lesson
+        resource_type.type:other
+    )
+"
+
+# Structured search term to fit Zenodo requirements
+search_term <- glue("{search_terms$zenodo} AND {limiters}") %>%
+    str_remove_all("\\n+") %>%
+    str_squish() %>%
+    str_remove_all("OR ")
+
+# Connect to Zenodo and run search ----------------------------------------
+
+# Requires token (PAT) from Zenodo to work
 zenodo <- ZenodoManager$new(
-    token = "put token here",
-    logger = "INFO" # use "DEBUG" to see detailed API operation logs, use NULL if you don't want logs at all
+    url = "https://zenodo.org/api",
+    logger = "DEBUG",
+    token = askpass::askpass()
 )
 
-my_zenodo_records <- zenodo$getRecords(q = "title:(+open +collaboration) publication_date:(2017-01-01 TO 2022-11-02)")
+# zenodo$getCommunities()
+zenodo_records <- zenodo$getRecords(q = search_term, size = 1000)
+
+# Number of extracted items
+# length(zenodo_records)
+# zenodo_records[[1]]$exportAsJSON()
+
+# Process extracted Zenodo records ----------------------------------------
+
+extract_relevant_data <- function(record_list) {
+    creators <- record_list$metadata$creators %>%
+        map_chr( ~ .x$name) %>%
+        str_flatten(" and ") %>%
+        str_trim()
+
+    keywords <- record_list$metadata$keywords %>%
+        str_flatten("; ") %>%
+        str_trim()
+
[…]

### 2022-11-04 R/zenodo-search.R
add code to remove dates after 5 years ago

@@ -14,7 +14,8 @@ source(here("R/search-terms.R"))
 # Create Zenodo-specific search term --------------------------------------
 
 # For some reason Zenodo doesn't accept this publication_date query in the API
-five_years_past <- glue("publication_date:[{today()-years(5)}TO{today()}]")
+five_years_ago <- glue("{today()-years(5)}")
+five_years_to_today <- glue("publication_date:[{five_years_ago} TO {today()}]")
 
 # Zenodo specific limiters
 limiters <- "
@@ -47,8 +48,10 @@ zenodo <- ZenodoManager$new(
 zenodo_records <- zenodo$getRecords(q = search_term, size = 1000)
 
 # Number of extracted items
-# length(zenodo_records)
-# zenodo_records[[1]]$exportAsJSON()
+length(zenodo_records)
+
+# To export an individual entry as JSON, with all information retreived.
+# zenodo_records[[1]]$exportAsJSON(filename = here::here("data-raw/zenodo-entry-1"))
 
 # Process extracted Zenodo records ----------------------------------------
 
@@ -73,8 +76,13 @@ extract_relevant_data <- function(record_list) {
     )
 }
 
+# Extract necessary data and keep only last five years
 zenodo_records_processed <- zenodo_records %>%
-    map(extract_relevant_data)
+    map(extract_relevant_data) %>%
+    keep(~ ymd(as_date(.x$date)) >= five_years_ago)
+
+# There's less entries from the original
+length(zenodo_records_processed)
 
 # Save for use later processing
 yaml::write_yaml(zenodo_records_processed, file = here("data-raw/zenodo.yaml"))

### 2023-05-12 R/pubmed-search.R
finally updated pubmed functions and added to targets

@@ -1,15 +1,10 @@
-# Pubmed search using easypubmed
 
-library(easyPubMed)
-library(tidyverse)
-library(here)
-library(purrr)
-library(readr)
-library(xml2)
-source(here("R/search-terms.R"))
-
-## making a list with the search terms
-
+#' Get records from PubMed based on a search term.
+#'
+#' @param search_terms The full search terms to use, see `search_terms()`.
+#'
+#' @return List of PubMed records.
+#'
 pubmed_get_records <- function(search_terms) {
   article_ids <- easyPubMed::get_pubmed_ids(search_terms)
   articles <- easyPubMed::fetch_pubmed_data(article_ids,
@@ -19,20 +14,44 @@ pubmed_get_records <- function(search_terms) {
   articles %>%
     xml2::read_xml() %>%
     xml2::xml_find_all(".//Article") %>%
-    as_list()
+    xml2::as_list()
 }
 
+#' Extract specific data from an individual PubMed Record.
+#'
+#' Use in combination with `purrr::map()`. See `pubmed_retrieve_records()`.
+#'
+#' @param record_list Individual record list.
+#'
+#' @return List with DOI, date, and article title.
+#'
 pubmed_extract_relevant_data <- function(record_list) {
   metadata <- record_list %>%
-    purrr::keep_at(c("ArticleTitle", "ArticleDate", "ELocationID"))
-  date <- paste(
+    purrr::keep_at(c("ArticleTitle", "ArticleDate", "ELocationID", "Journal"))
+  article_date <- paste(
     metadata$ArticleDate$Year,
     metadata$ArticleDate$Month,
     metadata$ArticleDate$Day,
     sep = "-"
   )
 
-  date <- ifelse(!rlang::is_empty(date), date, NA_character_)
+  pub_date <- metadata$Journal$JournalIssue$PubDate
+  pub_date <- paste(
+    pub_date$Year,
+    pub_date$Month,
+    if (!is.null(pub_date$Day)) pub_date$Day[[1]] else "01",
+    sep = "-"
+  )
+
+  # Keep either publication date or article date, sometimes there is one but not
+  # the other
+  date <- suppressWarnings(c(pub_date, article_date) %>%
+    lubridate::as_date() %>%
+    na.omit() %>%
+    head(1))
+
+  # Set any dates that don't exist to NA.
+  date <- if (length(article_date)) article_date else NA
 
   list(
     doi = unlist(metadata$ELocationID),
[…]

### 2023-05-12 _targets.R

@@ -46,4 +46,17 @@ list(
     format = "file"
   ),
   # PubMed ------------------------------------------------------------------
+  tar_target(
+    name = pubmed_search_terms,
+    command = search_terms("pubmed")
+  ),
+  tar_target(
+    name = pubmed_records,
+    command = pubmed_retrieve_records(pubmed_search_terms)
+  ),
+  tar_target(
+    name = data_raw_pubmed,
+    command = save_list_as_yaml(pubmed_records, here::here("data-raw/pubmed.yaml")),
+    format = "file"
+  )
 )

### 2023-05-12 R/zenodo-search.R
commented out this to speed up function

@@ -56,10 +56,11 @@ zenodo_get_records <- function(search_terms) {
 #' @return A list of records.
 #'
 zenodo_extract_relevant_data <- function(record_list) {
-  creators <- record_list$metadata$creators %>%
-    purrr::map_chr(~ .x$name) %>%
-    stringr::str_flatten(" and ") %>%
-    stringr::str_trim()
+  # For now don't need.
+  # creators <- record_list$metadata$creators %>%
+  #   purrr::map_chr(~ .x$name) %>%
+  #   stringr::str_flatten(" and ") %>%
+  #   stringr::str_trim()
 
   keywords <- record_list$metadata$keywords %>%
     stringr::str_flatten("; ") %>%

### 2023-05-12 R/search-terms.R
try to minimize wildcards, since they slow things down a bit.

@@ -7,10 +7,11 @@
 #' @examples
 #' search_terms("pubmed")
 search_terms <- function(engine) {
+  # Avoid using wildcards in terms, since they slow things down when sending a query
   switch(engine,
     general = "(open) AND (science OR research) AND (collaborat* OR team OR cooperat*) AND (technolog* OR tool OR framework OR guideline OR principles OR practices OR systems OR resources)",
-    pubmed = "(open[Title]) AND (science OR research) AND (collaborat* OR team OR cooperat*) AND (technolog* OR tool OR framework OR guideline OR principles OR practices OR systems OR resources) AND (y_5[Filter])",
-    zenodo = "(title:open) AND (science OR research) AND (collaborat* OR team OR cooperat*) AND (technolog* OR tool OR framework OR guideline OR principles OR practices OR systems OR resources)",
+    pubmed = "(open[Title]) AND (science OR research) AND (collaborate OR collaboration OR collaborating OR team OR cooperate OR cooperation OR cooperating) AND (technology OR technologies OR tool OR framework OR guideline OR principles OR practices OR systems OR resources) AND (y_5[Filter])",
+    zenodo = "(title:open) AND (science OR research) AND (collaborate OR collaboration OR collaborating OR team OR cooperate OR cooperation OR cooperating) AND (technology OR technologies OR tool OR framework OR guideline OR principles OR practices OR systems OR resources)",
     wos = "(TI=(open)) AND ((ALL=(science)) OR ALL=(research)) AND (((ALL=(collaborat*)) OR ALL=(team)) OR ALL=(cooperat*)) AND ((((((((ALL=(technolog*)) OR ALL=(tool)) OR ALL=(framework)) OR ALL=(guideline)) OR ALL=(principles)) OR ALL=(practices)) OR ALL=(systems)) OR ALL=(resources))",
     # For some reason, arxiv doesn't like the * wildcard...
     arxiv = 'ti:"open" AND (research OR science) AND (collaborate OR collaborating OR collaboration OR team OR cooperate OR cooperating OR cooperation) AND (technology OR technologies OR tool OR framework OR guideline OR principles OR practices OR systems OR resources)',

### 2023-05-12 R/search-terms.R
Updated arxiv search tesms

@@ -13,7 +13,7 @@ search_terms <- function(engine) {
     zenodo = "(title:open) AND (science OR research) AND (collaborat* OR team OR cooperat*) AND (technolog* OR tool OR framework OR guideline OR principles OR practices OR systems OR resources)",
     wos = "(TI=(open)) AND ((ALL=(science)) OR ALL=(research)) AND (((ALL=(collaborat*)) OR ALL=(team)) OR ALL=(cooperat*)) AND ((((((((ALL=(technolog*)) OR ALL=(tool)) OR ALL=(framework)) OR ALL=(guideline)) OR ALL=(principles)) OR ALL=(practices)) OR ALL=(systems)) OR ALL=(resources))",
     # For some reason, arxiv doesn't like the * wildcard... #Daniel: okay not to include. We will just state why here.
-    arxiv = 'ti:"open" AND (research OR science) AND (collaborate OR collaborating OR collaboration OR team OR cooperate OR cooperating OR cooperation) AND (technology OR technologies OR tool OR framework OR guideline OR principles OR practices OR systems OR resources)',
+    arxiv = '(ti:open) AND (all:science OR all:research) OR (all:collaborate OR all:collaborating OR all:collaboration OR all:team OR all:cooperate OR all:cooperating OR all:cooperation) AND (all:technology OR all:technologies OR all:tool OR all:framework OR all:guideline OR all:principles OR all:practices OR all:systems OR all:resources)'
     #Trying code for arxiv also for medrxiv. Assuming they have the same engine
     medrxiv ='ti:"open" AND (research OR science) AND (collaborate OR collaborating OR collaboration OR team OR cooperate OR cooperating OR cooperation) AND (technology OR technologies OR tool OR framework OR guideline OR principles OR practices OR systems OR resources)'
   )

### 2023-05-12 R/medrxiv-search.R
Update medrxiv-search.R

@@ -6,16 +6,33 @@
 
 library(medrxivr)
 library(here)
-
 source(here("R/search-terms.R"))
 
 # Running search ---------------------------------------------------------------
 
-medrxiv_data <- mx_snapshot() #It says in the documentation that the snapshot is from here: https://github.com/mcguinlu/medrxivr-data
-                              #however, it does not look like the it has been updated in 9 months.
+medrxiv_data <- mx_api_content(server = "medrxiv") #with this function we get the latest data! It takes a while, though
 
 medrxiv_search <- mx_search(data = medrxiv_data,
                             query = search_terms("medrxiv"),
-                     from_date = "2017-01-01",
-                     to_date = "2022-11-03", #should this be updated?
-                     auto_caps = TRUE)
+                            #query = list(c("open"), c("science", "research"), c("collaborate","collaborating", "collaboration", "team", "cooperate", "cooperating"), c("technology", "technologies", "tool","framework", "guideline", "principles", "practices", "systems","resources")),
+                            from_date = "2017-01-01",
+                            to_date = "2022-11-03", #should this be updated?
+                            auto_caps = TRUE,
+                            report = TRUE)
+
+#Let's try to get to obtain only those that have open in the title to meet the criteria of the searches for other tools:
+
+medrxiv_search_open_ti <- medrxiv_search[which(stringr::str_detect(string = medrxiv_search$title, pattern = "open") == TRUE |
+                                                 stringr::str_detect(string = medrxiv_search$title, pattern = "Open") == TRUE),] #only 6/37
+
+#Let's now save the data in the same format as arxiv data:
+
+medrxiv_results <- medrxiv_search_open_ti %>% 
+  select(id=ID, date, title, authors, link_abstract=link_page, link_pdf)
+
+#Finally, let's save the data:
+
+write_csv(
+  medrxiv_results,
+  file = here("data-raw/medrxiv-search.csv")
+)

### 2023-05-12 R/medrxiv-search.R
Update medrxiv-search.R

@@ -6,6 +6,7 @@
 
 library(medrxivr)
 library(here)
+library(tidyverse)
 source(here("R/search-terms.R"))
 
 # Running search ---------------------------------------------------------------

### 2023-05-12 R/search-terms.R
Changes to medrxiv

@@ -15,6 +15,6 @@ search_terms <- function(engine) {
     # For some reason, arxiv doesn't like the * wildcard... #Daniel: okay not to include. We will just state why here.
     arxiv = '(ti:open) AND (all:science OR all:research) OR (all:collaborate OR all:collaborating OR all:collaboration OR all:team OR all:cooperate OR all:cooperating OR all:cooperation) AND (all:technology OR all:technologies OR all:tool OR all:framework OR all:guideline OR all:principles OR all:practices OR all:systems OR all:resources)'
     #Trying code for arxiv also for medrxiv. Assuming they have the same engine
-    medrxiv ='ti:"open" AND (research OR science) AND (collaborate OR collaborating OR collaboration OR team OR cooperate OR cooperating OR cooperation) AND (technology OR technologies OR tool OR framework OR guideline OR principles OR practices OR systems OR resources)'
+    medrxiv = list(c("open"), c("science", "research"), c("collaborate","collaborating", "collaboration", "team", "cooperate", "cooperating"), c("technology", "technologies", "tool","framework", "guideline", "principles", "practices", "systems","resources"))
   )
 }

### 2023-05-12 R/search-terms.R
Changes to medrxiv

@@ -14,7 +14,7 @@ search_terms <- function(engine) {
     wos = "(TI=(open)) AND ((ALL=(science)) OR ALL=(research)) AND (((ALL=(collaborat*)) OR ALL=(team)) OR ALL=(cooperat*)) AND ((((((((ALL=(technolog*)) OR ALL=(tool)) OR ALL=(framework)) OR ALL=(guideline)) OR ALL=(principles)) OR ALL=(practices)) OR ALL=(systems)) OR ALL=(resources))",
     # For some reason, arxiv doesn't like the * wildcard... #Daniel: okay not to include. We will just state why here.
     arxiv = '(ti:open) AND (all:science OR all:research) OR (all:collaborate OR all:collaborating OR all:collaboration OR all:team OR all:cooperate OR all:cooperating OR all:cooperation) AND (all:technology OR all:technologies OR all:tool OR all:framework OR all:guideline OR all:principles OR all:practices OR all:systems OR all:resources)'
-    #Trying code for arxiv also for medrxiv. Assuming they have the same engine
+    #Changing according to the new tutorial: https://docs.ropensci.org/medrxivr/articles/medrxivr.html
     medrxiv = list(c("open"), c("science", "research"), c("collaborate","collaborating", "collaboration", "team", "cooperate", "cooperating"), c("technology", "technologies", "tool","framework", "guideline", "principles", "practices", "systems","resources"))
   )
 }

### 2023-05-12 R/search-terms.R
small edits and comments

@@ -11,11 +11,12 @@ search_terms <- function(engine) {
   switch(engine,
     general = "(open) AND (science OR research) AND (collaborat* OR team OR cooperat*) AND (technolog* OR tool OR framework OR guideline OR principles OR practices OR systems OR resources)",
     pubmed = "(open[Title]) AND (science OR research) AND (collaborate OR collaboration OR collaborating OR team OR cooperate OR cooperation OR cooperating) AND (technology OR technologies OR tool OR framework OR guideline OR principles OR practices OR systems OR resources) AND (y_5[Filter])",
+    # Doesn't like the wildcard...
     zenodo = "(title:open) AND (science OR research) AND (collaborate OR collaboration OR collaborating OR team OR cooperate OR cooperation OR cooperating) AND (technology OR technologies OR tool OR framework OR guideline OR principles OR practices OR systems OR resources)",
     wos = "(TI=(open)) AND ((ALL=(science)) OR ALL=(research)) AND (((ALL=(collaborat*)) OR ALL=(team)) OR ALL=(cooperat*)) AND ((((((((ALL=(technolog*)) OR ALL=(tool)) OR ALL=(framework)) OR ALL=(guideline)) OR ALL=(principles)) OR ALL=(practices)) OR ALL=(systems)) OR ALL=(resources))",
-    # For some reason, arxiv doesn't like the * wildcard...
+    # For some reason, arXiv doesn't like the * wildcard...
     arxiv = 'ti:"open" AND (research OR science) AND (collaborate OR collaborating OR collaboration OR team OR cooperate OR cooperating OR cooperation) AND (technology OR technologies OR tool OR framework OR guideline OR principles OR practices OR systems OR resources)',
-    #Trying code for arxiv also for medrxiv. Assuming they have the same engine
+    # Trying code for arxiv also for medrxiv. Assuming they have the same engine
     medrxiv ='ti:"open" AND (research OR science) AND (collaborate OR collaborating OR collaboration OR team OR cooperate OR cooperating OR cooperation) AND (technology OR technologies OR tool OR framework OR guideline OR principles OR practices OR systems OR resources)'
   )
 }

### 2023-05-12 R/arxiv-search.R
convert arxiv code to follow pattern

@@ -1,42 +1,42 @@
-# arxiv search using aRxiv
+#' Get all records from arXiv.
+#'
+#' @param search_terms Search terms, see `search_terms()`.
+#'
+#' @return Dataframe of records.
+#'
+arxiv_get_records <- function(search_terms) {
+  number_found <- aRxiv::arxiv_count(query = search_terms)
+  records <- aRxiv::arxiv_search(
+    query = search_terms,
+    # Round to nearest tenth.
+    limit = as.integer(round(number_found * 1.5, -2))
+  )
 
-# Load libraries ---------------------------------------------------------------
+  tibble::as_tibble(records)
+}
 
-library(tidyverse)
-library(lubridate)
-library(aRxiv)
-library(here)
-source(here("R/search-terms.R"))
+#' Retrieve and process records from arXiv, within last 5 years.
+#'
+#' @param search_terms Search terms, see `search_terms()`.
+#'
+#' @return Data frame of records.
+#'
+#' @examples
+#' search_terms("arxiv") |>
+#'   arxiv_retrieve_records()
+#'
+arxiv_retrieve_records <- function(search_terms) {
+  arxiv_records_processed <- search_terms %>%
+    arxiv_get_records() %>%
+    dplyr::select(id, date = updated, title, link_abstract) %>%
+    dplyr::filter(lubridate::ymd(lubridate::as_date(date)) >= five_years_ago())
 
-# Running search -----------------------------------------------------------------------
+  number_articles <- aRxiv::arxiv_count(query = search_terms)
 
-number_found <- arxiv_count(query = search_terms("arxiv"))
-arxiv_results <- arxiv_search(
-  query = search_terms("arxiv"),
-  # Round to nearest tenth.
-  limit = as.integer(round(number_found*1.5, -2))
-) %>%
-  as_tibble()
+  cli::cli_inform(c("Records from arXiv",
+    "i" = "{number_articles} records were retrieved.",
+    "i" = "{length(arxiv_records_processed)} records are within 5 years."
+  ))
 
-# Cleaning results -----------------------------------------------------------------------
-
-# Keep only some columns, drop anything before 5 years.
-
-five_years_ago <- "2017-01-01 00:00:00" #Could not run the code since this was not included. Change if we want it as an variable that we should load.
-
-arxiv_results_filtered <- arxiv_results %>% 
-  select(id, date = updated, title, authors, link_abstract, link_pdf) %>%
[…]

### 2023-05-12 R/utils.R
convert list into dataframe to store as csv (as function)

@@ -1,3 +1,17 @@
+#' Save a list of records to CSV file.
+#'
+#' @param records_list A list to save as CSV.
+#' @param path Path to save the records.
+#'
+#' @return Character for file path, side effect of saving a CSV file.
+#'
+save_list_as_csv <- function(records_list, path) {
+  records_list |>
+    dplyr::bind_rows() |>
+    readr::write_csv(path)
+  return(path)
+}
+
 #' Save a list object to a YAML file.
 #'
 #' @param records_list A list to save as YAML.

### 2023-05-12 R/zenodo-search.R
slightly rearrange data as list to match other sources

@@ -68,12 +68,12 @@ zenodo_extract_relevant_data <- function(record_list) {
 
   list(
     # creators = creators,
-    title = record_list$metadata$title,
-    # description = record_list$metadata$description,
+    doi = record_list$links$doi,
     date = record_list$metadata$publication_date,
+    title = drop_newlines(record_list$metadata$title),
+    # description = record_list$metadata$description,
     type = record_list$metadata$upload_type,
-    keywords = keywords,
-    doi = record_list$links$doi
+    keywords = keywords
   )
 }
 
@@ -82,6 +82,10 @@ zenodo_extract_relevant_data <- function(record_list) {
 #' @param search_terms Search terms to use for Zenodo.
 #'
 #' @return A list of records.
+#'
+#' @examples
+#' search_terms("zenodo") |>
+#' zenodo_retrieve_records()
 #'
 zenodo_retrieve_records <- function(search_terms) {
   zenodo_records <- search_terms %>%

### 2023-05-12 R/utils.R
function to drop newlines and to save as csv file

@@ -24,10 +24,34 @@ save_list_as_yaml <- function(records_list, path) {
   return(path)
 }
 
+#' Save a tibble to a CSV file.
+#'
+#' @param records_tbl A tibble to save to file.
+#' @param path Path to save the records.
+#'
+#' @return Character for file path, side effect of saving a CSV file.
+#'
+save_as_csv <- function(records_list, path) {
+  readr::write_csv(records_list, path)
+  return(path)
+}
+
 #' A date range from today until 5 years ago.
 #'
 #' @return A character vector of a date range.
 #'
 five_years_ago <- function() {
   glue::glue("{lubridate::today()-lubridate::years(5)}")
+}
+
+#' Drop newlines characters and flatten to a single string.
+#'
+#' @param text Text to modify.
+#'
+#' @return Combined text.
+#'
+drop_newlines <- function(text) {
+  text |>
+    stringr::str_remove_all("\n") |>
+    stringr::str_flatten(collapse = " ")
 }

### 2023-05-12 _targets.R
update targets file with arxiv

@@ -27,6 +27,7 @@ tar_option_set(
 # tar_source()
 source("R/search-terms.R")
 source("R/zenodo-search.R")
+source("R/arxiv-search.R")
 source("R/pubmed-search.R")
 source("R/utils.R")
 
@@ -42,7 +43,7 @@ list(
   ),
   tar_target(
     name = data_raw_zenodo,
-    command = save_list_as_yaml(zenodo_records, here::here("data-raw/zenodo.yaml")),
+    command = save_list_as_csv(zenodo_records, here::here("data-raw/zenodo.csv")),
     format = "file"
   ),
   # PubMed ------------------------------------------------------------------
@@ -56,7 +57,21 @@ list(
   ),
   tar_target(
     name = data_raw_pubmed,
-    command = save_list_as_yaml(pubmed_records, here::here("data-raw/pubmed.yaml")),
+    command = save_list_as_csv(pubmed_records, here::here("data-raw/pubmed.csv")),
+    format = "file"
+  ),
+  # arXiv ------------------------------------------------------------------
+  tar_target(
+    name = arxiv_search_terms,
+    command = search_terms("arxiv")
+  ),
+  tar_target(
+    name = arxiv_records,
+    command = arxiv_retrieve_records(arxiv_search_terms)
+  ),
+  tar_target(
+    name = data_raw_arxiv,
+    command = save_as_csv(arxiv_records, here::here("data-raw/arxiv.csv")),
     format = "file"
   )
 )

### 2023-05-12 R/arxiv-search.R
typos

@@ -35,7 +35,7 @@ arxiv_retrieve_records <- function(search_terms) {
 
   cli::cli_inform(c("Records from arXiv",
     "i" = "{number_articles} records were retrieved.",
-    "i" = "{length(arxiv_records_processed)} records are within 5 years."
+    "i" = "{nrow(arxiv_records_processed)} records are within 5 years."
   ))
 
   arxiv_records_processed

### 2023-05-12 R/search-terms.R

@@ -15,7 +15,7 @@ search_terms <- function(engine) {
     zenodo = "(title:open) AND (science OR research) AND (collaborate OR collaboration OR collaborating OR team OR cooperate OR cooperation OR cooperating) AND (technology OR technologies OR tool OR framework OR guideline OR principles OR practices OR systems OR resources)",
     wos = "(TI=(open)) AND ((ALL=(science)) OR ALL=(research)) AND (((ALL=(collaborat*)) OR ALL=(team)) OR ALL=(cooperat*)) AND ((((((((ALL=(technolog*)) OR ALL=(tool)) OR ALL=(framework)) OR ALL=(guideline)) OR ALL=(principles)) OR ALL=(practices)) OR ALL=(systems)) OR ALL=(resources))",
     # For some reason, arxiv doesn't like the * wildcard...
-    arxiv = '(ti:open) AND (all:science OR all:research) OR (all:collaborate OR all:collaborating OR all:collaboration OR all:team OR all:cooperate OR all:cooperating OR all:cooperation) AND (all:technology OR all:technologies OR all:tool OR all:framework OR all:guideline OR all:principles OR all:practices OR all:systems OR all:resources)'
+    arxiv = '(ti:open) AND (all:science OR all:research) OR (all:collaborate OR all:collaborating OR all:collaboration OR all:team OR all:cooperate OR all:cooperating OR all:cooperation) AND (all:technology OR all:technologies OR all:tool OR all:framework OR all:guideline OR all:principles OR all:practices OR all:systems OR all:resources)',
     # Changing according to the new tutorial: https://docs.ropensci.org/medrxivr/articles/medrxivr.html
     medrxiv = list(c("open"), c("science", "research"), c("collaborate","collaborating", "collaboration", "team", "cooperate", "cooperating"), c("technology", "technologies", "tool","framework", "guideline", "principles", "practices", "systems","resources"))
   )

### 2023-05-12 doc/paper.qmd
add some items to the paper results section about deviations from protocol

---
title: "Towards open collaboration in biomedical and health research: A scoping review"
date: last-modified
author: 
  - name: Hannah Chatwin
    affiliations: 
      - ref: au
  - name: Mario Garcia
    affiliations: 
      - ref: ku
  - name: Daniel Ibsen
    affiliations: 
      - ref: sdca
      - ref: au
  - name: Luke W. Johnston
    affiliations: 
      - ref: sdca
      - ref: au
affiliations:
  - id: sdca
    name: Steno Diabetes Center Aarhus
    country: Denmark
  - id: au
    name: Aarhus University
    country: Denmark
  - id: ku
    name: Copenhagen University
    country: Denmark
format: html
---

## Introduction

## Aims

Our original overall aim, as defined in the protocol, of this scoping
review is to identify current practices of open collaboration in
biomedical and health research.

The specific aims of this scoping review are to:

-   Provide an overview of current practices of or opinions about
    research collaboration that follow basic open principles (e.g.,
    transparency, accessibility)

-   Summarize existing online tools and resources available to improve
    open collaboration in research

We've expanded on our original aims to include a **secondary aim** of
building an open source R-based pipeline for conducting scoping reviews.
The entire source code, as well as text and collaboration workflows, are
found on our GitHub repository
[`science-collective/scoping-review`](https://github.com/science-collective/scoping-review).

## Methods

The full protocol for this scoping review was uploaded to the Open
Science Framework (DOI:
[`10.17605/OSF.IO/K9DR5`](https://doi.org/10.17605/OSF.IO/K9DR5)).

<!-- TODO: convert this to reference -->

### Formal sources

### Informal sources

<!-- TODO: need to add how we searched online sources, like lab websites -->

## Results

### Deviations from the protocol

-   **Original timeline**: We were quite ambitious with the timeline for
    completing this scoping review. We did not adhere to the timeline.
-   **API vs web search results**: Almost all source databases had
    exposed APIs, with R packages available to access them. We chose to
    use these rather than using the web to extract the source data is
    due to our secondary aim. However, we noticed that there were some
    small differences in search results between the API query compared
    to the web-based query. We can't explain these differences, though
    they were quite minor.

### 2023-05-14 R/arxiv-search.R
finished reviewing and downloading arxiv code/data. Closes #47

@@ -29,6 +29,7 @@ arxiv_retrieve_records <- function(search_terms) {
   arxiv_records_processed <- search_terms %>%
     arxiv_get_records() %>%
     dplyr::select(id, date = updated, title, link_abstract) %>%
+    dplyr::mutate(dplyr::across(dplyr::where(is.character), drop_newlines)) %>%
     dplyr::filter(lubridate::ymd(lubridate::as_date(date)) >= five_years_ago())
 
   number_articles <- aRxiv::arxiv_count(query = search_terms)

### 2023-05-14 R/utils.R

@@ -52,6 +52,5 @@ five_years_ago <- function() {
 #'
 drop_newlines <- function(text) {
   text |>
-    stringr::str_remove_all("\n") |>
-    stringr::str_flatten(collapse = " ")
+    stringr::str_replace_all("\n", " ")
 }

### 2023-05-14 R/pubmed-search.R
Update code and data for pubmed. Closes #34 closes #35

@@ -56,7 +56,9 @@ pubmed_extract_relevant_data <- function(record_list) {
   list(
     doi = unlist(metadata$ELocationID),
     date = date,
-    title = drop_newlines(unlist(metadata$ArticleTitle))
+    title = unlist(metadata$ArticleTitle) %>%
+      drop_newlines() %>%
+      stringr::str_flatten()
   )
 }
 

### 2023-05-14 R/zenodo-search.R
update zenodo code and data

@@ -70,7 +70,9 @@ zenodo_extract_relevant_data <- function(record_list) {
     # creators = creators,
     doi = record_list$links$doi,
     date = record_list$metadata$publication_date,
-    title = drop_newlines(record_list$metadata$title),
+    title = record_list$metadata$title %>%
+      drop_newlines() %>%
+      stringr::str_flatten(),
     # description = record_list$metadata$description,
     type = record_list$metadata$upload_type,
     keywords = keywords

### 2023-05-14 _targets.R
re-ran targets pipeline

@@ -25,11 +25,12 @@ tar_option_set(
 
 # Run the R scripts in the R/ folder with your custom functions:
 # tar_source()
+library(magrittr)
 source("R/search-terms.R")
+source("R/utils.R")
 source("R/zenodo-search.R")
 source("R/arxiv-search.R")
 source("R/pubmed-search.R")
-source("R/utils.R")
 
 list(
   # Zenodo ------------------------------------------------------------------

### 2023-06-01 doc/open-collab/selection/zenodo.Rmd

---
title: ""
output: html_document
---

```{r}
library(tidyverse)
library(here)
conflicted::conflict_prefer("filter", "dplyr")
zenodo_entries <- yaml::read_yaml(here("data-raw/zenodo.yaml"))
title_selection <- zenodo_entries %>% 
    map_dfr(~.x[c("title", "date", "doi", "keywords")]) 
View(title_selection)

remove_term_keep_collaborative <- function(variable, term) {
    !str_detect(variable, regex(term, ignore_case = TRUE)) &
        str_detect(variable, regex("collabora*", ignore_case = TRUE))
}

# TODO: Use ggcohort to track what is removed.
title_selection %>% 
    # Communication in the titles, e.g. "Scholarly communication" didn't fit 
    # with our aim.
    # filter(remove_term_keep_collaborative(title, "communication")) %>% 
    filter(str_detect(title, regex("communication", ignore_case = TRUE))) %>% 
    count()
    filter(str_detect(title, regex("publishing", ignore_case = TRUE))) %>% 
    View("Publishing")
    filter(str_detect(title, regex("open access", ignore_case = TRUE))) %>% 
    View("Open Access")
    View("")

title_selection %>% 
    filter(str_detect(title, regex("open science|collaboration", ignore_case = TRUE)))
    View()
```

### 2023-09-01 R/medrxiv-search.R
Update medrxiv-search.R
Added bit of code to make medrarxiv output same as arxiv output: same number of columns and column names.

@@ -48,5 +48,12 @@ medrxiv_retrieve_records <- function(search_terms) {
     "i" = "{number_articles} records were retrieved and are within 5 years.",
   ))
 
-  records_processed
+ #Small addition to get the necessary columns in the same format as arxiv:
+  
+ records_processed_clean <- records_processed %>%
+    dplyr::select(id, date, title, doi)
+  
+ colnames(records_processed_clean) <- c("id", "date", "title", "doi")
+  
+  records_processed_clean
 }

### 2023-09-01 R/medrxiv-search.R
Corrected the cli output to include articles with the word "open"

@@ -45,15 +45,15 @@ medrxiv_retrieve_records <- function(search_terms) {
 
   number_articles <- nrow(records_processed)
   cli::cli_inform(c("Records from medRxiv",
-    "i" = "{number_articles} records were retrieved and are within 5 years.",
+    "i" = "{number_articles} records were retrieved with the word 'open' in the title from the last 5 years.",
   ))
 
  #Small addition to get the necessary columns in the same format as arxiv:
-  
+
  records_processed_clean <- records_processed %>%
     dplyr::select(id, date, title, doi)
-  
+
  colnames(records_processed_clean) <- c("id", "date", "title", "doi")
-  
+
   records_processed_clean
 }

### 2023-09-01 doc/paper.qmd
added contributions sections

@@
       - ref: ku
-  - name: Daniel Ibsen
+  - name: Daniel B. Ibsen
     affiliations: 
@@
     they were quite minor.
+
+## Contributions
+
+<!-- TODO: add contributions according to: https://credit.niso.org/ -->
+
+HC: MG: DBI: LWJ:

### 2023-09-15 doc/paper.qmd
updated contributions
note about not using WOSR

@@
     they were quite minor.
+-   **Exclude Web of Science source**: We were unable to connect the Web
+    of Science source to R through the `{wosr}` package. Using the API
+    key did not as documented in the package did not work. We decided
+    that in the interest of reproducibility, that we exclude this
+    source.
 
@@
 
-HC: MG: DBI: LWJ:
+-   HC:
+-   MG:
+-   DBI: Conceptualization, Data curation, formal analysis,
+    investigation, methodology, writing
+-   LWJ:

### 2023-09-15 R/medrxiv-search.R
this last bit of code isn't necessary

@@ -109,12 +109,10 @@ medrxiv_generic_retrieve_records <- function(search_terms, server = c("biorxiv",
     "i" = "{number_articles} records were retrieved and are within 5 years."
   ))
 
- #Small addition to get the necessary columns in the same format as arxiv:
+ # Small addition to get the necessary columns in the same format as arxiv:
 
  records_processed_clean <- records_processed %>%
     dplyr::select(id, date, title, doi)
-
- colnames(records_processed_clean) <- c("id", "date", "title", "doi")
 
   records_processed_clean
 }

### 2023-10-06 R/automatic_exclusions.R
revise to fit within targets framework

@@ -1,13 +1,31 @@
-# Function to exclude titles containing excluded terms
-title_screening <- function(title, exclusions) {
-    any(grepl(paste(exclusions, collapse = "|"), title, ignore.case = TRUE))
+#' Exclude titles based on further criteria.
+#'
+#' @param data Reference/sources data frame.
+#'
+#' @return A tibble.
+#'
+#' @examples
+#' readr::read_csv(here::here("data-raw/zenodo.csv")) |> exclude_from_title() |> View()
+exclude_from_title <- function(data) {
+# TODO: Use ggcohort to track what is removed?
+  data |>
+    # Items related to healthcare or surgery
+    exclude(title, "open( |-)label|surgery|surgical|angle glaucoma|fracture|abdomen|wound") |>
+    # Items related to government, politics, or social
+    exclude(title, "open( |-)(government|governance|dialogue|letter|spaces|call|people|universit(y|ies))") |>
+    # Items related to electronics or tech
+    exclude(title, "open( |-)(circuit|shell|backend|set|iot)") |>
+    # Items related to dissemination
+    exclude(title, "open( |-)access|publishing|communication") |>
+    # Items related to misc
+    exclude(title, "open( |-)(end(ed)?|issues|water|air|education(al)?)")
 }
 
-# Load data
-pubmed_data <- read.csv("C:/Users/au711684/Documents/Science Collective/data-raw/pubmed.csv")
-
-# List of automatic exclusions
-automatic_exclusions <- c("open-label", "open label", "open surgery", "open government", "open governance", "open-angle glaucoma", "open dialogue", "open-circuit", "open circuit", "open-ended", "open fracture", "open issues", "open-shell", "open letter", "open abdomen", "open spaces", "open wound", "open call", "open people", "open water", "open university", "open universities")
-
-# Apply screening function to dataset
-pubmed_data_clean <- pubmed_data[!sapply(pubmed_data$title, title_screening, exclusions = automatic_exclusions), ]
+exclude <- function(data, variable, criteria) {
+  data |>
+    dplyr::filter(stringr::str_detect(
+      string = {{variable}},
+      pattern = stringr::regex(criteria, ignore_case = TRUE),
+      negate = TRUE
+    ))
+}

### 2023-10-06 _targets.R
add exclusions to targets

@@ -89,5 +89,14 @@ list(
     name = data_raw_medrxiv,
     command = save_as_csv(medrxiv_records, here::here("data-raw/medrxiv.csv")),
     format = "file"
+  ),
+  # Join sources and apply exclusions ---------------------------------------
+  tar_target(
+    name = records,
+    command = join_from_paths(c(data_raw_medrxiv, data_raw_arxiv, data_raw_pubmed, data_raw_zenodo)
+  ),
+  tar_targets(
+    name = records_after_title_exclusion,
+    command = exclude_from_title(records)
   )
 )

### 2023-10-06 R/merge-records.R
a function to join all the record data raw files

@@ -1,0 +1,10 @@
+#' Join all the record data into one tibble from the file paths.
+#'
+#' @param paths The file paths to the records in `data-raw/`.
+#'
+#' @return A tibble.
+#'
+join_from_path <- function(paths) {
+  purrr::map(paths, ~ readr::read_csv(.x)) |>
+    purrr::reduce(dplyr::full_join)
+}

### 2023-10-06 _targets.R
forgot to source these in targets

@@ -32,6 +32,8 @@ source("R/zenodo-search.R")
 source("R/arxiv-search.R")
 source("R/pubmed-search.R")
 source("R/medrxiv-search.R")
+source("R/merge-records.R")
+source("R/exclusions.R")
 
 list(
   # Zenodo ------------------------------------------------------------------

### 2023-10-06 R/pubmed-search.R
switch to tibble output and include id column

@@ -53,13 +53,14 @@ pubmed_extract_relevant_data <- function(record_list) {
   # Set any dates that don't exist to NA.
   date <- if (length(article_date)) article_date else NA
 
-  list(
+  tibble::tibble(
     doi = unlist(metadata$ELocationID),
     date = date,
     title = unlist(metadata$ArticleTitle) %>%
       drop_newlines() %>%
       stringr::str_flatten()
-  )
+  ) |>
+    dplyr::mutate(id = doi, .before = dplyr::everything())
 }
 
 #' Retrieve and process PubMed records from the last five years.

### 2023-10-06 R/zenodo-search.R

@@ -66,7 +66,7 @@ zenodo_extract_relevant_data <- function(record_list) {
     stringr::str_flatten("; ") %>%
     stringr::str_trim()
 
-  list(
+  tibble::tibble(
     # creators = creators,
     doi = record_list$links$doi,
     date = record_list$metadata$publication_date,
@@ -76,7 +76,8 @@ zenodo_extract_relevant_data <- function(record_list) {
     # description = record_list$metadata$description,
     type = record_list$metadata$upload_type,
     keywords = keywords
-  )
+  ) |>
+    dplyr::mutate(id = doi, .before = dplyr::everything())
 }
 
 #' Retrieve records from Zenodo in the last 5 years.

### 2023-10-06 R/pubmed-search.R
bind tibbles into rows, rather than use as list

@@ -73,9 +73,8 @@ pubmed_retrieve_records <- function(search_terms) {
   pubmed_records_processed <- search_terms %>%
     pubmed_get_records() %>%
     purrr::map(pubmed_extract_relevant_data) %>%
-    purrr::keep(~ {
-      is.na(.x$date) | lubridate::ymd(.x$date) >= five_years_ago()
-    })
+    purrr::list_rbind() |>
+    dplyr::filter(is.na(date) | lubridate::ymd(date) >= five_years_ago())
 
   number_articles <- easyPubMed::get_pubmed_ids(search_terms)$Count
 

### 2023-10-06 R/zenodo-search.R

@@ -98,7 +98,8 @@ zenodo_retrieve_records <- function(search_terms) {
   # Extract necessary data and keep only last five years
   zenodo_records_processed <- zenodo_records %>%
     purrr::map(zenodo_extract_relevant_data) %>%
-    purrr::keep(~ lubridate::ymd(lubridate::as_date(.x$date)) >= five_years_ago())
+    purrr::list_rbind() |>
+    dplyr::filter(lubridate::ymd(date) >= five_years_ago())
 
   # There's less entries from the original
   cli::cli_inform(c("Records from Zenodo",

### 2023-10-06 R/utils.R
don't need save_list_as_csv anymore, since they are not lists

@@ -1,29 +1,3 @@
-#' Save a list of records to CSV file.
-#'
-#' @param records_list A list to save as CSV.
-#' @param path Path to save the records.
-#'
-#' @return Character for file path, side effect of saving a CSV file.
-#'
-save_list_as_csv <- function(records_list, path) {
-  records_list |>
-    dplyr::bind_rows() |>
-    readr::write_csv(path)
-  return(path)
-}
-
-#' Save a list object to a YAML file.
-#'
-#' @param records_list A list to save as YAML.
-#' @param path Path to save the records.
-#'
-#' @return Character for file path, side effect of saving a YAML file.
-#'
-save_list_as_yaml <- function(records_list, path) {
-  yaml::write_yaml(records_list, path)
-  return(path)
-}
-
 #' Save a tibble to a CSV file.
 #'
 #' @param records_tbl A tibble to save to file.

### 2023-10-06 R/zenodo-search.R
remove the https part of the doi

@@ -68,7 +68,7 @@ zenodo_extract_relevant_data <- function(record_list) {
 
   tibble::tibble(
     # creators = creators,
-    doi = record_list$links$doi,
+    doi = stringr::str_remove(record_list$links$doi, "^https://doi.org/"),
     date = record_list$metadata$publication_date,
     title = record_list$metadata$title %>%
       drop_newlines() %>%

### 2023-10-06 doc/paper.qmd
rename title of paper

@@
 ---
-title: "Towards open collaboration in biomedical and health research: A scoping review"
+title: "Towards open collaboration in biomedical and health research: An open collaborative scoping review"
 date: last-modified

### 2023-10-06 R/exclusions.R
add more exclusion criteria based on quick reviews of the refs

@@ -5,20 +5,30 @@
 #' @return A tibble.
 #'
 #' @examples
-#' readr::read_csv(here::here("data-raw/zenodo.csv")) |> exclude_from_title() |> View()
+#' readr::read_csv(here::here("data-raw/pubmed.csv")) |> exclude_from_title() |> View()
 exclude_from_title <- function(data) {
 # TODO: Use ggcohort to track what is removed?
   data |>
-    # Items related to healthcare or surgery
-    exclude(title, "open( |-)label|surgery|surgical|angle glaucoma|fracture|abdomen|wound") |>
+    # Items related to surgery
+    exclude(title, "hysterectomy|surgery|surgical|angle glaucoma|fracture|abdomen|wound|colectomy|vein|resection|gastrectomy|urethroplasty") |>
+    # Items related to healthcare or health study design
+    exclude(title, "open( |-)(cohort|label|trial|radical|radiology|acute|study|weighing|registry)|rehab|neuroscience|rt-qpcr|randomi[zs]ed|neuronal|neurons") |>
     # Items related to government, politics, or social
-    exclude(title, "open( |-)(government|governance|dialogue|letter|spaces|call|people|universit(y|ies))") |>
+    exclude(title, "open( |-)(government|governance|dialog(ue)?|letter|spaces|call|people|universit(y|ies)|stewardship)") |>
     # Items related to electronics or tech
-    exclude(title, "open( |-)(circuit|shell|backend|set|iot)") |>
+    exclude(title, "open( |-)(electronics|circuit|shell|backend|set|iot|user|hollow|rdf)|hardware|blockchain|resonator|nanoparticle|robotic") |>
+    # Items related to physics or engineering
+    exclude(title, "resonator|nanoparticle|robotic|x-ray|open( |-)(universe|systems)|nanofluidic") |>
+    # Items related to specific software
+    exclude(title, "matlab|pathofusion|mrqy|imagej|opsef|open-tes") |>
     # Items related to dissemination
-    exclude(title, "open( |-)access|publishing|communication") |>
+    exclude(title, "open( |-)(access|review(er)?)|publishing|communication") |>
+    # Items related to education
+    exclude(title, "open( |-)(education(al)?|seminar|learning)|mooc|massive open online") |>
+    # Items related to industry/business
+    exclude(title, "open( |-)(leader(ship)?|marketplace|innovation|pit|biomass|fermentation|hydroponic)") |>
[…]

### 2024-04-04 doc/review-stages.qmd
start of draft for summary report on titles we kept, agreed on, and disagreed on

---
title: "Review stages"
format: html
---

```{r setup}
#| include: false
library(tidyverse)
library(here)
library(fs)
```

## Title review stage

```{r}
#| message: false
title_reviews <- here("data/review/titles/") |> 
  dir_ls(glob = "*.csv") |> 
  map(read_csv)

reviewers <- names(title_reviews) |> 
  path_file() |> 
  path_ext_remove() |> 
  str_to_sentence()

title_reviews <- title_reviews |> 
  set_names(reviewers)
```

```{r tbl-titles-kept}
#| tbl-cap: "Number of articles each reviewer kept after the first screening of the titles."
title_reviews |> 
  map(\(df) count(df, name = "Articles kept")) |> 
  list_rbind(names_to = "Reviewers") |> 
  knitr::kable()
```

```{r tbl-titles-agreements}
#| tbl-cap: "Agreements in article titles kept between all reviewers during the title screening stage."
common_titles <- title_reviews |>
  reduce(\(df1, df2) inner_join(df1, df2, by = join_by(id, title, publication_date, doi)))
common_titles |> 
  select("Article title" = title) |> 
  knitr::kable()
```

```{r tbl-title-disagreements}
#| tbl-cap: "Article titles **not** kept between all reviewers during the title screening stage."
title_reviews |> 
  map(\(df) anti_join(df, common_titles, by = join_by(id, title, publication_date, doi))) |>
  list_rbind() |> 
  select("Article titles" = title) |> 
  distinct() |> 
  knitr::kable()
```

### 2024-04-05 doc/review-stages.qmd
wip: updates to doc based on meeting

@@
 
+<!-- TODO: Include last date the articles were extracted from. -->
+
 ## Title review stage
+
+During the first stage of the reviewing, we only looked at titles. Below
+is the code to extract the titles we each individually reviewed, so we
+can show some details about how many were included, excluded, and which
+titles we agreed on or disagreed on.
 
@@
 
+In the title screening stage, the number of titles we kept are listed in
+@tbl-titles-kept.
+
 ```{r tbl-titles-kept}
@@
   list_rbind(names_to = "Reviewers") |>
+  # TODO: Include percent of total articles.
   knitr::kable()
@@
 
+We want to know how many of these titles we all agreed on between the
+three reviewers, which is shown in @tbl-titles-agreements
+
+```{r}
+common_titles <- title_reviews |>
+  reduce(\(df1, df2) {
+    inner_join(df1, df2, by = join_by(id, title, publication_date, doi))
+  })
+```
+
 ```{r tbl-titles-agreements}
-#| tbl-cap: "Agreements in article titles kept between all reviewers during the title screening stage."
-common_titles <- title_reviews |>
-  reduce(\(df1, df2) inner_join(df1, df2, by = join_by(id, title, publication_date, doi)))
+#| tbl-cap: !expr glue::glue("The {nrow(common_titles)} article titles we all agreed on and kept during the title screening stage.")
 common_titles |>
@@
 ```
+
+One person will review and flag any o might be relevant but are not in
+agreement to keep.
 
@@
 ```
+
+## Abstract review stage
+
+## Reading stage
+
+-   first us reading a few to get an idea of themes and information to
+    extract
+-   and then discuss together the themes to group by and information to
+    extract
+-   Then we follow what we agreed on
+
+## Writing stage
+
+-   How to visualize?

### 2024-04-10 doc/review-stages.qmd
Added next stage with a list of screened papers.

@@
 ```{r tbl-titles-kept}
+#| message: false
 #| tbl-cap: "Number of articles each reviewer kept after the first screening of the titles."
@@
   })
+
+#| tbl-cap: "Number of articles we all agreed on."
+common_titles |>
+  count(name = "Titles all agreed on") |>
+  knitr::kable()
+
 ```
@@
 
-One person will review and flag any o might be relevant but are not in
-agreement to keep.
+One person will review the titles and flag any paper that might be
+relevant but are not in agreement to keep.
 
@@
 
+We saved a new csv file with all the disagreements and saved a new list
+called "resolved.csv" where the final papers to include are listed.
+
+```{r csv-paper-disagreements}
+
+title_disagrements <- title_reviews |>
+  map(\(df) anti_join(df, common_titles, by = join_by(id, title, publication_date, doi))) |>
+  list_rbind() |>
+  distinct()
+
+#save new csv file to go through links and check disagreements
+write.table(title_disagrements, file = here("data/review/titles/disagreements.csv"))
+
+```
+
 ## Abstract review stage
+
+-   all will review the abstracts of the included papers
+-   this will create our final list of included papers
 
@@
 
--   first us reading a few to get an idea of themes and information to
+-   first skimming the papers and group by themes
+-   then read a few from each theme to decide on what information to
     extract
--   and then discuss together the themes to group by and information to
+-   then discuss together the themes to group by and information to
     extract
--   Then we follow what we agreed on
+-   then we follow what we agreed on
 
@@
 
--   How to visualize?
+-   how to visualize?

### 2024-05-13 doc/review-stages.qmd
refactor: moved code from quarto into own function file

@@
 library(fs)
+targets::tar_config_set(store = here("_targets"))
 ```
@@
 #| message: false
-title_reviews <- here("data/review/titles/") |>
-  dir_ls(glob = "*.csv") |>
-  map(read_csv)
-
-reviewers <- names(title_reviews) |>
-  path_file() |>
-  path_ext_remove() |>
-  str_to_sentence()
-
-title_reviews <- title_reviews |>
-  set_names(reviewers)
 ```
@@
 #| tbl-cap: "Number of articles each reviewer kept after the first screening of the titles."
-title_reviews |>
+targets::tar_read(titles_kept) |>
   map(\(df) count(df, name = "Articles kept")) |>
@@
 We want to know how many of these titles we all agreed on between the
-three reviewers, which is shown in @tbl-titles-agreements
+three reviewers:
 
 ```{r}
-common_titles <- title_reviews |>
-  reduce(\(df1, df2) {
-    inner_join(df1, df2, by = join_by(id, title, publication_date, doi))
-  })
+common_titles <- targets::tar_read(titles_agreed_on)
+```
 
-#| tbl-cap: "Number of articles we all agreed on."
-common_titles |>
-  count(name = "Titles all agreed on") |>
-  knitr::kable()
-
-```
+We seemed to agree on `r nrow(common_titles)` titles, with the full
+title list shown in @tbl-titles-agreements.
 
@@
 #| tbl-cap: "Article titles **not** kept between all reviewers during the title screening stage."
-title_reviews |>
-  map(\(df) anti_join(df, common_titles, by = join_by(id, title, publication_date, doi))) |>
-  list_rbind() |>
+targets::tar_read(titles_disagreed_on) |>
   select("Article titles" = title) |>
-  distinct() |>
   knitr::kable()
@@
 
-We saved a new csv file with all the disagreements and saved a new list
-called "resolved.csv" where the final papers to include are listed.
+We saved a new csv file with all the disagreements and then made a copy
+of that list in the file `resolved.csv`. This file contains some titles
+that we disagreed on but that were briefly reviewed by one reviewer,
+discussed, and included in the end.
 
-```{r csv-paper-disagreements}
+The titles we agreed on were:
 
-title_disagrements <- title_reviews |>
-  map(\(df) anti_join(df, common_titles, by = join_by(id, title, publication_date, doi))) |>
-  list_rbind() |>
-  distinct()
-
-#save new csv file to go through links and check disagreements
-write.table(title_disagrements, file = here("data/review/titles/disagreements.csv"))
-
+```{r}
+#| tbl-cap: "Article titles we agreed to keep from the disagreement list."
+targets::tar_read(titles_resolved_path) |>
+  select("Article title" = title) |>
+  knitr::kable()
 ```

### 2024-05-13 R/title-review.R

@@ -1,0 +1,40 @@
+path_reviewer_titles <- function(reviewers) {
+  here::here("data/review/titles", reviewers) |>
+    fs::path_ext_set("csv")
+}
+
+read_title_reviews <- function(path) {
+  title_reviews <- path |>
+    purrr::map(read_csv)
+
+  reviewers <- names(title_reviews) |>
+    fs::path_file() |>
+    fs::path_ext_remove() |>
+    stringr::str_to_sentence()
+
+  title_reviews |>
+    rlang::set_names(reviewers)
+}
+
+get_agreed_on_titles <- function(title_list) {
+  stopifnot(is.list(title_list))
+  title_list |>
+    purrr::reduce(\(df1, df2) {
+      dplyr::inner_join(df1, df2, by = dplyr::join_by(id, title, publication_date, doi))
+    })
+}
+
+get_disagreed_on_titles <- function(title_list, agreed_on_titles) {
+  stopifnot(is.list(title_list))
+  title_list |>
+    purrr::map(\(df) dplyr::anti_join(df, agreed_on_titles, by = dplyr::join_by(id, title, publication_date, doi))) |>
+    purrr::list_rbind() |>
+    dplyr::distinct()
+}
+
+copy_if_not_exists <- function(path, copied_path) {
+  if (!fs::file_exists(copied_path)) {
+    fs::file_copy(path, copied_path)
+  }
+  copied_path
+}

### 2024-05-13 _targets.R
build: update targets file with further build items

@@ -5,7 +5,7 @@
 
 # Load packages required to define the pipeline:
 library(targets)
-# library(tarchetypes) # Load other packages as needed. # nolint
+library(tarchetypes)
 
 # Set target options:
 tar_option_set(
@@ -29,9 +29,10 @@ library(magrittr)
 source("R/utils.R")
 source("R/openalex-search.R")
 source("R/exclusions.R")
+source("R/title-review.R")
 
 list(
-  # Open Alex ---------------------------------------------------------------
+  # Open Alex Title Search --------------------------------------------------
   tar_target(
     name = search_term,
     command = search_terms()
@@ -50,7 +51,52 @@ list(
     command = exclude_from_title(records_title_only)
   ),
   tar_target(
-    name = data_records,
-    command = save_as_csv(records_after_title_exclusion, here::here("data/records.csv"))
+    name = records_titles_path,
+    command = save_as_csv(records_after_title_exclusion, here::here("data/titles.csv"))
+  ),
+
+  # Save individual review files for title review ---------------------------
+  tar_target(
+    name = reviewers,
+    command = c("daniel", "mario", "luke")
+  ),
+  tar_target(
+    name = reviewers_title_files,
+    command = reviewers |>
+      path_reviewer_titles() |>
+      purrr::walk(\(path) copy_if_not_exists(records_titles_path, path)),
+    format = "file"
+  ),
+  tar_target(
+    name = titles_kept,
+    command = reviewers_title_files |>
+      read_title_reviews()
+  ),
+  tar_target(
+    name = titles_agreed_on,
+    command = titles_kept |>
+      get_agreed_on_titles()
+  ),
+  tar_target(
+    name = titles_disagreed_on,
+    command = titles_kept |>
+      get_disagreed_on_titles(titles_agreed_on)
+  ),
+  tar_target(
+    name = titles_disagreed_on_path,
+    command = save_as_csv(titles_disagreed_on, here::here("data/review/titles-disagreed-on.csv")),
+    format = "file"
+  ),
+  tar_target(
+    name = titles_resolved_path,
+    command = titles_disagreed_on |>
+      copy_if_not_exists(
+        here::here("data/review/titles/resolved.csv")
+      )
+  ),
+  # Report -----------------------------------------------------------------
+  tar_quarto(
+    name = review_steps,
+    path = here::here("doc/review-stages.qmd")
   )
 )

### 2024-05-13 R/extract-prisma-scr-checklist.R
style: ran styler

@@ -3,39 +3,40 @@ library(tidyverse)
 
 docx_file <- fs::file_temp(ext = ".docx")
 download.file(
-    "http://www.prisma-statement.org/documents/PRISMA-ScR-Fillable-Checklist_10Sept2019.docx",
-    destfile = docx_file
+  "http://www.prisma-statement.org/documents/PRISMA-ScR-Fillable-Checklist_10Sept2019.docx",
+  destfile = docx_file
 )
 
 doc_contents <- read_docx(docx_file)
 checklist <- docx_extract_tbl(doc_contents) %>%
-    rename_with(snakecase::to_snake_case) %>%
-    rename(subsection = section) %>%
-    mutate(section = if_else(is.na(item), str_to_sentence(subsection), NA_character_)) %>%
-    fill(section) %>%
-    filter(!is.na(item)) %>%
-    select(section, subsection, item, description = prisma_sc_r_checklist_item)
+  rename_with(snakecase::to_snake_case) %>%
+  rename(subsection = section) %>%
+  mutate(section = if_else(is.na(item), str_to_sentence(subsection), NA_character_)) %>%
+  fill(section) %>%
+  filter(!is.na(item)) %>%
+  select(section, subsection, item, description = prisma_sc_r_checklist_item)
 
 # Save to doc/instructions/primsa-scr-checklist.md file
 knitr::kable(checklist) %>%
-    write_lines(here::here("doc", "instructions", "primsa-scr-checklist.md"))
+  write_lines(here::here("doc", "instructions", "primsa-scr-checklist.md"))
 
 checklist_for_issue <- function(data) {
-    header <- glue::glue("**{unique(data$section)}**:")
-    check_lists <- data %>%
-        glue::glue_data("- [ ] {subsection}: {description}")
-    c("\n", header, "\n", check_lists)
+  header <- glue::glue("**{unique(data$section)}**:")
+  check_lists <- data %>%
+    glue::glue_data("- [ ] {subsection}: {description}")
+  c("\n", header, "\n", check_lists)
 }
 
 text_for_issue <- checklist %>%
-    mutate(section = fct_inorder(section)) %>%
-    group_split(section) %>%
-    map(checklist_for_issue) %>%
-    unlist()
+  mutate(section = fct_inorder(section)) %>%
+  group_split(section) %>%
+  map(checklist_for_issue) %>%
+  unlist()
 
 # Save to clipboard to paste into GitHub Issue.
[…]

### 2024-05-13 R/title-review.R
build: small fixes and rebuild pipeline

@@ -5,7 +5,8 @@ path_reviewer_titles <- function(reviewers) {
 
 read_title_reviews <- function(path) {
   title_reviews <- path |>
-    purrr::map(read_csv)
+    rlang::set_names(path) |>
+    purrr::map(readr::read_csv)
 
   reviewers <- names(title_reviews) |>
     fs::path_file() |>

### 2024-05-13 _targets.R

@@ -55,7 +55,7 @@ list(
     command = save_as_csv(records_after_title_exclusion, here::here("data/titles.csv"))
   ),
 
-  # Save individual review files for title review ---------------------------
+  # Title review stage ------------------------------------------------------
   tar_target(
     name = reviewers,
     command = c("daniel", "mario", "luke")
@@ -84,7 +84,7 @@ list(
   ),
   tar_target(
     name = titles_disagreed_on_path,
-    command = save_as_csv(titles_disagreed_on, here::here("data/review/titles-disagreed-on.csv")),
+    command = save_as_csv(titles_disagreed_on, here::here("data/review/titles/disagreements.csv")),
     format = "file"
   ),
   tar_target(
@@ -94,7 +94,15 @@ list(
         here::here("data/review/titles/resolved.csv")
       )
   ),
-  # Report -----------------------------------------------------------------
+  tar_target(
+    name = titles_selected,
+    command = purrr::list_rbind(list(
+      titles_agreed_on,
+      titles_resolved_path |>
+        readr::read_csv()
+    )) |>
+      dplyr::distinct()
+  ),
   tar_quarto(
     name = review_steps,
     path = here::here("doc/review-stages.qmd")

### 2024-05-13 doc/review-stages.qmd
feat: add function to get abstracts

@@
 ```{r}
+#| message: false
 #| tbl-cap: "Article titles we agreed to keep from the disagreement list."
 targets::tar_read(titles_resolved_path) |>
+  read_csv() |>
+  select("Article title" = title) |>
+  knitr::kable()
+```
+
+The final list of titles we selected, between the agreed on ones as well
+as the resolved ones, are:
+
+```{r}
+#| message: false
+#| tbl-cap: "Article titles we reviewed and selected to continue for abstract review."
+targets::tar_read(titles_selected) |>
   select("Article title" = title) |>
@@
 ## Abstract review stage
+
+```{r}
+targets::tar_read(titles_selected) |> 
+  dplyr::pull(id) |> 
+  openalex_retrieve_abstracts() |>
+  jsonlite::toJSON() |> 
+  jsonlite::parse_json() |>
+  yaml::as.yaml() |>
+  yaml::write_yaml(here("data/review/abstracts.yaml"))
+```
 

### 2024-05-13 R/openalex-search.R

@@ -39,3 +39,14 @@ openalex_retrieve_titles <- function(search_term, from_date) {
   ) |>
     dplyr::rename(title = display_name)
 }
+
+openalex_retrieve_abstracts <- function(ids) {
+  openalexR::oa_fetch(
+    identifier = ids,
+    per_page = 200,
+    mailto = "lwjohnst@gmail.com",
+    abstract = TRUE
+  ) |>
+    dplyr::select(id, doi, display_name, publication_date, ab) |>
+    dplyr::rename(title = display_name, abstract = ab)
+}

### 2024-05-17 doc/review-stages.qmd
build: setup targets for getting the abstracts

@@
 
-```{r}
-targets::tar_read(titles_selected) |> 
-  dplyr::pull(id) |> 
-  openalex_retrieve_abstracts() |>
-  jsonlite::toJSON() |> 
-  jsonlite::parse_json() |>
-  yaml::as.yaml() |>
-  yaml::write_yaml(here("data/review/abstracts.yaml"))
-```
-
 -   all will review the abstracts of the included papers
@@
 
--   first skimming the papers and group by themes
+-   first skimming the papers and group by themes, writing a basic
+    free-hand summary
 -   then read a few from each theme to decide on what information to

### 2024-05-17 R/abstract-review.R

@@ -1,0 +1,4 @@
+path_reviewer_abstracts <- function(reviewers) {
+  here::here("data/review/abstracts", reviewers) |>
+    fs::path_ext_set("yaml")
+}

### 2024-05-17 R/utils.R

@@ -1,12 +1,12 @@
 #' Save a tibble to a CSV file.
 #'
-#' @param records_tbl A tibble to save to file.
+#' @param data A tibble to save to file.
 #' @param path Path to save the records.
 #'
 #' @return Character for file path, side effect of saving a CSV file.
 #'
-save_as_csv <- function(records_tbl, path) {
-  readr::write_csv(records_tbl, path)
+save_as_csv <- function(data, path) {
+  readr::write_csv(data, path)
   return(path)
 }
 
@@ -18,4 +18,26 @@ five_years_ago <- function() {
   # To make this accessible to the function below.
   `%m-%` <- lubridate::`%m-%`
   as.character(glue::glue("{lubridate::today() %m-% lubridate::years(5)}"))
+}
+
+#' Save a tibble to a YAML file.
+#'
+#' @param data The data to save.
+#' @param path The output file path.
+#'
+#' @return A character vector with file path.
+#'
+save_as_yaml <- function(data, path) {
+  data |>
+    yaml::as.yaml(column.major = FALSE) |>
+    yaml::write_yaml(path)
+  return(path)
+}
+
+copy_if_not_exists <- function(path, copied_path) {
+  if (!fs::file_exists(copied_path)) {
+    fs::dir_create(fs::path_dir(copied_path), recurse = TRUE)
+    fs::file_copy(path, copied_path)
+  }
+  copied_path
 }

### 2024-05-17 _targets.R

@@ -30,6 +30,7 @@ source("R/utils.R")
 source("R/openalex-search.R")
 source("R/exclusions.R")
 source("R/title-review.R")
+source("R/abstract-review.R")
 
 list(
   # Open Alex Title Search --------------------------------------------------
@@ -52,7 +53,7 @@ list(
   ),
   tar_target(
     name = records_titles_path,
-    command = save_as_csv(records_after_title_exclusion, here::here("data/titles.csv"))
+    command = save_as_csv(records_after_title_exclusion, here::here("data/review/titles.csv"))
   ),
 
   # Title review stage ------------------------------------------------------
@@ -102,6 +103,24 @@ list(
         readr::read_csv()
     )) |>
       dplyr::distinct()
+  ),
+
+  # Abstract retrieval ------------------------------------------------------
+  tar_target(
+    name = records_abstracts,
+    command = openalex_retrieve_abstracts(titles_selected$id)
+  ),
+  tar_target(
+    name = records_abstracts_path,
+    command = save_as_yaml(records_abstracts, here::here("data/review/abstracts.yaml")),
+    format = "file"
+  ),
+  tar_target(
+    name = reviewers_abstract_files,
+    command = reviewers |>
+      path_reviewer_abstracts() |>
+      purrr::walk(\(path) copy_if_not_exists(records_abstracts_path, path)),
+    format = "file"
   ),
   tar_quarto(
     name = review_steps,

### 2024-05-17 R/title-review.R
chore: this was moved to utils

@@ -33,9 +33,3 @@ get_disagreed_on_titles <- function(title_list, agreed_on_titles) {
     dplyr::distinct()
 }
 
-copy_if_not_exists <- function(path, copied_path) {
-  if (!fs::file_exists(copied_path)) {
-    fs::file_copy(path, copied_path)
-  }
-  copied_path
-}

### 2024-06-02 doc/presentations/steno-epi-meeting-240603/index.qmd
structure for presentation at group meeting

---
title: 'Introduction to scoping review on open collaboration and experiences with working reproducibly and using GitHub'
date: "2024-06-03"
date-format: long
author:
  - Daniel B. Ibsen
location: "Steno Diabetes Center Aarhus"
format: 
  revealjs:
    fig-align: center
    from: markdown+emoji
    theme:
      - dark
    progress: true
    embed-resources: true
editor: 
  markdown: 
    wrap: 72
    canonical: true
---

# The Polymath problem - revisited

Recall the example from the research retreat.

They used open collaboration to solve a very complex problem.

## Open collaboration {.center}

Today, scientific research almost always requires working with other
people. And with the growing complexity and specialization in scientific
practices and methods, together with globalisation of health and
environmental issues, there is a great need for a paradigm shift in
research collaboration to be able to tackle these challenges.

Open collaboration may offer this solution. Open collaboration is
defined as:

> "*an online environment that (a) supports the collective production of
> an artifact (b) through a technologically mediated collaboration
> platform (c) that presents a low barrier to entry and exit and (d)
> supports the emergence of persistent but malleable social
> structures.*" This scoping review will focus on current practices of
> open collaboration and open science in relation to collaboration in
> the field of biomedical and health research (Forte and Lampe (2013)).

## Aim of scoping review {.center}

Our overarching aim of this scoping review is to identify current
practices of open collaboration in biomedical and health research.

The specific aims of this scoping review are to:

-   Provide an overview of current practices of or opinions about
    research collaboration that follow basic open principles (e.g.,
    transparency, accessibility)

-   Summarize existing online tools and resources available to improve
    open collaboration in research

-   building an open source R-based pipeline for conducting scoping
    reviews.

The entire source code, as well as text and collaboration workflows, are
found on our GitHub repository
[`science-collective/scoping-review`](https://github.com/science-collective/scoping-review).

## Process {.center}

1.  Select topic

2.  Workflow

3.  Protocol

4.  S

## Process

```         
-   R and Github
-   Discord
-   Co-working sessions/regular meetings
-   Organizing
    tasks/[issues](https://github.com/science-collective/scoping-review/issues)/[roadmap](https://github.com/science-collective/scoping-review/blob/main/ROADMAP.md)
-   Reflections
```

## Protocol

[Registration link](https://doi.org/10.17605/OSF.IO/K9DR5)

Search several databases...

But then came OpenAlex

Included all our databases and more.

## Search

See review-stages.qmd

### 2024-06-06 R/abstract-review.R
feat: functions to read abstract yaml files

@@ -2,3 +2,26 @@ path_reviewer_abstracts <- function(reviewers) {
   here::here("data/review/abstracts", reviewers) |>
     fs::path_ext_set("yaml")
 }
+
+read_abstract_yaml <- function(path) {
+  path |>
+    # There's a weird `|` at the start of each file
+    readr::read_lines(skip = 1) |>
+    yaml::yaml.load() |>
+    purrr::map(tibble::as_tibble) |>
+    purrr::list_rbind()
+}
+
+read_abstract_reviews <- function(path) {
+  abstract_reviews <- path |>
+    rlang::set_names(path) |>
+    purrr::map(read_abstract_yaml)
+
+  reviewers <- names(abstract_reviews) |>
+    fs::path_file() |>
+    fs::path_ext_remove() |>
+    stringr::str_to_sentence()
+
+  abstract_reviews |>
+    rlang::set_names(reviewers)
+}

### 2024-06-06 R/extract-prisma-scr-checklist.R
chore: comment out this, so this can be used as a package

@@ -1,42 +1,42 @@
-library(docxtractr)
-library(tidyverse)
-
-docx_file <- fs::file_temp(ext = ".docx")
-download.file(
-  "http://www.prisma-statement.org/documents/PRISMA-ScR-Fillable-Checklist_10Sept2019.docx",
-  destfile = docx_file
-)
-
-doc_contents <- read_docx(docx_file)
-checklist <- docx_extract_tbl(doc_contents) %>%
-  rename_with(snakecase::to_snake_case) %>%
-  rename(subsection = section) %>%
-  mutate(section = if_else(is.na(item), str_to_sentence(subsection), NA_character_)) %>%
-  fill(section) %>%
-  filter(!is.na(item)) %>%
-  select(section, subsection, item, description = prisma_sc_r_checklist_item)
-
-# Save to doc/instructions/primsa-scr-checklist.md file
-knitr::kable(checklist) %>%
-  write_lines(here::here("doc", "instructions", "primsa-scr-checklist.md"))
-
-checklist_for_issue <- function(data) {
-  header <- glue::glue("**{unique(data$section)}**:")
-  check_lists <- data %>%
-    glue::glue_data("- [ ] {subsection}: {description}")
-  c("\n", header, "\n", check_lists)
-}
-
-text_for_issue <- checklist %>%
-  mutate(section = fct_inorder(section)) %>%
-  group_split(section) %>%
-  map(checklist_for_issue) %>%
-  unlist()
-
-# Save to clipboard to paste into GitHub Issue.
-c(
-  "> Note: This checklist was generated with the script `R/extract-prisma-scr-checklist.R`.",
-  "The checklist can also be found at `doc/instructions/prisma-scr-checklist.md`.",
-  text_for_issue
-) %>%
-  clipr::write_clip()
+# library(docxtractr)
+# library(tidyverse)
+#
+# docx_file <- fs::file_temp(ext = ".docx")
+# download.file(
+#   "http://www.prisma-statement.org/documents/PRISMA-ScR-Fillable-Checklist_10Sept2019.docx",
+#   destfile = docx_file
+# )
+#
+# doc_contents <- read_docx(docx_file)
+# checklist <- docx_extract_tbl(doc_contents) %>%
+#   rename_with(snakecase::to_snake_case) %>%
+#   rename(subsection = section) %>%
+#   mutate(section = if_else(is.na(item), str_to_sentence(subsection), NA_character_)) %>%
+#   fill(section) %>%
[…]

### 2024-06-06 _targets.R
build: update targets pipeline with abstract review code

@@ -122,6 +122,33 @@ list(
       purrr::walk(\(path) copy_if_not_exists(records_abstracts_path, path)),
     format = "file"
   ),
+  tar_target(
+    name = abstracts_kept,
+    command = reviewers_abstract_files |>
+      read_abstract_reviews()
+  ),
+  # tar_target(
+  #   name = abstracts_agreed_on,
+  #   command = abstracts_kept |>
+  #     get_agreed_on_abstracts()
+  # ),
+  # tar_target(
+  #   name = abstracts_disagreed_on,
+  #   command = abstracts_kept |>
+  #     get_disagreed_on_abstracts(abstracts_agreed_on)
+  # ),
+  # tar_target(
+  #   name = abstracts_disagreed_on_path,
+  #   command = save_as_csv(abstracts_disagreed_on, here::here("data/review/abstracts/disagreements.csv")),
+  #   format = "file"
+  # ),
+  # tar_target(
+  #   name = abstracts_resolved_path,
+  #   command = abstracts_disagreed_on |>
+  #     copy_if_not_exists(
+  #       here::here("data/review/abstracts/resolved.csv")
+  #     )
+  # ),
   tar_quarto(
     name = review_steps,
     path = here::here("doc/review-stages.qmd")

### 2024-06-06 doc/review-stages.qmd
docs: added code chunk to show number of kept abstracts

@@
 titles we agreed on or disagreed on.
-
-```{r}
-#| message: false
-```
 
@@
 
+The second phase of the review is looking over the abstracts. In
+@tbl-abstracts-kept below are the number of articles each reviewer kept
+after this second screening.
+
+```{r tbl-abstracts-kept}
+#| message: false
+#| tbl-cap: "Number of articles each reviewer kept after the second screening of the abstracts."
+targets::tar_read(abstracts_kept) |> 
+  map(\(df) count(df, name = "Articles kept")) |>
+  list_rbind(names_to = "Reviewers") |>
+  # TODO: Include percent of total articles.
+  knitr::kable()
+
+# targets::tar_read(abstracts_kept) |> 
+#   select("Article titles" = title) |>
+#   knitr::kable()
+```
+
 ## Reading stage

### 2024-06-06 doc/presentations/steno-epi-meeting-240603/index.qmd
presentation for group meeting at SDCA

@@
 ---
-title: 'Introduction to scoping review on open collaboration and experiences with working reproducibly and using GitHub'
+title: 'Scoping review on open collaboration'
+subtitle: 'Experiences with working reproducibly and using GitHub'
 date: "2024-06-03"
@@
 
+::: notes
 Recall the example from the research retreat.
@@
 They used open collaboration to solve a very complex problem.
+:::
 
@@
 
+Open collaboration is defined as:
+
+> "*an online environment that (a) supports the collective production of
+> an artifact (b) through a technologically mediated collaboration
+> platform (c) that presents a low barrier to entry and exit and (d)
+> supports the emergence of persistent but malleable social
+> structures.*" (Forte and Lampe, 2013)
+
+::: notes
 Today, scientific research almost always requires working with other
@@
 
-Open collaboration may offer this solution. Open collaboration is
-defined as:
-
-> "*an online environment that (a) supports the collective production of
-> an artifact (b) through a technologically mediated collaboration
-> platform (c) that presents a low barrier to entry and exit and (d)
-> supports the emergence of persistent but malleable social
-> structures.*" This scoping review will focus on current practices of
-> open collaboration and open science in relation to collaboration in
-> the field of biomedical and health research (Forte and Lampe (2013)).
+Open collaboration may offer this solution.
+:::
 
 ## Aim of scoping review {.center}
-
-Our overarching aim of this scoping review is to identify current
-practices of open collaboration in biomedical and health research.
-
-The specific aims of this scoping review are to:
 
@@
 
-The entire source code, as well as text and collaboration workflows, are
-found on our GitHub repository
-[`science-collective/scoping-review`](https://github.com/science-collective/scoping-review).
+Source code
+[`science-collective/scoping-review`](https://github.com/science-collective/scoping-review)
+
+::: notes
+Our overarching aim of this scoping review is to identify current
+practices of open collaboration in biomedical and health research.
+:::
 
@@
 1.  Select topic
-
 2.  Workflow
-
 3.  Protocol
-
-4.  S
+4.  Search
+5.  data extraction
+6.  data analysis
+7.  reporting
 
@@
 
-```         
 -   R and Github
@@
 -   Reflections
-```
 
@@
 
-But then came OpenAlex
+But then came [OpenAlex](https://openalex.org/about)
 
@@
 
-See review-stages.qmd
+See
+[review-stages.qmd](https://github.com/science-collective/scoping-review/blob/main/doc/review-stages.qmd)
+
+## Where are we today
+
+Screening abstracts

### 2024-06-07 doc/review-stages.qmd
updated tasks for review stages

@@
     free-hand summary
--   then read a few from each theme to decide on what information to
-    extract
+-   then read a few papers from each theme to decide on what information
+    to extract
 -   then discuss together the themes to group by and information to
     extract
--   then we follow what we agreed on
+
+## Data extraction
+
+-   we make a data extraction template
+-   extract data and read the papers
 

### 2024-07-03 R/abstract-review.R
feat: :sparkles: add functions to get agreed and disagreed abstracts

@@ -25,3 +25,21 @@ read_abstract_reviews <- function(path) {
   abstract_reviews |>
     rlang::set_names(reviewers)
 }
+
+get_agreed_on_abstracts <- function(abstract_list) {
+  stopifnot(is.list(abstract_list))
+  abstract_list |>
+    purrr::reduce(\(df1, df2) {
+      dplyr::inner_join(df1, df2, by = dplyr::join_by(id, title, publication_date, doi, abstract))
+    })
+}
+
+get_disagreed_on_abstracts <- function(abstract_list, agreed_on_abstracts) {
+  stopifnot(is.list(abstract_list))
+  abstract_list |>
+    purrr::map(\(df) dplyr::anti_join(df, agreed_on_abstracts,
+      by = dplyr::join_by(id, title, publication_date, doi, abstract)
+    )) |>
+    purrr::list_rbind() |>
+    dplyr::distinct()
+}

### 2024-07-03 doc/review-stages.qmd
docs: :memo: update review stages file with what we kept, etc

@@
 targets::tar_config_set(store = here("_targets"))
+source(here::here("R/abstract-review.R"))
 ```
@@
 
-```{r tbl-title-disagreements}
+```{r tbl-titles-disagreements}
 #| tbl-cap: "Article titles **not** kept between all reviewers during the title screening stage."
@@
 #| message: false
-#| tbl-cap: "Number of articles each reviewer kept after the second screening of the abstracts."
+#| tbl-cap: "Number of articles each reviewer kept after the second screening of the articles."
 targets::tar_read(abstracts_kept) |> 
@@
   knitr::kable()
+```
 
-# targets::tar_read(abstracts_kept) |> 
-#   select("Article titles" = title) |>
-#   knitr::kable()
+Based on the abstract review, we want to know how many of these titles
+we all agreed on between the three reviewers:
+
+```{r}
+common_abstracts <- targets::tar_read(abstracts_agreed_on)
+```
+
+We seemed to agree on `r nrow(common_abstracts)` abstracts, with the
+full article list shown in @tbl-abstracts-agreements.
+
+```{r tbl-abstracts-agreements}
+#| tbl-cap: !expr glue::glue("The {nrow(common_abstracts)} article abstracts we all agreed on and kept during the abstract screening stage.")
+targets::tar_read(abstracts_agreed_on) |>
+  select("Article titles" = title) |>
+  knitr::kable()
+```
+
+One person will review the titles and flag any paper that might be
+relevant but are not in agreement to keep.
+
+```{r tbl-abstracts-disagreements}
+#| tbl-cap: "Article abstracts **not** kept between all reviewers during the title screening stage."
+targets::tar_read(abstracts_disagreed_on) |>
+  select("Article titles" = title) |>
+  knitr::kable()
+```
+
+Like with the title review, we saved a new csv file with all the
+disagreements and then made a copy of that list in the file
+`resolved.csv`. This file contains some articles that we disagreed on
+but that were briefly reviewed by one reviewer, discussed, and included
+in the end.
+
+The abstracts we agreed on were:
+
+```{r}
+#| message: false
+#| tbl-cap: "Article abstracts we agreed to keep from the disagreement list."
+targets::tar_read(abstracts_resolved_path) |>
+  read_abstract_yaml() |>
+  select("Article title" = title) |>
+  knitr::kable()
+```
+
+The final list of titles we selected, between the agreed on ones as well
+as the resolved ones, are:
+
+```{r}
+#| message: false
+#| tbl-cap: "Article abstracts we reviewed and selected to continue to final article reviewing."
+targets::tar_read(abstracts_selected) |>
+  select("Article title" = title) |>
+  knitr::kable()
 ```

### 2024-07-03 doc/reviews/daniel.qmd

---
title: 'Full Article Review'
---

# Open and reproducible neuroimaging: From study inception to publication

- File: data/review/fulltext/oa-id-W4295290221.pdf
- DOI: https://doi.org/10.1016/j.neuroimage.2022.119623
- OpenAlex ID: https://openalex.org/W4295290221

<!-- Write your notes down here -->

# Ten simple rules for helping newcomers become contributors to open projects

- File: data/review/fulltext/oa-id-W2972809368.pdf
- DOI: https://doi.org/10.1371/journal.pcbi.1007296
- OpenAlex ID: https://openalex.org/W2972809368

<!-- Write your notes down here -->

# Collaborative open science as a way to reproducibility and new insights in primate cognition research

- File: data/review/fulltext/oa-id-W4251805646.pdf
- DOI: https://doi.org/10.31234/osf.io/8w7zd
- OpenAlex ID: https://openalex.org/W4251805646

<!-- Write your notes down here -->

# Promoting FAIR Data Through Community-driven Agile Design: the Open Data Commons for Spinal Cord Injury (odc-sci.org)

- File: data/review/fulltext/oa-id-W3188722327.pdf
- DOI: https://doi.org/10.1007/s12021-021-09533-8
- OpenAlex ID: https://openalex.org/W3188722327

<!-- Write your notes down here -->

# UKRN Open Research Training Resources and Priorities Working Paper

- File: data/review/fulltext/oa-id-W4372403418.pdf
- DOI: https://doi.org/10.31219/osf.io/s2f6k
- OpenAlex ID: https://openalex.org/W4372403418

<!-- Write your notes down here -->

# Eleven Strategies for Making Reproducible Research and Open Science Training the Norm at Research Institutions

- File: data/review/fulltext/oa-id-W4378611187.pdf
- DOI: https://doi.org/10.31219/osf.io/kcvra
- OpenAlex ID: https://openalex.org/W4378611187

<!-- Write your notes down here -->

# Collaboration and Open Science Initiatives in Primate Research

- File: data/review/fulltext/oa-id-W3183365357.pdf
- DOI: https://doi.org/10.31219/osf.io/7c93a
- OpenAlex ID: https://openalex.org/W3183365357

<!-- Write your notes down here -->

# Open and reproducible practices in developmental psychology research: The workflow of the WomCogDev lab as an example

- File: data/review/fulltext/oa-id-W4229452124.pdf
- DOI: https://doi.org/10.31234/osf.io/73bwu
- OpenAlex ID: https://openalex.org/W4229452124

<!-- Write your notes down here -->

# Accelerating addiction research via Open Science and Team Science

- File: data/review/fulltext/oa-id-W4383376256.pdf
- DOI: https://doi.org/10.31234/osf.io/pbkrx
- OpenAlex ID: https://openalex.org/W4383376256

<!-- Write your notes down here -->

# Ten strategies to foster open science in psychology and beyond

- File: data/review/fulltext/oa-id-W4281886503.pdf
- DOI: https://doi.org/10.31234/osf.io/c38a2
- OpenAlex ID: https://openalex.org/W4281886503

<!-- Write your notes down here -->

# Open and collaborative tools for disaster management and risk reduction

- File: data/review/fulltext/oa-id-W4303191041.pdf
- DOI: https://doi.org/10.36335/vnjhm.2022(12).33-38
- OpenAlex ID: https://openalex.org/W4303191041

<!-- Write your notes down here -->

# UKRN ORCC Primer on Working in Open Research

- File: data/review/fulltext/oa-id-W4386723394.pdf
- DOI: https://doi.org/10.31219/osf.io/346hr
- OpenAlex ID: https://openalex.org/W4386723394

<!-- Write your notes down here -->

# Lessons Learned: A Neuroimaging Research Center’s Transition to Open and Reproducible Science

- File: data/review/fulltext/oa-id-W4283836446.pdf
- DOI: https://doi.org/10.31219/osf.io/fe74t
- OpenAlex ID: https://openalex.org/W4283836446

<!-- Write your notes down here -->

### 2024-07-05 _targets.R
fix: ops an extra comma

@@ -180,7 +180,7 @@ list(
       dplyr::rename(path = pdf_proj_path) |>
       create_fulltext_review_template(reviewers),
     format = "file"
-  ),
+  )
   # Render report -----------------------------------------------------------
   # TODO: there is an error and I don't know why.
   # tar_quarto(

### 2024-07-05 R/fulltext-review.R
refactor: update the template for the paper review sections

@@ -15,7 +15,26 @@ create_fulltext_review_template <- function(data, reviewers) {
     - DOI: {doi}
     - OpenAlex ID: {id}
 
-    <!-- Write your notes down here -->
+    ## General themes
+
+    ::: content-hidden
+    Look for what the paper is generally about and some basic overall themes and
+    topics in the paper.
+    :::
+
+    ## Type of paper
+
+    ::: content-hidden
+    Is it a guide, community-building, an example of a workflow, etc.
+    :::
+
+    ## Other notes
+
+    ::: content-hidden
+    What we found was interesting or what we'd like to share, discuss, or
+    present in the main scoping review paper.
+    :::
+
 
     "
 

### 2024-07-05 doc/reviews/luke.qmd
chore: recreated the docs for reviewing

--- 2024-07-03 doc/reviews/daniel.qmd
@@
 
-<!-- Write your notes down here -->
+## General themes
+
+::: content-hidden
+Look for what the paper is generally about and some basic overall themes and
+topics in the paper.
+:::
+
+## Type of paper
+
+::: content-hidden
+Is it a guide, community-building, an example of a workflow, etc.
+:::
+
+## Other notes
+
+::: content-hidden
+What we found was interesting or what we'd like to share, discuss, or
+present in the main scoping review paper.
+:::
 
@@
 
-<!-- Write your notes down here -->
+## General themes
+
+::: content-hidden
+Look for what the paper is generally about and some basic overall themes and
+topics in the paper.
+:::
+
+## Type of paper
+
+::: content-hidden
+Is it a guide, community-building, an example of a workflow, etc.
+:::
+
+## Other notes
+
+::: content-hidden
+What we found was interesting or what we'd like to share, discuss, or
+present in the main scoping review paper.
+:::

### 2024-08-06 doc/reviews/daniel.qmd
Update daniel.qmd

@@
 
-<!-- Write your notes down here -->
+## General themes
+
+::: content-hidden
+Look for what the paper is generally about and some basic overall themes and
+topics in the paper.
+:::
+
+Tools to use.
+
+## Type of paper
+
+::: content-hidden
+Is it a guide, community-building, an example of a workflow, etc.
+:::
+
+- example
+- guide
+
+## Other notes
+
+::: content-hidden
+What we found was interesting or what we'd like to share, discuss, or
+present in the main scoping review paper.
+:::
+
+This paper is not much about open collaboration but more about which tools to use for open and reproducible research from start to finish of a project.
 
@@
 
-<!-- Write your notes down here -->
+## General themes
+
+::: content-hidden
+Look for what the paper is generally about and some basic overall themes and
+topics in the paper.
+:::
+
+- community building
+- social rules
+- organization around the collaboration
+- new comers
+
+## Type of paper
+
+::: content-hidden
+Is it a guide, community-building, an example of a workflow, etc.
+:::
+
+- guide
+
+## Other notes
+
+::: content-hidden
+What we found was interesting or what we'd like to share, discuss, or
+present in the main scoping review paper.
+:::
+
+- Focus on building community: 1: be welcoming, 3. make governance explicit, 6. Develop forms of legitimate peripheral participation, 7. Make it easy for newcomers to get started.
 
@@
 
-<!-- Write your notes down here -->
+## General themes
+
+::: content-hidden
+Look for what the paper is generally about and some basic overall themes and
+topics in the paper.
+:::
+
+- practical setup of collaboration
+
+## Type of paper
+
+::: content-hidden
+Is it a guide, community-building, an example of a workflow, etc.
+:::
+
+- example
+
+## Other notes
+
+::: content-hidden
+What we found was interesting or what we'd like to share, discuss, or
+present in the main scoping review paper.
+:::
+
+Focus on large-scale collaboration in psychology, because of a main challenge of small samples sizes.
+
+Project started in connection with a conference.
+First paper was a pilot.
+Main aim of the project is to provide infrastructure for latge-scale collaboration.
+Used mailing list to share information, then slack for discussions.
+Use Google docs for writing and documentation and github for code and data.
+Data analysis plans pre-registered at OSF.
+Have a website - good for newcomers and sharing info.
+Topic for research selected through voting.
+After organizing the data, they had a modelling challenge.
+Also discuss challenges.
+Main one was how to make decisions.
+Leadership team preferable.
+Also have author guidelines.
 
@@
 
-<!-- Write your notes down here -->
+## General themes
+
+::: content-hidden
+Look for what the paper is generally about and some basic overall themes and
+topics in the paper.
+:::
+
+- data sharing
+
+## Type of paper
+
+::: content-hidden
+Is it a guide, community-building, an example of a workflow, etc.
+:::
+
+- example
+
+## Other notes
+
+::: content-hidden
+What we found was interesting or what we'd like to share, discuss, or
+present in the main scoping review paper.
+:::
+
+- this paper is mostly about a database for sharing spinal injusry data. There are some points for how to improve sharing but not much about open collaboration
+- open data commons for spinal injury
+- Studies based on game theory suggest that data sharing might be beneficial if a collaborative approach is taken and data sharing is embraced as a community rather than by individuals
+- key events for the collaboration to be possible: - introduction of FAIR principles, - update from funders, funding given to specific projects
+- Open Data Commons for SCI (ODC-SCI, odc-sci.org), a platform to share tabular data of research in the field of spinal cord injury
+- Ain of the paper: to illustrate how members of research communities can work together toward the development of dedicated data sharing initiatives under the umbrella of FAIR
+- clearly highlighted the value of the massive demonstration/work for beta testing the site to reveal unforeseen problems
+- Moreover, participants pointed out the need for improving self-explanatory tutorials and help materials that would facilitate the learning experience for those who could not attend the workshop
+- “Registered users can request to become ODC-SCI Community members with further approval by the Leadership team.” The most permissive account type is becoming an ODC-SCI Community member associated to an ODC-SCI lab, known as a Lab member
 

### 2024-08-14 doc/reviews/luke.qmd
started reviewing some of the papers

@@
 ::: content-hidden
-Look for what the paper is generally about and some basic overall themes and
-topics in the paper.
+Look for what the paper is generally about and some basic overall themes
+and topics in the paper.
 :::
@@
 ::: content-hidden
-Look for what the paper is generally about and some basic overall themes and
-topics in the paper.
+Look for what the paper is generally about and some basic overall themes
+and topics in the paper.
 :::
+
+-   Onboarding
+-   Documentation
+-   Contributing
+-   Centralization
+-   Knowledge management
+-   Communication
+-   Guidelines
 
@@
 
+-   Guide
+
 ## Other notes
@@
 :::
+
+This paper seems more targeted to general open projects and not strictly
+about open collaboration within research. However, it is useful
+information contained within on some general steps to take to encourage
+and continue collaboration in open projects and in as open ways as
+possible.
+
+The rules that are more relevant to open collaboration are:
+
+1.  Be welcoming: Example, recognize when newcomers join and have an
+    onboarding process or document.
+2.  Make governance explicit: Example, how are decisions made?
+3.  Keep knowledge up to date and findable: Example, where are the
+    contributing guidelines?
+4.  Have a code of conduct that you enforce: Example, what are the
+    guidelines for communication and what happens if someone breaks
+    them?
+5.  Make it easy for contributors to get started: Example, like the
+    being welcome, have an onboarding document and/or roadmap for the
+    projects work.
+6.  Acknowledge all contributions: Any contribution can be meaningful if
+    it helps further the goal of the project.
 
@@
 ::: content-hidden
-Look for what the paper is generally about and some basic overall themes and
-topics in the paper.
+Look for what the paper is generally about and some basic overall themes
+and topics in the paper.
 :::
+
+-   Data infrastructure
+-   FAIR data
+-   Case study
+-   Agile design
+-   Templates
+-   Examples
+-   Strategies
+-   Software development
 
@@
 
+-   Case study
+-   Example workflow
+
 ## Other notes
@@
 :::
+
+-   While the project's output is a data sharing platform, the process
+    to get there required a high level of collaboration.
+-   Seems to use GitHub to at least build the website.
+-   Building up an open collaboration project takes years of continued
+    work and effort.
+-   Took a multi-staged approach to establishing the group/community.
+    -   At each stage, it was slowly about introducing the concepts to a
+        broader and broader audience and getting feedback all along the
+        way.
+-   Development follows principles of agile software development by
+    getting requirements from users, designing and developing those
+    requirements, seeking feedback from users on what was developed, and
+    testing the developed features.
+-   Use of the iterative development helped them identify and respond to
+    issues that came up. This is something that could be something that
+    non-software projects could use to help with collaboration and
+    maintaining momentum and motivation.
 
@@
 ::: content-hidden
-Look for what the paper is generally about and some basic overall themes and
-topics in the paper.
+Look for what the paper is generally about and some basic overall themes
+and topics in the paper.
 :::
+
+-   Large-scale collaboration
+-   Data aggregation
+-   Replications
+-   Limited resources
+-   Strategies
+-   Case study
+-   Communities of practice
 
@@
 
+-   Example workflow
+-   Community building
+-   Case study
+
 ## Other notes
@@
 :::
+
+-   Mostly an example of what they did and why
+-   Faced with limited resources and small sample sizes, but
+    wanting/needing more to make results generalizable, they put
+    together this collaboration project.
+-   Outlines benefits of this collaboration, such as reducing the
+    efforts of individual researchers by distributing workload,
+    resources, and knowledge sharing/creation/management.
+-   Challenges to this collaboration are less papers, lower ability to
+    cover more topics, less freedom of control and direction at the
+    individual researcher level (since they are part of a larger group
+    and need to have a consensus on a topic or standards of practice),
+    higher level of rules and processes for dealing with researchers who
+    try to take advantage of the community for their own benefit, as
+    well as how to decide on authorship/contributorship for scientific
+    publications.
+    -   A big challenge to these collaborations is sources of funding.
+        Who pays for whose salary? How are funds distributed?
+-   Argues that any large-scale collaboration needs to use open
+    practices by default.
+-   Something to consider when building large-scale collaboration is its
+    continuation. If its started by one or a few people and with
+    dedicated funding for it, what happens if that person or people
+    leave or move on to other things? Or when the funding ends? These
+    need to be considered at the start.
+-   The ManyPrimates use GitHub, at least to host their website with
+    some general documentation and guidelines, as well as some analysis
+    code and data for some papers they've published.
+-   The ManyPrimates project also set some basic standards for project
+    file and folder structure, for pre-registering the study, etc.
 

### 2024-08-15 doc/reviews/daniel.qmd
clean: the notes taken so far

@@
 
-::: content-hidden
-Look for what the paper is generally about and some basic overall themes and
-topics in the paper.
-:::
-
 Tools to use.
@@
 ## Type of paper
-
-::: content-hidden
-Is it a guide, community-building, an example of a workflow, etc.
-:::
 
@@
 
-::: content-hidden
-What we found was interesting or what we'd like to share, discuss, or
-present in the main scoping review paper.
-:::
-
-This paper is not much about open collaboration but more about which tools to use for open and reproducible research from start to finish of a project.
+This paper is not much about open collaboration but more about which
+tools to use for open and reproducible research from start to finish of
+a project.
 
@@
 
-::: content-hidden
-Look for what the paper is generally about and some basic overall themes and
-topics in the paper.
-:::
-
 -   community building
@@
 
-::: content-hidden
-Is it a guide, community-building, an example of a workflow, etc.
-:::
-
 -   guide
@@
 
-::: content-hidden
-What we found was interesting or what we'd like to share, discuss, or
-present in the main scoping review paper.
-:::
-
-- Focus on building community: 1: be welcoming, 3. make governance explicit, 6. Develop forms of legitimate peripheral participation, 7. Make it easy for newcomers to get started.
+-   Focus on building community: 1: be welcoming, 3. make governance
+    explicit, 6. Develop forms of legitimate peripheral
+    participation, 7. Make it easy for newcomers to get started.
 
@@
 
-::: content-hidden
-Look for what the paper is generally about and some basic overall themes and
-topics in the paper.
-:::
-
 -   practical setup of collaboration
@@
 
-::: content-hidden
-What we found was interesting or what we'd like to share, discuss, or
-present in the main scoping review paper.
-:::
+Focus on large-scale collaboration in psychology, because of a main
+challenge of small samples sizes.
 
-Focus on large-scale collaboration in psychology, because of a main challenge of small samples sizes.
-
-Project started in connection with a conference.
-First paper was a pilot.
-Main aim of the project is to provide infrastructure for latge-scale collaboration.
-Used mailing list to share information, then slack for discussions.
-Use Google docs for writing and documentation and github for code and data.
-Data analysis plans pre-registered at OSF.
-Have a website - good for newcomers and sharing info.
-Topic for research selected through voting.
-After organizing the data, they had a modelling challenge.
-Also discuss challenges.
-Main one was how to make decisions.
-Leadership team preferable.
-Also have author guidelines.
+Project started in connection with a conference. First paper was a
+pilot. Main aim of the project is to provide infrastructure for
+latge-scale collaboration. Used mailing list to share information, then
+slack for discussions. Use Google docs for writing and documentation and
+github for code and data. Data analysis plans pre-registered at OSF.
+Have a website - good for newcomers and sharing info. Topic for research
+selected through voting. After organizing the data, they had a modelling
+challenge. Also discuss challenges. Main one was how to make decisions.
+Leadership team preferable. Also have author guidelines.
 
@@
 
-::: content-hidden
-Look for what the paper is generally about and some basic overall themes and
-topics in the paper.
-:::
-
 -   data sharing
@@
 
-::: content-hidden
-What we found was interesting or what we'd like to share, discuss, or
-present in the main scoping review paper.
-:::
-
-- this paper is mostly about a database for sharing spinal injusry data. There are some points for how to improve sharing but not much about open collaboration
+-   this paper is mostly about a database for sharing spinal injusry
+    data. There are some points for how to improve sharing but not much
+    about open collaboration
 -   open data commons for spinal injury
-- Studies based on game theory suggest that data sharing might be beneficial if a collaborative approach is taken and data sharing is embraced as a community rather than by individuals
-- key events for the collaboration to be possible: - introduction of FAIR principles, - update from funders, funding given to specific projects
-- Open Data Commons for SCI (ODC-SCI, odc-sci.org), a platform to share tabular data of research in the field of spinal cord injury
-- Ain of the paper: to illustrate how members of research communities can work together toward the development of dedicated data sharing initiatives under the umbrella of FAIR
-- clearly highlighted the value of the massive demonstration/work for beta testing the site to reveal unforeseen problems
-- Moreover, participants pointed out the need for improving self-explanatory tutorials and help materials that would facilitate the learning experience for those who could not attend the workshop
-- “Registered users can request to become ODC-SCI Community members with further approval by the Leadership team.” The most permissive account type is becoming an ODC-SCI Community member associated to an ODC-SCI lab, known as a Lab member
+-   Studies based on game theory suggest that data sharing might be
+    beneficial if a collaborative approach is taken and data sharing is
+    embraced as a community rather than by individuals
+-   key events for the collaboration to be possible: - introduction of
+    FAIR principles, - update from funders, funding given to specific
+    projects
+-   Open Data Commons for SCI (ODC-SCI, odc-sci.org), a platform to
+    share tabular data of research in the field of spinal cord injury
+-   Ain of the paper: to illustrate how members of research communities
+    can work together toward the development of dedicated data sharing
+    initiatives under the umbrella of FAIR
+-   clearly highlighted the value of the massive demonstration/work for
+    beta testing the site to reveal unforeseen problems
+-   Moreover, participants pointed out the need for improving
+    self-explanatory tutorials and help materials that would facilitate
+    the learning experience for those who could not attend the workshop
+-   "Registered users can request to become ODC-SCI Community members
+    with further approval by the Leadership team." The most permissive
+    account type is becoming an ODC-SCI Community member associated to
+    an ODC-SCI lab, known as a Lab member
 
@@
 
-# Lessons Learned: A Neuroimaging Research Center’s Transition to Open and Reproducible Science
+# Lessons Learned: A Neuroimaging Research Center's Transition to Open and Reproducible Science
 

### 2024-10-20 doc/reviews/daniel.qmd

--- 2024-07-03 doc/reviews/daniel.qmd
@@
 
-<!-- Write your notes down here -->
+## General themes
+
+Tools to use.
+
+## Type of paper
+
+-   example
+-   guide
+
+## Other notes
+
+-   This paper is not much about open collaboration but more about which
+    tools to use for open and reproducible research from start to finish
+    of a project.
 
@@
 
-<!-- Write your notes down here -->
+## General themes
+
+-   community building
+-   social rules
+-   organization around the collaboration
+-   new comers
+
+## Type of paper
+
+-   guide
+
+## Other notes
+
+-   Focus on building community: 1: be welcoming, 3. make governance
+    explicit, 6. Develop forms of legitimate peripheral
+    participation, 7. Make it easy for newcomers to get started.
 
@@
 
-<!-- Write your notes down here -->
+## General themes
+
+-   practical setup of collaboration
+
+## Type of paper
+
+-   example
+
+## Other notes
+
+-   Focus on large-scale collaboration in psychology, because of a main
+    challenge of small samples sizes.
+-   Project started in connection with a conference. First paper was a
+    pilot. Main aim of the project is to provide infrastructure for
+    large-scale collaboration. Used mailing list to share information,
+    then slack for discussions. Use Google docs for writing and
+    documentation and github for code and data. Data analysis plans
+    pre-registered at OSF.
+-   Have a website - good for newcomers and sharing info. Topic for
+    research selected through voting. After organizing the data, they
+    had a modelling challenge. Also discuss challenges. Main one was how
+    to make decisions.
+-   Leadership team preferable. Also have author guidelines.
 
@@
 
-<!-- Write your notes down here -->
+## General themes
+
+-   data sharing
+
+## Type of paper
+
+-   example
+
+## Other notes
+
+-   this paper is mostly about a database for sharing spinal injury
+    data. There are some points for how to improve sharing but not much
+    about open collaboration
+-   open data commons for spinal injury
+-   Studies based on game theory suggest that data sharing might be
+    beneficial if a collaborative approach is taken and data sharing is
+    embraced as a community rather than by individuals
+-   key events for the collaboration to be possible: - introduction of
+    FAIR principles, update from funders, funding given to specific
+    projects
+-   Open Data Commons for SCI (ODC-SCI, odc-sci.org), a platform to
+    share tabular data of research in the field of spinal cord injury
+-   Aim of the paper: to illustrate how members of research communities
+    can work together toward the development of dedicated data sharing
+    initiatives under the umbrella of FAIR
+-   clearly highlighted the value of the massive demonstration/work for
+    beta testing the site to reveal unforeseen problems
+-   Moreover, participants pointed out the need for improving
+    self-explanatory tutorials and help materials that would facilitate
+    the learning experience for those who could not attend the workshop
+-   "Registered users can request to become ODC-SCI Community members
+    with further approval by the Leadership team." The most permissive
+    account type is becoming an ODC-SCI Community member associated to
+    an ODC-SCI lab, known as a Lab member
 
@@
 
-<!-- Write your notes down here -->
+## General themes
+
+-   recommendations
+-   training
+
+## Type of paper
+
+-   survey
+
+## Other notes
+
+-   aim of the survey is to inform training priorities for open science
+-   research cycle: planning, conducting, analysing, disseminating
+-   Planning: team science guides, research co-production
+-   Conducting: open research testing platforms, electronic
+-   Most resources focus on the planning and analysing stage
+-   Many resources were only for internal use
+-   Very few ressources for open collaboration, none were open and they
+    were valued poorly compared to other practices
 
@@
 
-<!-- Write your notes down here -->
+## General themes
+
+-   training
+-   recommendations
+
+## Type of paper
+
+-   survey
+
+## Other notes
+
+-   Strategy 5 - Perform replication or meta-research studies as course
+    projects: As the class collaborates on one project, participants
+    also build skills for collaborative team science and gain experience
+    leading small teams.
+-   Tips for Strategy 5 - Perform replication or meta-research studies
+    as course projects: Carefully define the scope of the project,
+    Ensure that you have adequate support
+-   build communities: Foster accessible discussions (Consider running
+    "beginner" and "advanced" community meetings), Build communities:
+    Organize regular meetings
 
@@
 
-<!-- Write your notes down here -->
+## General themes
+
+-   large-scale collaboration
+
+## Type of paper
+
+-   example
+
+## Other notes
+
+-   for them, making the large-scale collaboration was about overcoming
+    challenges related to their research
+-   Large-scale collaborations can help to set standards in the field by
+    following good scientific practice of replications, data reporting,
+    and pre-registration
+-   Low entry barriers and the various ways in which a scientist can be
+    involved in a large-scale collaboration (design, data collection,
+    analysis, manuscript writing) offer a multitude of possibilities for
+    researchers in different stages of their careers
+-   These types of projects also present valuable opportunities to make
+    new contacts, initiate new collaborations, and connect with a bigger
+    community on a regular basis
+-   Large-scale collaborations represent a wholesale shift in scientific
+    practice, from how research questions are chosen and approached, to
+    how research is logistically coordinated and how credit for research
+    efforts is allocated
+-   large-scale collaborative projects may reduce the diversity of
+    topics by covering them at a scale that would be unfeasible by
+    independent research groups
+-   Agreeing on project selection, study design, stimuli, analysis plan,
+    and findings' interpretation is not easy in big groups. (...)
+    research questions are selected democratically - proposals for
+    projects are submitted and members vote to select which projects
+    will be carried out.
+-   Large-scale projects also have to develop authorship guidelines,
+    which specify the minimal conditions that one person has to fulfill
+    to qualify for authorship
+-   none of the large-scale consortia in psychology have a steady source
+    of financing
+-   setup the project to be long-lasting and build an infrastructure
+    that they piloted
+-   task forces within the project prepared different materials they
+    then uploaded to github and pre-register
 
@@
 
-<!-- Write your notes down here -->
+## General themes
+
+-   guide
+-   workflow
+
+## Type of paper
+
+-   guide
+
+## Other notes
+
+-   Nice figure with workflow
+-   Resources: lab meetings, slack, trello, OSF repository
+-   They setup a clear structure for how to conduct the research - how a
+    project is supposed to work
+-   Open Science is never static, as each of us continues to incorporate
+    more and more practices into our repertoires over time
 
@@
 
-<!-- Write your notes down here -->
+## General themes
+
+-   team science
+-   example
+
+## Type of paper
+
+-   guide
+
+## Other notes
+
+-   mentions registered reports that are peer reviewer twice
+-   recommend sharing on OSF
+-   synthpop package in R creates a synthetic dataset with same
+    statistical properties
+-   large-scale collaboration is recommended to improve generalizability
+    and power.
+-   they provide an example of an individual-participant meta-analysis
+    they conducted
+-   As part of this process, we made several decisions as a group (via
+    an anonymous poll), such as which smallest effect size of interest
+    to preregister and to which journal to submit the paper
+-   Barriers: within our current scientific culture, there are few
+    incentives to work in large teams, all large-scale collaborations
+    need leadership
 
@@
 
-<!-- Write your notes down here -->
+## General themes
+
+-   tools
+-   large-scale collaboration
+
+## Type of paper
+
+-   guide
+
+## Other notes
+
+-   Strategy 6: Collaborate with Others Using Open Tools
+-   can get started by writing in markdown/quarto, using github
+-   Strategy 7: Develop Networks of Open Collaboration
+-   Big Team Science has advantages for research, as it allows
+    investigators to access more resources, work with greater sample
+    sizes, take advantage of the expertise of a larger team of
+    researchers in areas such as data analysis, and distribute work more
+    efficiently
+-   Participating in these large-scale projects is not easy and calls on
+    researchers to develop specific standards and guidelines that ensure
+    effective communication among collaborators and enable projects to
+    develop coherently and cohesively
+-   there is still a long way to go before open science becomes the
+    by-design and by-default model for scientific research
 
@@
 
-<!-- Write your notes down here -->
+## General themes
+
+-   could not access
+
+::: content-hidden
+Look for what the paper is generally about and some basic overall themes
+and topics in the paper.
+:::
+
+## Type of paper
+
+::: content-hidden
+Is it a guide, community-building, an example of a workflow, etc.
+:::
+
+## Other notes
+
+::: content-hidden
+What we found was interesting or what we'd like to share, discuss, or
+present in the main scoping review paper.
+:::
 
@@
 
-<!-- Write your notes down here -->
+## General themes
 
-# Lessons Learned: A Neuroimaging Research Center’s Transition to Open and Reproducible Science
+-   not relevant. Is about working in open research not performing it
+
+::: content-hidden
+Look for what the paper is generally about and some basic overall themes
+and topics in the paper.
+:::
+
+## Type of paper
+
+::: content-hidden
+Is it a guide, community-building, an example of a workflow, etc.
+:::
+
+## Other notes
+
+::: content-hidden
+What we found was interesting or what we'd like to share, discuss, or
+present in the main scoping review paper.
+:::
+
+# Lessons Learned: A Neuroimaging Research Center's Transition to Open and Reproducible Science
 
@@
 
-<!-- Write your notes down here -->
+## General themes
+
+-   workflow
+
+## Type of paper
+
+-   guide
+
+## Other notes
+
+-   also nice figure of workflow including open science practices in the
+    workflow
+-   use OSF for registering protocols
+-   focus on open software like R and Python, git and github
+-   this is a practical guide to make a transition, very little
+    mentioned specifically about collaboration or team work

### 2024-10-21 doc/reviews/themes.qmd
Made a file with identified themes with notes from individial papers

---
title: 'Analysis of themes'
---

# Tools

-   Open and reproducible neuroimaging: From study inception to
    publication

    -   study inception, planning, and ethics: OSF pre-registration,
        clinicaltrials.gov, aspredicted

    -   data processing and analysis: git, github, gitlab, etc

    -   many others

-   Collaborative open science as a way to reproducibility and new
    insights in primate cognition research

    -   Used mailing list to share information, then slack for
        discussions

    -   Use Google docs for writing and documentation

    -   Github for code and data

    -   Data analysis plans pre-registered at OSF

    -   Have a website - good for newcomers and sharing info

-   Open and reproducible practices in developmental psychology
    research: The workflow of the WomCogDev lab as an example

    -   Resources: lab meetings, slack, trello, OSF repository

-   Accelerating addiction research via Open Science and Team Science

    -   recommend sharing on OSF

    -   synthpop package in R creates a synthetic dataset with same
        statistical properties

-   Ten strategies to foster open science in psychology and beyond

    -   can get started by writing in markdown/quarto, using github

-   Lessons Learned: A Neuroimaging Research Center's Transition to Open
    and Reproducible Science

    -   use OSF for registering protocols

    -   focus on open software like R and Python, git and github

# Organization

-   Open and reproducible neuroimaging: From study inception to
    publication

    -   publishing Code of Conduct for collaborative projects is one
        practice that helps ensure a more welcoming and inclusive space
        for everyone regardless of background or identity

-   Ten simple rules for helping newcomers become contributors to open
    projects

    -   be welcoming

    -   make governance explicit

    -   develop forms of legitimate peripheral participation

    -   make it easy for newcomers to get started

-   Collaborative open science as a way to reproducibility and new
    insights in primate cognition research

    -   topic for research selected through voting

    -   also discuss challenges. Main one was how to make decisions

    -   leadership team preferable

    -   also have author guidelines.

-   Promoting FAIR Data Through Community-driven Agile Design: the Open
    Data Commons for Spinal Cord Injury (odc-sci.org)

    -   key events for the collaboration to be possible: - introduction
        of FAIR principles, update from funders, funding given to
        specific projects

    -   moreover, participants pointed out the need for improving
        self-explanatory tutorials and help materials that would
        facilitate the learning experience for those who could not
        attend the workshop

    -   registered users can request to become ODC-SCI Community members
        with further approval by the Leadership team.

-   Eleven Strategies for Making Reproducible Research and Open Science
    Training the Norm at Research Institutions

    -   perform replication or meta-research studies as course projects:
        Carefully define the scope of the project, Ensure that you have
        adequate support

    -   build communities: Foster accessible discussions (Consider
        running "beginner" and "advanced" community meetings)

    -   build communities: Organize regular meetings

-   Collaboration and Open Science Initiatives in Primate Research

    -   Agreeing on project selection, study design, stimuli, analysis
        plan, and findings' interpretation is not easy in big groups.
        (...) research questions are selected democratically - proposals
        for projects are submitted and members vote to select which
        projects will be carried out.

    -   Large-scale projects also have to develop authorship guidelines,
        which specify the minimal conditions that one person has to
        fulfill to qualify for authorship

    -   task forces within the project prepared different materials they
        then uploaded to github and pre-register

    -   Low entry barriers and the various ways in which a scientist can
        be involved in a large-scale collaboration (design, data
        collection, analysis, manuscript writing) offer a multitude of
        possibilities for researchers in different stages of their
        careers

-   Accelerating addiction research via Open Science and Team Science

    -   As part of this process, we made several decisions as a group
        (via an anonymous poll), such as which smallest effect size of
        interest to preregister and to which journal to submit the paper

-   Ten strategies to foster open science in psychology and beyond

    -   Participating in these large-scale projects is not easy and
        calls on researchers to develop specific standards and
        guidelines that ensure effective communication among
        collaborators and enable projects to develop coherently and
        cohesively

## Workflow

-   Open and reproducible practices in developmental psychology
    research: The workflow of the WomCogDev lab as an example

    -   They setup a clear structure for how to conduct the research -
        how a project is supposed to work

-   Lessons Learned: A Neuroimaging Research Center's Transition to Open
    and Reproducible Science

    -   also nice figure of workflow including open science practices in
        the workflow

# Training

-   UKRN Open Research Training Resources and Priorities Working Paper

    -   research cycle: planning, conducting, analysing, disseminating

    -   planning: team science guides, research co-production

    -   most resources focus on the planning and analysing stage

    -   very few resources for open collaboration, none were open and
        they were valued poorly compared to other practices

-   Eleven Strategies for Making Reproducible Research and Open Science
    Training the Norm at Research Institutions

    -   perform replication or meta-research studies as course projects:
        As the class collaborates on one project, participants also
        build skills for collaborative team science and gain experience
        leading small teams

# Barriers/limitations for implementation

-   Accelerating addiction research via Open Science and Team Science

    -   Barriers: within our current scientific culture, there are few
        incentives to work in large teams, all large-scale
        collaborations need leadership

# Levels of collaboration

## multi-center

-   Collaboration and Open Science Initiatives in Primate Research

## center

-   Lessons Learned: A Neuroimaging Research Center's Transition to Open
    and Reproducible Science

## lab

-   Open and reproducible practices in developmental psychology
    research: The workflow of the WomCogDev lab as an example

### 2024-10-21 doc/charting/charting_form_template.qmd
made a first draft of a charting form

---
title: 'Charting form template'
---

::: content-hidden
fill in one form per paper. Name the form according to first author and
year like this: "Turoman-2022". Copy-paste the information from the
full-text review below.
:::

# title of publication

-   File:
-   DOI:
-   OpenAlex ID:

## Tools

### Specific tools mentioned - their function - where in the researh process used

::: content-hidden
For instance: "OSF - pre-registration - planning". You can mention
multiple tools. Just make another bullet.

The research process is: planning, conducting, analysing, disseminating.
If a combination write several, if all write "all"
:::

-

## Organizational structure for open collaboration

### Governance

::: content-hidden
For instance: "Develop forms of legitimate peripheral participation."

These are bit of information and recommendations for governance of the
project.
:::

-

### Workflow

::: content-hidden
For instance: "designing the project - preregistration - creating the
experiment - recruitment and data collection - data analysis -
dissemination".

These are overall process highlights
:::

-

## Educational perspectives

### Educational needs

::: content-hidden
For instance: "few resources for open collaboration, none were open and
they were valued poorly compared to other practices"

What does the paper write is the need for education in the field?
:::

## Barriers

### Barriers for open science

::: content-hidden
For instance: "lack of education"

Which barriers do the paper indicate for implementation of open science?
:::

-

### 2024-10-21 R/fulltext-review.R
fix: :bug: forgot to add the `readr::` namespacing

@@ -49,7 +49,7 @@ create_fulltext_review_template <- function(data, reviewers) {
 
   purrr::walk(
     paths,
-    \(path) write_lines(c(header, review_body), path)
+    \(path) readr::write_lines(c(header, review_body), path)
   )
   paths
 }

### 2024-10-21 doc/charting/Alessandroni-2022.qmd

---
title: 'Alessandroni-2022'
---

# Ten strategies to foster open science in psychology and beyond

-   File: data/review/fulltext/oa-id-W4281886503.pdf
-   DOI: https://doi.org/10.31234/osf.io/c38a2
-   OpenAlex ID: https://openalex.org/W4281886503

## Tools

### Specific tools mentioned - their function - where in the researh process used

-   Markdown/quarto - collaborative writing - all
-   Github - version control - all

## Organizational structure for open collaboration

### Governance

-   use open tools for collaboration
-   develop specific standards and guidelines that ensure effective
    communication among collaborators and enable projects to develop
    coherently and cohesively

## Educational perspectives

### Educational needs

-   Introduce open science practices into courses
-   Institutions can create courses in open science practices

## Barriers

### Barriers for open science

-   Incorporating open tools may have a steep learning curve
-   Open science in the curricula vitae of academics must become a
    requirement and not just a nice addition
-   The problem with current incentive structures such as impact factor

### 2024-10-21 doc/charting/Bush-2022.qmd

---
title: 'Bush-2022'
---

# Lessons Learned: A Neuroimaging Research Center's Transition to Open and Reproducible Science

-   File: data/review/fulltext/oa-id-W4283836446.pdf
-   DOI: https://doi.org/10.31219/osf.io/fe74t
-   OpenAlex ID: https://openalex.org/W4283836446

## Tools

### Specific tools mentioned - their function - where in the researh process used

-   Github - open-source code, version control, collaboration -
    analysing
-   Python - open-source programming - analysing
-   R - open-source programming - analysing
-   arXiv/bioRxiv/psyRxiv - preprint sharing - disseminating
-   OpenNeuro - data sharing - disseminating
-   Open Science Framework - preregistration - planning
-   clinicaltrials.gov - preregistration - planning

## Organizational structure for open collaboration

### Governance

### Workflow

-   hypothesis - experiment - data collection - data analysis -
    reporting

## Educational perspectives

### Educational needs

-   people in the organization need to learn additional programming,
    version control, and data management skills and work with unfamiliar
    naming conventions and directory structures mandated by the used
    standards

## Barriers

### Barriers for open science

-   costs of effort to be borne by individuals already engaged in
    challenging, time-consuming work
-   during transition, the research productivity will suffer

### 2024-10-21 doc/charting/Dora-2024.qmd

--- 2024-10-21 doc/charting/charting_form_template.qmd
@@
 ---
-title: 'Charting form template'
+title: 'Dora-2024'
 ---
 
-::: content-hidden
-fill in one form per paper. Name the form according to first author and
-year like this: "Turoman-2022". Copy-paste the information from the
-full-text review below.
-:::
+# Accelerating addiction research via Open Science and Team Science
 
-# title of publication
-
--   File:
--   DOI:
--   OpenAlex ID:
+-   File: data/review/fulltext/oa-id-W4383376256.pdf
+-   DOI: https://doi.org/10.31234/osf.io/pbkrx
+-   OpenAlex ID: https://openalex.org/W4383376256
 
@@
 
--
+-   Used anonymous polls to make critical decisions in a large
+    collaborative project
+-   Important to setup a structure for leadership of the project and
+    that the leadership is held accountable to decisions made
+-   setup a structure to regularly ask for formal and informal feedback
+    from members
 
@@
 
+-   Education in open science needed to increase uptake
+
 ## Barriers
@@
 
--
+-   no open science standards in journals
+-   few opportunities for registered reports
+-   there are few incentives to collaborate in large teams
+-   grants are often given to an individual not a team

### 2024-10-21 doc/reviews/daniel.qmd
small updates on review file

@@
 
-Tools to use.
+-   tools
+-   organization
 
@@
     of a project.
+-   Study inception, planning, and ethics: OSF pre-registration,
+    clinicaltrials.gov, aspredicted
+-   Data processing and analysis: git, github, gitlab, etc
+-   Scientific research can now become more transparent, inclusive and
+    collaborative throughout the research cycle
+-   Publishing Code of Conduct for collaborative projects is one
+    practice that helps ensure a more welcoming and inclusive space for
+    everyone regardless of background or identity
 
@@
 
--   practical setup of collaboration
+-   collaboration structure
+-   tools
+-   organization
 
@@
 -   data sharing
+-   organization
 
@@
 -   open data commons for spinal injury
--   Studies based on game theory suggest that data sharing might be
+-   studies based on game theory suggest that data sharing might be
     beneficial if a collaborative approach is taken and data sharing is
@@
 
--   recommendations
+-   organization
 -   training
@@
 -   survey
+-   recommendations
 
@@
 -   Planning: team science guides, research co-production
--   Conducting: open research testing platforms, electronic
+-   Conducting: open research testing platforms
 -   Most resources focus on the planning and analysing stage
 -   Many resources were only for internal use
--   Very few ressources for open collaboration, none were open and they
+-   Very few resources for open collaboration, none were open and they
     were valued poorly compared to other practices
@@
 -   recommendations
+-   organization
 
@@
 -   large-scale collaboration
+-   organization
+-   tools
 
@@
 
--   guide
+-   tools
 -   workflow
@@
 
--   team science
--   example
+-   organisation
 
@@
 -   guide
+-   example
 
@@
 -   tools
+-   organization
 -   large-scale collaboration
@@
 -   workflow
+-   tools
 

### 2024-10-21 doc/charting/ManyPrimates-2021.qmd
Add files via upload

---
title: 'ManyPrimates-2021'
---

# Collaborative open science as a way to reproducibility and new insights in primate cognition research

-   File: data/review/fulltext/
-   DOI: https://doi.org/10.31234/osf.io/8w7zd
-   OpenAlex ID: W4251805646

## Tools

### Specific tools mentioned - their function - where in the researh process used

-   Github - version control - all
-   Registered reports - help designing analysis to prove specific hypothesis - study design
-   p-curve software - helps avoiding overrepresantation of positive results - 
-   A.P.E.S Wiki - open access platform for standardized research and conservation of the data - they report it as an outcome of large-scale collaboration
-   PRIMatE Research Exchange - platform to exchange data, ideas and protocols - they report it as an outcome of large-scale collaboration

## Organizational structure for open collaboration

### Setting up a network of collaborators

-   ManyPrimates wanted a lasting infrastructure
-   They developed a mailing list where researchers can exchange their ideas and analysis.
-   They developed a twitter (now X) account to disseminate and extend their work to other researchers.

### Setting up the bases for collaboration and a test example to educate people in open sciences

-   They developed ethical guidelines for all collaborators (non-invasive research, always open science, author list)
-   They ran a pilot study that tried replicating analysis on short-term memory with more sample size.
-   They preregistered protocols, created code and hosted data in repositories so that other coworkers can run the analysis systematically.
-   Data was collected.
-   Other workforce merged the data and visualized the results.
-   With this pipeline, they decided to run other analysis. This highlights the importance of a good test study.

## Educational perspectives

-   Large-scale collaboration are a great opportunity for making more researchers get in touch with open science practices.
-   Creating websites like A.P.E.S Wiki or a mailing list creates a network of researchers that can follow similar practices.
-   Replication studies like the mentioned MP1 project on short-term memory can be of great educational value and help set up and infrastructure to promote openness.

## Barriers

### Barriers for open science

-   Pre-registration might neglect innovation due to their rigid structure, but creates very solid results.

### 2024-10-21 doc/charting/Kohrs-2023.qmd
Add files via upload

---
title: 'Khors-2023'
---

# Eleven Strategies for Making Reproducible Research and Open Science Training the Norm at Research Institutions

-   File: data/review/fulltext/
-   DOI: https://doi.org/10.31219/osf.io/kcvra
-   OpenAlex ID: W4378611187

## Tools

### Specific tools mentioned - their function - where in the researh process used

-   Virtual unconference - not a tool per se, but a nice way of networking and sharing ideas - can be used either early to brainstorm and network or later to disseminate ideas
-   COARA - fairer way of assessing research output than impact factors - Not used, just mentioned.
-   Open Science Labs - not a tool per se, but dedicated staff and organizations who works solely to contribute and assist on designing open science - study design, but they can     assist in other stages. other decentralized hubs exist such as FORRT or STEM education hub.
-   SCOSS - application for funding to be able to publish with open science standards - publication.

## Organizational structure for open collaboration

### Systematic changes to promote Open Science

-   Make open science necessary for the curriculum in universities (Munich university as example) and add courses that touches on openness, preregistration, etc.
-   Thesis are required to have open science elements to them. including collaborative thesis
-   Open Science requirements in the curriculum needed to hire individuals.

## Educational perspectives

-   Here education is the central aspect of the structure to build open science the norm in an institution
-   They suggest offering open science courses, but also integreate open science in other courses
-   They also suggest that hand-on training is the best way to learn, some ways of doing this is by making courses more interactive or have research groups go on open science        courses. Some of the courses or examples can be replications or collaborative thesis.
-   An essential part of education is allowing for spaces where researchers can work, such as journal clubs, resource hubs or hackathons.

## Barriers

### Barriers for open science

-   Allocation for resources.
-   In general all the things required to change expressed in the topics above: open science not being part of the standard curriculum of universities or a required skill for        when hiring. The lack of spaces and infrastructure to network and collaborate. Innovative papers being preferred by mainstream media than replications.

### 2024-10-21 doc/reviews/luke.qmd
docs: read through more papers

@@
 
+-   Systematic review
+-   Large-scale collaboration
+-   Large-scale infrastructure
+
 ## Type of paper
@@
 :::
+
+-   Review
+-   Example workflow
 
@@
 :::
+
+-   This paper wasn't the most relevant, as it didn't go into as much
+    detail as we might like, even though it was describing exactly what
+    we are looking for.
+
+-   Research needs a certain sample size to be able to answer certain
+    questions. But primate research is difficult to get enough sample
+    size for any given project. This need drove the push for more
+    openness and sharing.
+
+-   Centralized platform for primate researchers and for sharing data.
+
+-   Use GitHub to share things.
+
+-   Projects should preregister the plans, and all data, code, and
+    materials are uploaded to GitHub.
+
+-   Tools:
+
+    -   GitHub
+    -   Google Docs
+    -   Slack
+    -   OSF
+
+-   Use their website to disseminate news and findings
+
+-   Limitations:
+
+    -   Logistical. Impossible to use the exact same methods across all
+        studies.
+    -   Also technical and knowledge, not enough funding to hire
+        relevant expertise and technical resources.
 
@@
     to get there required a high level of collaboration.
+
 -   Seems to use GitHub to at least build the website.
+
 -   Building up an open collaboration project takes years of continued
     work and effort.
+
 -   Took a multi-staged approach to establishing the group/community.
+
     -   At each stage, it was slowly about introducing the concepts to a
@@
         way.
+
 -   Development follows principles of agile software development by
@@
     testing the developed features.
+
 -   Use of the iterative development helped them identify and respond to
@@
 -   Mostly an example of what they did and why
+
 -   Faced with limited resources and small sample sizes, but
@@
     together this collaboration project.
+
 -   Outlines benefits of this collaboration, such as reducing the
@@
     resources, and knowledge sharing/creation/management.
+
 -   Challenges to this collaboration are less papers, lower ability to
@@
     publications.
+
     -   A big challenge to these collaborations is sources of funding.
         Who pays for whose salary? How are funds distributed?
+
 -   Argues that any large-scale collaboration needs to use open
     practices by default.
+
 -   Something to consider when building large-scale collaboration is its
@@
     need to be considered at the start.
+
 -   The ManyPrimates use GitHub, at least to host their website with
@@
     code and data for some papers they've published.
+
 -   The ManyPrimates project also set some basic standards for project
@@
 
+-   Example
+-   Workflows
+-   Barriers
+-   Lessons learned
+-   Tools
+
 ## Type of paper
@@
 :::
+
+-   Example of a workflow
+-   Guide
 
@@
 :::
+
+-   This was a very good paper and very relevant and detailed.
+
+-   More inclusive term might be "open scholarship"
+
+-   Applying openness can be very challenging when it involves data on
+    children, but also that data on children is difficult to collect and
+    benefits substantially from researchers using open practices,
+    especially open data.
+
+-   The WomCogDev lab is a fairly small group (\~13 people), almost all
+    of whom are students (e.g. Masters, undergraduates, PhD students).
+
+-   General steps in their workflow:
+
+    1.  Design project
+    2.  Pre-register project or Registered Report
+    3.  Create experiment
+    4.  Recruit participants and collect data
+    5.  Analyze data
+    6.  Disseminate results
+
+-   Focus on 1, 4, and 5 since they say those are less discussed in the
+    literature.
+
+-   For 1, involves writing something up by the lead researcher, getting
+    feedback from all lab, writing detailed plan, upload to OSF, decide
+    on authorship.
+
+    -   Making hypothesis and thinking of what all possible outcomes for
+        results and what that means in the context of the hypothesis
+    -   A Data Management Plan is also created at this stage that
+        includes details about how to be FAIR
+
+-   For 2, they start off with trying to do a Registered Report, but if
+    it gets rejected, they will take the reviewer comments, revise and
+    make edits, and then upload to OSF as a pre-registered protocol.
+
+-   For 3, they do not have a common programming language for creating
+    experiments but do prioritize open source over proprietary.
+
+-   For 4, something they do to help with reproducibility is to use
+    "data partners", which is someone who is in the lab but not directly
+    involved in the specific project. Their task is to re-analyse the
+    data to see if they come to the same conclusions as the lead author.
+    Generally, the data partner is a PhD student or more senior.
+
+-   Tools used:
+
+    -   Slack for communication
+    -   Trello board
+    -   OSF, which has components made for literature, documents,
+        methods, raw data, experiment details, analysis and results,
+        manuscript, and communication (e.g. for outreach). Made private
+        at first.
+    -   R or JASP for analysis
+    -   bioRxiv/PsyArXiv for preprints
+
+-   Philosophy:
+
+    -   More work done upfront, the less work done later.
+    -   Some openness is better than no openness.
+    -   Openness is on a spectrum.
+    -   Always improving and can't always do everything at once.
+
+-   Other workflows notes:
+
+    -   Each weekly lab meeting, people start with "an interesting error
+        I found..." to encourage self-correction and open and honest
+        dialogue and discussions
+    -   They have a lab manual which describes these processes.
+    -   Not all projects follow this workflow, nor are they open.
+    -   Try to build the values into the work culture
+
+-   Advantages of workflow:
+
+    -   Uncertainty is reduced
+    -   Reproducibility is inherent to the design and practice of the
+        workflow
+
+-   Disadvantages of workflow:
+
+    -   Can sometimes be quite time-consuming
+    -   Can be difficult to get everyone on board and to follow it
+        fairly closely
+    -   Steep learning curve
+    -   Overreliance on OSF, which has a cap on amount of data to put
+        into it
 
@@
 
+-   Tips
+-   Guidelines
+-   Review
+-   Strategies
+-   Overview
+
 ## Type of paper
@@
 :::
+
+-   Community-building
+-   Tips
+-   Guide
 
@@
 :::
+
+-   Relevant paper as an overview
+
+-   Open science resources tend to be more theoretical then practical
+    ("do this" but not "this is how you do this")
+
+-   Strategy: Start small and slowly incorporate open science practices.
+
+    -   For instance, start with uploading a preprint, then
+        pre-register, then share notebooks/methods, then analysis code,
+        etc.
+
+-   Strategy: Become familiar with national/institutional open science
+    policies
+
+-   Strategy: Analyze and share successful cases of implementing open
+    science practices
+
+    -   By sharing, you bring awareness to others about it, which can
+        over time pressure and push for institutional/organizational
+        change.
+
+-   Strategy: Include open science practices in your teaching
+
+    -   Getting students to be more familiar with and comfort on open
+        science practices, in course settings and assignments, will mean
+        they will be more comfortable applying it to real projects.
+
+-   Strategy: Embrace and use open educational resources
+
+    -   Use them, create them, publish them
+
+-   Strategy: Collaborate with others using open tools
+
+    -   Example: Write an article using R Markdown or Quarto. Use open
+        formats for data. Use GitHub to share and collaborate on
+        projects.
+
+-   Strategy: Develop networks of open collaboration
+
+    -   Build networks of working with others in an open way.
+    -   Develop standards, frameworks, and templates to follow within
+        this network.
+
+-   Strategy: Voice your opinions
+
+    -   Write things in support of these initiatives
+    -   Outline values and principles to follow
+
+-   Strategy: Rethink and promote changes in assessment of scholarship
+
+    -   Push for and advocate for alternatives to assessments outside of
+        the typical impact factor and h-index
+
+-   Strategy: Create opportunities for people to specialize in open
+    science
+
+-   Tools:
+
+    -   OSF, GitHub, Zenodo, R, Quarto, R Markdown, Jupyter Notebooks
 
@@
 
+-   Best practices
+-   Lessons learned
+-   Review
+
 ## Type of paper
@@
 :::
+
+-   Example of workflow
+-   Guide
 
@@
 :::
+
+-   Very general outline of what they've done, without very clear
+    details on how they did it
+
+-   Best practices: Pre-registration, FAIR data, reproducible imaging,
+    open science of workflows, methods, analysis code
+
+-   Strategies:
+
+    -   Include a long review period to identify best practices and
+        tools before implementing any changes
+    -   Implement version control using Git and GitHub, so that when
+        students move on, the knowledge isn't lost
+    -   Transition from Matlab to Python (or R)
+    -   For new projects, start from scratch using best practices
+    -   For older projects, update to best practices as much as possible
+        given time and effort
+    -   All finished papers need to be uploaded to preprint archives
+    -   Convert data to BIDS format (very difficult procedure)
+    -   Converted in-house pipeline to standard fMRIPrep, which is a
+        standard imaging pipeline
+    -   Upload data to OpenNeuro
+    -   Constructed a common data dictionary for data collected (very
+        difficult)
+
+-   Tools:
+
+    -   Git, GitHub, Python
+    -   psyRxiv, bioRxiv, arXiv
+    -   BIDS data format as well as BIDS-Apps
+    -   fMRIPrep and Singularity
+    -   Deposit data on OpenNeuro
+
+-   Benefits:
+
+    -   Uploading to open records/archives shows institutional work and
+        knowledge put into the work
+    -   Reduced time to completion of many tasks
+    -   Reduced costs
+    -   Minimal loss of knowledge when students leave, so knowledge can
+        more easily be built up on more
+    -   Reducing errors from processing, analyzing, and data collection
+    -   Increased cross-group collaboration and knowledge sharing
+    -   Uploading preprints, using open source programming languages,
+        depositing data to public repos, and using containerized
+        reproducible pipelines all had low cost-high benefit ratios.

### 2024-10-22 doc/charting/Grange-2023.qmd
Add files via upload

---
title: 'Grange-2023'
---

# UKRN Open Research Training Resources and Priorities Working Paper

-   File: data/review/fulltext/
-   DOI: https://doi.org/10.31219/osf.io/s2f6k
-   OpenAlex ID: W4372403418

## Tools

### Specific tools mentioned - their function - where in the researh process used

-   Systematic review -used to assess the open access resources available - used as the initial point to improve open science in universities.
-   Large-scale survey - used to assess the needs of the trainers and students regarding open science - another initial point to build a infrastructure that             accommodates open science behaviour in university.
-   There is a huge set of mentioned tools used for each stage of the research cycle. Might be interesting to add them here too.

## Organizational structure for open collaboration

### Systematic review of open source tools to understand the current situation of open science in 18 centers

-   This paper focuses on understanding where the 18 centers are in terms of open science. By assessing this, they can make a strategy to be more open.
-   After informal chats with leaders of the centers, they organized the items related to open science into 6 categories according to the research cycle: planning,      conducting, analyzing. disseminating, evaluating and incentivizing research.

## Educational perspectives

-   There is no educational infrastructure on open access across this study. 62% of the resources don't have a certain trainer, indicating that researchers learn by     themselves. This is, of course, not a bad thing, but if learning groups were established, it would be more efficient, for example.
-   Most of the resources are decentralized (online), a common online infrastructure that guides researchers would be very beneficial.

## Barriers

### Barriers for open science

-   Most of open sources for training researchers in open science are involved in planning or analysis, which hinders the educational loop of open science.              Incentivizing and disseminating are just as important.
-   Very few resources are destinied to reproducibility, which also hinders open science.
-   The sources of highest quality are not even open access!

### 2024-10-22 doc/charting/Dora-2024.qmd
update data extraction from my studies

@@
 
-## Tools
+## Characteristics of the paper
 
-### Specific tools mentioned - their function - where in the researh process used
-
-::: content-hidden
-For instance: "OSF - pre-registration - planning". You can mention
-multiple tools. Just make another bullet.
-
-The research process is: planning, conducting, analysing, disseminating.
-If a combination write several, if all write "all"
-:::
-
--
+-   Type of paper (e.g., tips, example): guide
+-   Themes (e.g., tools, organization): organization
+-   Other keywords (e.g., newcomers): team science, individual-centered
 
@@
 ### Governance
-
-::: content-hidden
-For instance: "Develop forms of legitimate peripheral participation."
-
-These are bit of information and recommendations for governance of the
-project.
-:::
 
@@
 
-### Workflow
-
-::: content-hidden
-For instance: "designing the project - preregistration - creating the
-experiment - recruitment and data collection - data analysis -
-dissemination".
-
-These are overall process highlights
-:::
-
--
-
 ## Educational perspectives
@@
 ### Educational needs
-
-::: content-hidden
-For instance: "few resources for open collaboration, none were open and
-they were valued poorly compared to other practices"
-
-What does the paper write is the need for education in the field?
-:::
 
@@
 
-::: content-hidden
-For instance: "lack of education"
-
-Which barriers do the paper indicate for implementation of open science?
-:::
-
 -   no open science standards in journals

### 2024-10-22 doc/charting/Turoman-2022.qmd
making charting template and testing with a few studies
update data extraction from my studies

--- 2024-10-21 doc/charting/charting_form_template.qmd
@@
 ---
-title: 'Charting form template'
+title: 'Turoman-2022'
 ---
 
-::: content-hidden
-fill in one form per paper. Name the form according to first author and
-year like this: "Turoman-2022". Copy-paste the information from the
-full-text review below.
-:::
+# Open and reproducible practices in developmental psychology research: The workflow of the WomCogDev lab as an example
 
-# title of publication
+-   File: data/review/fulltext/oa-id-W4229452124.pdf
+-   DOI: https://doi.org/10.31234/osf.io/73bwu
+-   OpenAlex ID: https://openalex.org/W4229452124
 
--   File:
--   DOI:
--   OpenAlex ID:
+## Characteristics of the paper
+
+-   Type of paper (e.g., tips, example): example
+-   Themes (e.g., tools, organization): tools, workflow
+-   Other keywords (e.g., newcomers): lab-centered
 
@@
 
-::: content-hidden
-For instance: "OSF - pre-registration - planning". You can mention
-multiple tools. Just make another bullet.
-
-The research process is: planning, conducting, analysing, disseminating.
-If a combination write several, if all write "all"
-:::
-
--
+-   Slack - communication - all
+-   Trello - project management - planning
+-   Open Science Framework - repository - planning, analysing,
+    dissemination
+-   R - data analysis - analysing
+-   Jasp - data analysis - analysing
+-   Zenodo - data sharing - dissemination
+-   OpenNeuro - data sharing - dissemination
 
@@
 
-::: content-hidden
-For instance: "Develop forms of legitimate peripheral participation."
-
-These are bit of information and recommendations for governance of the
-project.
-:::
-
--
+-   Setup a clear structure for how to conduct the research considering
+    open science in each step
+-   Build in steps for error correction
 
@@
 
-::: content-hidden
-For instance: "designing the project - preregistration - creating the
-experiment - recruitment and data collection - data analysis -
-dissemination".
-
-These are overall process highlights
-:::
-
--
-
-## Educational perspectives
-
-### Educational needs
-
-::: content-hidden
-For instance: "few resources for open collaboration, none were open and
-they were valued poorly compared to other practices"
-
-What does the paper write is the need for education in the field?
-:::
+-   designing the project - preregistration - creating the experiment -
+    recruiting and data collection - data analysis - dissemination
 
@@
 
-::: content-hidden
-For instance: "lack of education"
-
-Which barriers do the paper indicate for implementation of open science?
-:::
-
--
+-   Not everyone have the same prerequisites. There are conscious
+    tradeoffs between trying to be as open as possible, and the
+    feasibility of applying an open practice
+-   Some practices can take additional time
+-   For the workflow to work, lab members must follow it quite closely
+-   The learning curve can be steep, especially for people who arrive
+    from more goal-oriented labs

### 2024-10-22 doc/charting/ManyPrimates-2021.qmd
added a few points to this paper

@@
 -   Github - version control - all
--   Registered reports - help designing analysis to prove specific hypothesis - study design
--   p-curve software - helps avoiding overrepresantation of positive results - 
--   A.P.E.S Wiki - open access platform for standardized research and conservation of the data - they report it as an outcome of large-scale collaboration
--   PRIMatE Research Exchange - platform to exchange data, ideas and protocols - they report it as an outcome of large-scale collaboration
+-   Registered reports - help designing analysis to prove specific
+    hypothesis - planning
+-   p-curve software - helps avoiding overrepresantation of positive
+    results - analysis
+-   A.P.E.S Wiki - open access platform for standardized research and
+    conservation of the data - dissemination
+-   PRIMatE Research Exchange - platform to exchange data, ideas and
+    protocols - dissemination
 
@@
 -   ManyPrimates wanted a lasting infrastructure
--   They developed a mailing list where researchers can exchange their ideas and analysis.
--   They developed a twitter (now X) account to disseminate and extend their work to other researchers.
+-   They developed a mailing list where researchers can exchange their
+    ideas and analysis.
+-   They developed a twitter (now X) account to disseminate and extend
+    their work to other researchers.
 
@@
 
--   They developed ethical guidelines for all collaborators (non-invasive research, always open science, author list)
--   They ran a pilot study that tried replicating analysis on short-term memory with more sample size.
--   They preregistered protocols, created code and hosted data in repositories so that other coworkers can run the analysis systematically.
+-   They developed ethical guidelines for all collaborators
+    (non-invasive research, always open science, author list)
+-   Research questions are selected democratically - proposals for
+    projects are submitted and members vote to select which projects
+    will be carried out
+-   They ran a pilot study that tried replicating analysis on short-term
+    memory with more sample size.
+-   They preregistered protocols, created code and hosted data in
+    repositories so that other coworkers can run the analysis
+    systematically.
 -   Data was collected.
 -   Other workforce merged the data and visualized the results.
--   With this pipeline, they decided to run other analysis. This highlights the importance of a good test study.
+-   With this pipeline, they decided to run other analysis. This
+    highlights the importance of a good test study.
+-   Task forces within the project prepared different materials they
+    then uploaded to github and pre-register
 
@@
 
--   Large-scale collaboration are a great opportunity for making more researchers get in touch with open science practices.
--   Creating websites like A.P.E.S Wiki or a mailing list creates a network of researchers that can follow similar practices.
--   Replication studies like the mentioned MP1 project on short-term memory can be of great educational value and help set up and infrastructure to promote openness.
+-   Large-scale collaboration are a great opportunity for making more
+    researchers get in touch with open science practices.
+-   Creating websites like A.P.E.S Wiki or a mailing list creates a
+    network of researchers that can follow similar practices.
+-   Replication studies like the mentioned MP1 project on short-term
+    memory can be of great educational value and help set up and
+    infrastructure to promote openness.
 
@@
 
--   Pre-registration might neglect innovation due to their rigid structure, but creates very solid results.
+-   Pre-registration might neglect innovation due to their rigid
+    structure, but creates very solid results.

### 2024-10-22 doc/charting/Kohrs-2023.qmd
updated list of tools to sync with format in other papers and added info to other sections

@@
 
--   Virtual unconference - not a tool per se, but a nice way of networking and sharing ideas - can be used either early to brainstorm and network or later to disseminate ideas
--   COARA - fairer way of assessing research output than impact factors - Not used, just mentioned.
--   Open Science Labs - not a tool per se, but dedicated staff and organizations who works solely to contribute and assist on designing open science - study design, but they can     assist in other stages.
-other decentralized hubs exist such as FORRT or STEM education hub.
--   SCOSS - application for funding to be able to publish with open science standards - publication.
+-   Virtual conference - networking and sharing ideas - all
+-   COARA - fairer way of assessing research output than impact
+    factors - dissemination
+-   SCOSS - application for funding to be able to publish with open
+    science standards - dissemination
 
@@
 
--   Make open science necessary for the curriculum in universities (Munich university as example) and add courses that touches on openness, preregistration, etc.
--   Thesis are required to have open science elements to them. including collaborative thesis
--   Open Science requirements in the curriculum needed to hire individuals.
+-   Make open science necessary for the curriculum in universities
+    (Munich university as example) and add courses that touches on
+    openness, preregistration, etc.
+-   Thesis are required to have open science elements to them. Including
+    collaborative thesis
+-   Open Science requirements in the CV needed to hire individuals
+-   Carefully define the scope of the project, Ensure that you have
+    adequate support
+-   Foster accessible discussions (Consider running "beginner" and
+    "advanced" community meetings)
+-   Build communities:Organize regular meetings
 
@@
 
--   Here education is the central aspect of the structure to build open science the norm in an institution
--   They suggest offering open science courses, but also integreate open science in other courses
--   They also suggest that hand-on training is the best way to learn, some ways of doing this is by making courses more interactive or have research groups go on open science        courses.
-Some of the courses or examples can be replications or collaborative thesis.
--   An essential part of education is allowing for spaces where researchers can work, such as journal clubs, resource hubs or hackathons.
+-   Here education is the central aspect of the structure to build open
+    science the norm in an institution
+-   Offering open science courses, but also integreate open science in
+    other courses
+-   Hands-on training is the best way to learn, some ways of doing this
+    is by making courses more interactive or have research groups go on
+    open science courses. Some of the courses or examples can be
+    replications or collaborative thesis.
+-   Perform replication or meta-research studies as course projects
+-   An essential part of education is allowing for spaces where
+    researchers can work, such as journal clubs, resource hubs or
+    hackathons.
 
@@
 -   Allocation for resources.
--   In general all the things required to change expressed in the topics above: open science not being part of the standard curriculum of universities or a required skill for        when hiring.
-The lack of spaces and infrastructure to network and collaborate.
-Innovative papers being preferred by mainstream media than replications.
+-   In general all the things required to change expressed in the topics
+    above: open science not being part of the standard curriculum of
+    universities or a required skill for when hiring. The lack of spaces
+    and infrastructure to network and collaborate. Innovative papers
+    being preferred by mainstream media than replications.

### 2024-10-22 doc/scispace/README.Rmd
scispace charting of the papers with documentation

# Description of process and instructions for SciSpace

We used SciSpace to additionally perform data charting using the themes
we identified.

All papers were uploaded to SciSpace.

## Instructions

The summary columns were as follows with the following instructions:

### TL_DR

TL;DR column used the default setting for TL;DR summary from SciSpace.

### Tools

A custom column.

Named: tools suggested for open collaboration

Specification: what are the specific tools mentioned in the paper to
help researchers to open and collaborative science? For instance open
science framework (OSF) or github.

### Organization

A custom column.

Named: organization of open collaboration

Specification: what are the suggested practices for open collaboration?
this also includes own examples in the papers. This could be the use of
slack for communication and github for coding.

### Barriers

A custom column.

Named: barrier

Specification: what are the barriers for doing more open science
mentioned in the paper?

### 2024-10-22 doc/paper.qmd
docs: small note about using open alex instead
started to add text from protocol and make structure for introduction

@@
 
-## Aims
+-   Open science and its role in research
 
-Our original overall aim, as defined in the protocol, of this scoping
-review is to identify current practices of open collaboration in
-biomedical and health research.
+-   Collaboration and its role in modern research
+
+    -   collaboration spanning from lab, to research center to multiple
+        centers
+    -   collaboration needed to tackle limitations: small populations,
+        lack of replication, etc
+    -   re-inventing discovery: a new way of working in science
+
+Scientific research now almost always requires working with other
+people.
+
+With the growing complexity and specialization in scientific practices
+and methods, together with globalisation of health and environmental
+issues, there is a great need for a paradigm shift in research
+collaboration to be able to tackle these challenges.
+
+-   Open collaboration - a combination of two themes
+
+    -   definition
+    -   big potential in science
+    -   but there very few resources and examples of how to integrate
+        open science into collaborations
+
+We define open collaboration using the definition as found in Forte and
+Lampe (2013):
+
+> "*an online environment that (a) supports the collective production of
+> an artifact (b) through a technologically mediated collaboration
+> platform (c) that presents a low barrier to entry and exit and (d)
+> supports the emergence of persistent but malleable social
+> structures.*"
+
+With the increasing emphasis on and demand for science to be more open,
+how we collaborate together is a key component to making science more
+open from the start of any project. But how do we collaborate in an open
+and transparent way? What are the best practices and tools we can use?
+What is an ideal collaborative workflow and how close or far are we from
+this ideal in reality?
+
+-   Aim
+
+This scoping review will focus on current practices of open
+collaboration and open science in relation to collaboration in the field
+of biomedical and health research.
 
@@
 
+This is a scoping review, so we are following the framework described by
+Arksey and O'Malley
+([DOI:10.1080/1364557032000119616](https://doi.org/10.1080/1364557032000119616))
+and by Levac, Colquhoun, and O'Brien
+([DOI:10.1186/1748-5908-5-69](https://doi.org/10.1186/1748-5908-5-69))
+as well as the guidelines outlined in the PRISMA-ScR
+([DOI:10.7326/M18-0850](https://doi.org/10.7326/M18-0850) statement.
+
 ### Formal sources
+
+We developed the initial search strategy in consultation with a research
+librarian. We will collect the data via systematic searches of
+databases, as well as some hand searches.
+
+We used OpenAlex is an open database with scholarly works from MAG,
+Crossref, ORCID, ROR, DOAJ, Unpaywall, Pubmed, Pubmed Central, The ISSN
+International Centre, Internet Archive, Web crawls, Subject-area and
+institutional repositories from arXiv and Zenodo.
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE)
+library(stringr)
+library(here)
+source(here("R/search-terms.R"))
+search_terms_inline <- str_replace_all(search_terms$general, "\\*", "\\\\\\*")
+```
+
+We used the following search terms:
+
+```         
+> `r search_terms_inline`
+```
+
+Inclusion criteria included any document where open collaboration
+practices are not the primary focus. We will be guided by the definition
+of open collaboration from Forte and Lampe (2013) mentioned above in
+determining whether the records are relevant. Any published document
+with reporting on current open collaboration practices. Any published
+document with advice, guidance, tools, and/or recommendations for
+improving open collaboration. Article language in English.
+
+Exclusion criteria were documents that do not report on specific open
+collaboration practices. Documents published \>5 years in the past
+(defined as before xxxx) to capture current/most recent practices.
+
+All data obtained from all searches in online databases will be exported
+into text files or CVS files for further processing including removal of
+duplicates.
+
+At least two of us will extract data using a standardized and tested
+template. Data regarding the data source (e.g., author, title,
+publication year), open collaboration practices, and any other relevant
+information, will be extracted. Extracted data will be summarized with
+the descriptive analytical method described by Arksey and O'Malley
+(2005). The descriptive analytical method is aimed at identifying and
+summarizing different open collaboration practices.
 
@@
     source.
+-   **Move all searching to using Open Alex**
+
+## Discussion
 

### 2024-10-23 doc/charting/Alessandroni-2022.qmd
update data extraction from my studies
Update Alessandroni-2022.qmd
Added a couple of barriers I found relevant. Other than that, this paper is all over the place and it has less workflow or structure than otherrs. Interesting, but does not add anything new if you have read the others.

@@
 
+## Characteristics of the paper
+
+-   Type of paper (e.g., tips, example): guide
+-   Themes (e.g., tools, organization): organization, tools
+-   Other keywords (e.g., newcomers):
+
 ## Tools
@@
 -   Markdown/quarto - collaborative writing - all
--   Github - version control - all
+-   Github/Gitlab - version control - all
 
@@
 -   Incorporating open tools may have a steep learning curve
+-   Concerns about data safety
+-   High prices for making papers open
 -   Open science in the curricula vitae of academics must become a

### 2024-10-26 doc/charting/_template.qmd
docs: :pencil2: very minor edits to template, most format and one typo

--- 2024-10-21 doc/charting/charting_form_template.qmd
@@
 ::: content-hidden
-fill in one form per paper. Name the form according to first author and
+Fill in one form per paper. Name the form according to first author and
 year like this: "Turoman-2022". Copy-paste the information from the
@@
 
-# title of publication
+# Title of publication
 
@@
 
+## Characteristics of the paper
+
+-   Type of paper (e.g., tips, example):
+-   Themes (e.g., tools, organization):
+-   Other keywords (e.g., newcomers):
+
 ## Tools
 
-### Specific tools mentioned - their function - where in the researh process used
+### Specific tools mentioned; their function; where in the research process used
 
 ::: content-hidden
-For instance: "OSF - pre-registration - planning". You can mention
+For instance: "OSF; pre-registration; planning". You can mention
 multiple tools. Just make another bullet.
@@
 
+-
+
 ## Barriers

### 2024-10-26 doc/charting/TorresEspin-2021.qmd

---
title: 'TorresEspin-2021'
---

# Promoting FAIR Data Through Community-driven Agile Design: the Open Data Commons for Spinal Cord Injury (odc-sci.org)

-   File: data/review/fulltext/oa-id-W3188722327.pdf
-   DOI: https://doi.org/10.1007/s12021-021-09533-8
-   OpenAlex ID: https://openalex.org/W3188722327

## Characteristics of the paper

-   Type of paper (e.g., tips, example):
    -   Case study
    -   Example workflow
-   Themes (e.g., tools, organization):
    -   tools
    -   organization
-   Other keywords (e.g., newcomers):
    -   Data infrastructure
    -   FAIR data
    -   Case study
    -   Agile design
    -   Templates
    -   Examples
    -   Strategies
    -   Software development

## Tools

### Specific tools mentioned; their function; where in the research process used

::: content-hidden
For instance: "OSF; pre-registration; planning". You can mention
multiple tools. Just make another bullet.

The research process is: planning, conducting, analysing, disseminating.
If a combination write several, if all write "all"
:::

-   GitHub?; Seems to use GitHub to at least build the website;
    dissemination?
-   Agile development; iteratively develop project and help with project
    management; workflow, planning, development
-   Staged development; distinct stages mixed with iterations; planning,
    development

## Organizational structure for open collaboration

### Governance

::: content-hidden
For instance: "Develop forms of legitimate peripheral participation."

These are bit of information and recommendations for governance of the
project.
:::

-   Building and encouraging community approval, support, and ownership
    via workshop events done in collaboration with major
    organizations/conferences.
    -   Engaging multiple levels of stakeholders
    -   Collaborate with funding agencies early on
-   Split into different teams, which have positions that aim to be
    about 3 year to rotate around people:
    -   Leadership board to coordinate the development and operation
    -   Executive board for oversight and be involved in executive
        decisions
    -   Community board to engage in community, get feedback from
        workshops
    -   Data science team for data curation, quality control, and
        revision

### Workflow

::: content-hidden
For instance: "designing the project - preregistration - creating the
experiment - recruitment and data collection - data analysis -
dissemination".

These are overall process highlights
:::

-   Took a multi-staged approach to establishing the group/community.

    -   At each stage, it was slowly about introducing the concepts to a
        broader and broader audience and getting feedback all along the
        way.

-   Development follows principles of agile software development by
    getting requirements from users, designing and developing those
    requirements, seeking feedback from users on what was developed, and
    testing the developed features.

-   Use of the iterative development helped them identify and respond to
    issues that came up. This is something that could be something that
    non-software projects could use to help with collaboration and
    maintaining momentum and motivation.

## Educational perspectives

### Educational needs

::: content-hidden
For instance: "few resources for open collaboration, none were open and
they were valued poorly compared to other practices"

What does the paper write is the need for education in the field?
:::

-   No education or training was mentioned in this paper.

## Barriers

### Barriers for open science

::: content-hidden
For instance: "lack of education"

Which barriers do the paper indicate for implementation of open science?
:::

-   Building up an open collaboration project takes years of continued
    work and effort.

-   While the project's output is a data sharing platform, the process
    to get there required a high level of collaboration.

-   Required a lot of expertise not typically found in researchers (e.g.
    software development, UI/UX design, data engineering, writing
    user-friendly documentation/tutorials).

-   Required getting regular direct feedback from potential users of
    project, which wasn't always easy.

### 2024-10-26 doc/charting/Sholler-2019.qmd
docs: :memo: finished charting sholler 2019

---
title: Sholler-2019
---

This paper seems more targeted to general open projects and not strictly
about open collaboration within research. However, it is useful
information contained within on some general steps to take to encourage
and continue collaboration in open projects and in as open ways as
possible.

# Ten simple rules for helping newcomers become contributors to open projects

-   File: data/review/fulltext/oa-id-W2972809368.pdf
-   DOI: https://doi.org/10.1371/journal.pcbi.1007296
-   OpenAlex ID: https://openalex.org/W2972809368

## Characteristics of the paper

-   Type of paper (e.g., tips, example): guide
-   Themes (e.g., tools, organization):
    -   community-building
-   Other keywords (e.g., newcomers):
    -   Onboarding
    -   Documentation
    -   Contributing
    -   Centralization
    -   Knowledge management
    -   Communication
    -   Guidelines

## Tools

### Specific tools mentioned; their function; where in the research process used

-   Not relevant.

## Organizational structure for open collaboration

### Governance

-   Make governance explicit (e.g. have clear documents describing who
    are in leadership positions, who makes decisions, and how decisions
    are made).
-   Include forms of legitimate peripheral participation that newcomers
    are most likely to start doing, such as commenting on issues or
    discussions or creating issues when they find something that needs
    attention.

### Workflow

-   There wasn't anything specific about workflows in this paper.

## Educational perspectives

### Educational needs

-   Ensure there are clear contributing guidelines and code of conduct
    to help contributors out.
-   Make it easy for people to get started, for instance, clear
    instructions for newcomers on how to collaborate.

## Barriers

### Barriers for open science

-   There wasn't anything specific about barriers in this paper.

### 2025-01-07 doc/protocol.qmd
chore: :truck: reformat to be a qmd file

--- 2022-11-03 doc/protocol.Rmd
@@
 shorttitle: "Scoping review of open collaboration"
-date: "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"
-author: 
-  - name: Hannah Chatwin
-    affiliation: 2
-  - name: Mario Garcia
-    affiliation: 3
-  - name: Daniel Ibsen
-    affiliation: 1
-  - name: Luke W. Johnston
-    affiliation: "1,2"
-affiliation:
-  - id: 1
-    institution: Steno Diabetes Center Aarhus, Denmark
-  - id: 2
-    institution: Aarhus University, Denmark
-  - id: 3
-    institution: Copenhagen University, Denmark
-output: 
-    prereg::prereg_pdf: default
-    md_document: default
+date: "2022-11-04"
+doi: 10.17605/OSF.IO/K9DR5
+execute:
+  echo: false
 ---
 
-<!--TODO: Include badge link to OSF-->
-
-```{r setup, include=FALSE}
+```{r setup}
+#| include: false
 knitr::opts_chunk$set(echo = FALSE)
@@
 library(here)
-source(here("R/search-terms.R"))
-search_terms_inline <- str_replace_all(search_terms$general, "\\*", "\\\\\\*")
+source(here("R/openalex-search.R"))
+search_terms_inline <- glue::glue("({search_terms()$title_search}[title]) AND {search_terms()$general_search}")
 ```
@@
 # Study information
-
-## Title
-
-`r rmarkdown::metadata$title`
 
@@
 : Estimated timeline for project.
-
-# References
-
-##
-
-```{=tex}
-\vspace{-2pc}
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{-1in}
-\setlength{\parskip}{8pt}
-```
-\noindent

### 2025-01-08 doc/paper.qmd

--- 2023-10-06 doc/paper.qmd
@@
 format: html
+bibliography: references.bib
+csl: vancouver.csl
 ---
@@
 The full protocol for this scoping review was uploaded to the Open
-Science Framework (DOI:
-[`10.17605/OSF.IO/K9DR5`](https://doi.org/10.17605/OSF.IO/K9DR5)).
+Science Framework [@Johnston2022].
 
-<!-- TODO: convert this to reference -->
+As with any research project, things evolve compared to what was
+originally intended or planned. In this section we describe what was
+changed from the original, uploaded protocol.
 
-### Formal sources
+### Document types
 
-### Informal sources
+We originally intended on searching websites, blogs, and other online
+resources, but it was very difficult to programmatically and
+systemtically achieve this. So we ended up only searching for scholarly
+work that was indexed in databases.
 
-<!-- TODO: need to add how we searched online sources, like lab websites -->
+### Source databases
+
+We originally aimed to review individual archives that included PubMed,
+bioRxiv, Scopus, and several others (the full list is in the protocol),
+and to use R packages with web API connections to each of these sources
+to programmatically extract the sources we wanted. However we
+encountered substantial issues that completely changed how we actually
+found and extracted the sources.
+
+The first challenge we encountered was that, while most of the source
+databases had (hypothetically) exposed APIs along with R packages
+available to access them, they didn't always work well or had
+complicated instructions for actually using them. For instance, the
+preprint repositories bioRxiv and medRxiv didn't have an up to date R
+package to access the preprints nor was the web API well described, nor
+well designed. In order to effectively use it, you need to download the
+entire database of preprints locally before being able to search for the
+preprints you want. This made it effectively impossible to use.
+
+The second challenge we encountered was a difference in results between
+using the web API compared to using the web search interface for some
+source databases. There were some small differences in search results
+between the API query compared to the web-based query. We couldn't
+identify or understand how these differences happened or way, though
+they were quite small differences (less than 10 out of thousands of
+scholarly works from the search results).
+
+The third challenge we had was that some source databases, like the Web
+of Science or Scopus, didn't work consistently between the authors. In
+order to use the web API with the R packages, you need to generate a
+token for authentication. However, for some authors, the token worked
+fine, and for others, it didn't work at all, with no explanation or
+error message. Given our interest in and aim for reproducibility, since
+the same code ran differently between authors, we decided to exclude
+these source databases.
+
+Given these challenges however, we unintentionally found
+[OpenAlex](https://openalex.org/), which is a public database of
+scholarly output that aggregates dozens of other source databases into
+one, easy interface. This resource also has an R package called
+`{openalexR}` [@Aria2024] with a very well designed interface, which
+simplified or made redundant much of our code we wrote. It also made it
+unnecessary to use the individual R packages for each source database
+that we originally listed in the protocol. By using this archive, it
+resolved all our challenges and barriers we had before. For a list of
+where they get their source data from, see their ["About the
+data"](https://help.openalex.org/hc/en-us/articles/24397285563671-About-the-data)
+page.
+
+### Inclusion and exlucion criteria
+
+While we didn't change our search terms for the initial search and
+extraction, we found that our search terms were not precise enough and
+got many irrelevant scholarly works. The full R code to filter down the
+search results is kept in the
+[`R/exlusions.R`](https://github.com/science-collective/scoping-review/blob/main/R/exclusions.R)
+file on the GitHub repository. For example, we extracted a large number
+of scholarly works describing surgery such as "open wound", electronics
+such as "open circuit", or environmental such as "open water" that we
+had to post-process and exclude.
+
+### Search period
+
+We were not able to dedicate as much time to this project as we had
+initially planned, so our "stopping rule" for end date didn't match with
+our actual search period. The actual end date for when we did the last
+search results extraction was
+[2024-02-29](https://github.com/science-collective/scoping-review/commit/f288d3f23d028e77ad1081e0cfe3583ce4dcb8b6).
 
@@
 
-### Deviations from the protocol
+## Discussions
 
--   **Original timeline**: We were quite ambitious with the timeline for
-    completing this scoping review. We did not adhere to the timeline.
--   **API vs web search results**: Almost all source databases had
-    exposed APIs, with R packages available to access them. We chose to
-    use these rather than using the web to extract the source data is
-    due to our secondary aim. However, we noticed that there were some
-    small differences in search results between the API query compared
-    to the web-based query. We can't explain these differences, though
-    they were quite minor.
--   **Exclude Web of Science source**: We were unable to connect the Web
-    of Science source to R through the `{wosr}` package. Using the API
-    key did not as documented in the package did not work. We decided
-    that in the interest of reproducibility, that we exclude this
-    source.
+## Conclusions
 
@@
 
--   HC:
--   MG:
--   DBI: Conceptualization, Data curation, formal analysis,
-    investigation, methodology, writing
--   LWJ:
+We originally had another author involved, HC, who is on the protocol
+author list. Since the time we uploaded the protocol, she has moved out
+of academia and could no longer participate in any work.
+
+Otherwise, the remaining authors (MG, DBI, and LWJ) had the following
+contribution roles, following the [CRediT](https://credit.niso.org/)
+taxonomy of conceptualization, data curation, formal analysis,
+investigation, methodology, writing - original draft, writing -
+reviewing and editing, project administration, software, validation, and
+visualization.

### 2025-01-08 doc/charting/ManyPrimates-2019.qmd

---
title: ManyPrimates-2019
---

::: callout-note
This paper wasn't the most relevant, as it didn't go into much detail on
collaboration.
:::

# Collaborative open science as a way to reproducibility and new insights in primate cognition research

-   File: data/review/fulltext/oa-id-W4251805646.pdf
-   DOI: https://doi.org/10.31234/osf.io/8w7zd
-   OpenAlex ID: https://openalex.org/W4251805646

## Characteristics of the paper

-   Type of paper (e.g., tips, example): review?, example
-   Themes (e.g., tools, organization):
    -   organization
    -   tools
    -   review
-   Other keywords (e.g., newcomers):
    -   Systematic review
    -   Large-scale collaboration
    -   Large-scale infrastructure

## Tools

### Specific tools mentioned; their function; where in the research process used

::: content-hidden
For instance: "OSF; pre-registration; planning". You can mention
multiple tools. Just make another bullet.

The research process is: planning, conducting, analysing, disseminating.
If a combination write several, if all write "all"
:::

-   GitHub; sharing materials and final papers; archiving, dissemination
-   Mailing lists; communication; all
-   Google Docs; collaborative writing; writing, planning
-   Google Drive; sharing of procedures and documentation; all
-   Slack
-   OSF; archiving protocols and analysis plans; archiving
-   Organization website; share news and communicate updates; all

## Organizational structure for open collaboration

### Governance

::: content-hidden
For instance: "Develop forms of legitimate peripheral participation."

These are bit of information and recommendations for governance of the
project.
:::

-   Started from symposium as part of regular major conference.
-   Established a mailing list to connect everyone.
-   No clear description of how they organized their governance.

### Workflow

::: content-hidden
For instance: "designing the project - preregistration - creating the
experiment - recruitment and data collection - data analysis -
dissemination".

These are overall process highlights
:::

-   They weren't completely clear on how exactly they used the workflows
    they (very briefly) describe.
-   Use GitHub or Google Drive to share things.
-   Use Google Docs to write papers.
-   Use their website to disseminate news and findings.
-   Projects should preregister the plans, and all data, code, and
    materials are uploaded to GitHub.

## Educational perspectives

### Educational needs

::: content-hidden
For instance: "few resources for open collaboration, none were open and
they were valued poorly compared to other practices"

What does the paper write is the need for education in the field?
:::

-   No major educational comments were made.
-   Outreach of results and activities is done through social media and
    conferences.

## Barriers

### Barriers for open science

::: content-hidden
For instance: "lack of education"

Which barriers do the paper indicate for implementation of open science?
:::

-   Logistical. Impossible to use the exact same methods across all
    studies, so re-using of methods and materials wasn't very directly
    useful.
-   Also technical and knowledge, not enough funding to hire relevant
    expertise and technical resources.
-   Lacked a clear governance structure, which is something they want to
    do in the future.

### 2025-01-08 doc/paper.qmd

@@
 
-The full protocol for this scoping review was uploaded to the Open
-Science Framework [@Johnston2022].
+The full protocol for this scoping review was uploaded to the Open Science Framework [@Johnston2022].
 
+This is a scoping review, so we are following the framework described by
+Arksey and O'Malley
+([DOI:10.1080/1364557032000119616](https://doi.org/10.1080/1364557032000119616))
+and by Levac, Colquhoun, and O'Brien
+([DOI:10.1186/1748-5908-5-69](https://doi.org/10.1186/1748-5908-5-69))
+as well as the guidelines outlined in the PRISMA-ScR
+([DOI:10.7326/M18-0850](https://doi.org/10.7326/M18-0850) statement.
+
+### Deviations from protocol
 As with any research project, things evolve compared to what was
@@
 
-### Document types
+#### Document types
 
@@
 
-### Source databases
+#### Source databases
 
@@
 
-### Inclusion and exlucion criteria
+#### Inclusion and exlucion criteria
 
@@
 
-### Search period
+#### Search period
 
@@
 
+### Formal sources
+
+We developed the initial search strategy in consultation with a research
+librarian. We will collect the data via systematic searches of
+databases, as well as some hand searches.
+
+We used OpenAlex is an open database with scholarly works from MAG,
+Crossref, ORCID, ROR, DOAJ, Unpaywall, Pubmed, Pubmed Central, The ISSN
+International Centre, Internet Archive, Web crawls, Subject-area and
+institutional repositories from arXiv and Zenodo.
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE)
+library(stringr)
+library(here)
+source(here("R/search-terms.R"))
+search_terms_inline <- str_replace_all(search_terms$general, "\\*", "\\\\\\*")
+```
+
+We used the following search terms:
+
+```         
+> `r search_terms_inline`
+```
+
+Inclusion criteria included any document where open collaboration
+practices are not the primary focus. We will be guided by the definition
+of open collaboration from Forte and Lampe (2013) mentioned above in
+determining whether the records are relevant. Any published document
+with reporting on current open collaboration practices. Any published
+document with advice, guidance, tools, and/or recommendations for
+improving open collaboration. Article language in English.
+
+Exclusion criteria were documents that do not report on specific open
+collaboration practices. Documents published \>5 years in the past
+(defined as before xxxx) to capture current/most recent practices.
+
+All data obtained from all searches in online databases will be exported
+into text files or CVS files for further processing including removal of
+duplicates.
+
+At least two of us will extract data using a standardized and tested
+template. Data regarding the data source (e.g., author, title,
+publication year), open collaboration practices, and any other relevant
+information, will be extracted. Extracted data will be summarized with
+the descriptive analytical method described by Arksey and O'Malley
+(2005). The descriptive analytical method is aimed at identifying and
+summarizing different open collaboration practices.
+
+### Informal sources
+
 ## Results
@@
 ## Conclusions
+
+## Discussion
 

### 2025-01-08 doc/reviews/luke.qmd

@@
 
+-   Strategies
+-   Overview
+-   Resources
+-   Tools
+
 ## Type of paper
@@
 :::
+
+-   Guide
+-   Review
 
@@
 :::
+
+-   They have a website version of their paper, hosted on GitHub, which
+    is fantastic to see!
+
+-   The paper doesn't really get into collaboration itself that much,
+    just tools that are open and that by default might make it easier to
+    collaborate with others.
+
+-   Other terms included: "robustness" when same data but different
+    methods give similar results, "generalizable" when new data and new
+    methods give similar results when new data and new methods give
+    similar results.
+
+-   Reviewed survey says that training and education were major barriers
+    to adopting open science practices because of lack of knowledge and
+    skill on the tools and processes. And because there are so many new
+    tools, it is hard even for experienced researchers to navigate
+    everything.
+
+-   The authors have a good strategy for how and why they list the tools
+    and resources that they do in the review.
+
+-   BIDS for open neuroimaging data formatting.
+
+-   Hierarchical Events Descriptor (HED) for metadata standard.
+
+-   DataLad for managing data versioning.
 
@@
 
+-   Training
+-   Resources
+-   Tools
+-   Survey
+
 ## Type of paper
@@
 :::
+
+-   Survey
 
@@
 :::
+
+-   Not a super relevant paper for our review.
+
+-   Related to training, most training material are not created with
+    open licenses, which makes it difficult to share and spread and be
+    re-used.
+
+-   Training is an area that needs improvement, not enough of it or not
+    relevant enough for current situation.
 
@@
 
+-   Strategies
+-   Best practices
+-   Review
+-   Community-building
+-   Training
+-   Assessment
+
 ## Type of paper
@@
 :::
+
+-   Useful guidelines for basic strategies to build up open science and
+    reproducibility, but not too much on collaboration specifically.
+
+-   Strategies for training:
+
+    -   have more courses on reproducibility and open science
+    -   integrate skills in reproducibility and open science into
+        existing courses
+    -   have more hands-on courses
+    -   embed a course training within a research group (e.g. like an
+        intervention)
+    -   reproduce a study as part of a course group project, to also
+        train collaborative team science
+    -   require curriculum to include reproducibility and open science
+        training
 
@@
 
+-   Review
+-   Tools
+-   Best practices
+
 ## Type of paper
@@
 :::
+
+-   Review
 
@@
 :::
+
+-   Is mostly a review of best practices.
+
+-   The content that does get into collaboration is higher level and
+    more general, for instance, "collaboration by sending us the data"
+    and "we sent out polls to the group to make decisions".
+
+-   Does get into some limitations of doing larger-scale collaborations:
+
+    -   Needs leadership to have progress, so people need to agree on
+        who and on how to limit abuse of power and to make decisions
+        based on their own preferences or goals without getting input
+        from the others
+    -   More people means more differences in opinions means more
+        potential for conflict.
 
@@
 
+-   Review
+-   Tools
+
 ## Type of paper
@@
 :::
+
+-   This was a very short paper, without anything of relevance to our
+    review.
 
@@
 
+-   Primer
+-   Review
+
 ## Type of paper
@@
 :::
+
+-   This paper is very short and has almost nothing about doing open
+    research and specifically nothing about open collaboration.
 
@@
 
--   Very general outline of what they've done, without very clear
-    details on how they did it
+-   Though a bit general, its a good overview of the steps they took to
+    get more collaboration going and moving into more openness
 

### 2025-01-08 doc/charting/Bush-2022.qmd
update data extraction from my studies

@@
 -   OpenAlex ID: https://openalex.org/W4283836446
+
+## Characteristics of the paper
+
+-   Type of paper (e.g., tips, example): example
+-   Themes (e.g., tools, organization): tools
+-   Other keywords (e.g., newcomers): workflow
 
@@
 -   clinicaltrials.gov - preregistration - planning
+-   FAIR (findability”, “accessibility”, “interoperability”, and “reusability”) -principles to organize data, not a tool per se, but I think they 
+    need to be emphasized - data collection, organization and sharing - 
+-   Brain imaging data structure (BIDS) - a common and standardized framework all scientists can work on - data collection and sharing
+-   Containarized pipelines - code that allows easy reproduction - data analysis
+-   ReproBIDS - dictionary with standardized terms for BIDS neuro data - planning, data collection, data deposition
 
@@
 
-### Governance
+### Workflow
 
-### Workflow
+-   The steps below were identified after: 1) assessing the crisis of reproducibility, 2) literature search (systematic review) #worth noting 
+    since it pops up in so many papers as a previous step to implementation.
 
@@
     reporting
+
+### Centre workflow of practices to become more open (the ones above are more on the individual level)
+
+-   publish code, publishing pre-prints, standardizing data to BIDS, transition to containarized pipelines, publish data in repositories, 
+    establish data dictionaries, pre-registration,
 

### 2025-01-08 doc/charting/Niso-2022.qmd

---
title: 'Charting for Niso et al 2022'
---

Review for  Niso-2022: Open and reproducible neuroimaging: From study inception to publication

# Title of publication

-   File: 
-   DOI: 10.1016/j.neuroimage.2022.119623
-   OpenAlex ID: w4295290221

## Characteristics of the paper

-   Type of paper (e.g., tips, example): guide (to conduct open science), review (of existing tools).
-   Themes (e.g., tools, organization): organization.
-   Other keywords (e.g., newcomers): all science cycle

## Tools

### Specific tools mentioned; their function; where in the research process used

The provide tools for each step in workflow. Here I highlight those that I find the most relevant.

protocolexchange - public example of Standard Operating Procedures (SOPs)
OSF preregistration (aspredicted.org)
MRIQC (monitoring quality)
Hierarchical Event Descriptor (HED) - helps with naming conventions
DataLad (similar to Github for handling data)
Fuzzy: for multiverse analysis
BrainLife: for derivatives that are a tad more complex in the field. Otherwise, other tools such as OSF.
COBIDAS: pipelines for best practices of writing.

## Organizational structure for open collaboration

None stated. This paper is purely focused on what researchers should do, but never states how it should be done with other people.

### Workflow

#### Study inception and planning

Study preparation (highlighting piloting, that is, reviewing all data and methods necessary for the studies are ready for the analysis).
Pre-registration
Ethics and sharing plan
Monitoring quality

#### Data acquisition

Human Connectome Project establishes frameworks and protocols to make reproducible and comparable data ascquisition, to some extent. This is the most important part of them all.

### Data management

Set up organization standards: have the same framework (BIDS)
Set up metadata and format conventions
Set up format of saving the data and trace it back.

### Data processing

With software and version control or desiging pipeline and workflows it all boils down to share clear code that ensures all of this is ensured.

They focus a lot on multiverse, that is, focus on the results that converge with different software or pipelines.

### Research dissemination

Data sharing (and data should be organized in a standardized way)
Preprints.

## Educational perspectives

The paper tries to educate on best practices, but never focuses on the education per se.

## Barriers

### Barriers for open science

Utilizing private devices for data acquisition, which leads to black boxes and difficults comparision.    
Struggle with derivative data sharing. Which format should be the best for data that we generate from the available raw standardized data? Here they propose BrainLife as an example, but in other fields this is a very interesting topic!

### 2025-01-08 doc/paper.qmd

@@
 
+```{r setup}
+#| include: false
+knitr::opts_chunk$set(echo = FALSE)
+library(stringr)
+library(here)
+source(here("R/openalex-search.R"))
+# TODO: This doesn't work, Luke is fixing it in connection with making Quarto website
+# search_terms_inline <- str_replace_all(search_terms$general, "\\*", "\\\\\\*")
+```
+
 ## Introduction
@@
 
-We define open collaboration using the definition as found in Forte and
-Lampe (2013):
+We define open collaboration using the definition as found in
+[@Forte2013]:
 
@@
 
--   Aim
+### Aim
 
@@
 
-The full protocol for this scoping review was uploaded to the Open Science Framework [@Johnston2022].
+The full protocol for this scoping review was uploaded to the Open
+Science Framework [@Johnston2022]. As with any research project, things
+evolve compared to what was originally intended or planned. In this
+section we briefly re-state what we described in the protocol and
+especially we describe what was changed from the protocol.
 
-This is a scoping review, so we are following the framework described by
-Arksey and O'Malley
-([DOI:10.1080/1364557032000119616](https://doi.org/10.1080/1364557032000119616))
-and by Levac, Colquhoun, and O'Brien
-([DOI:10.1186/1748-5908-5-69](https://doi.org/10.1186/1748-5908-5-69))
-as well as the guidelines outlined in the PRISMA-ScR
-([DOI:10.7326/M18-0850](https://doi.org/10.7326/M18-0850) statement.
+This is a scoping review, so we followed the framework described in
+[@Arksey2005, @Levac2010] as well as the guidelines outlined in the
+PRISMA-ScR statement [@Tricco2018].
 
-### Deviations from protocol
-As with any research project, things evolve compared to what was
-originally intended or planned. In this section we describe what was
-changed from the original, uploaded protocol.
-
-#### Document types
-
-We originally intended on searching websites, blogs, and other online
-resources, but it was very difficult to programmatically and
-systemtically achieve this. So we ended up only searching for scholarly
-work that was indexed in databases.
-
-#### Source databases
+### Deviations and challenges
 
@@
 
+We also originally intended on searching websites, blogs, and other
+online resources, but it was very difficult to programmatically and
+systemtically achieve this. So we ended up only searching for scholarly
+work that were indexed in databases.
+
 Given these challenges however, we unintentionally found
@@
 that we originally listed in the protocol. By using this archive, it
-resolved all our challenges and barriers we had before. For a list of
-where they get their source data from, see their ["About the
+resolved all our challenges and barriers we had before. For a full list
+of where they get their source data from, see their ["About the
 data"](https://help.openalex.org/hc/en-us/articles/24397285563671-About-the-data)
@@
 
-#### Inclusion and exlucion criteria
+### Document selection
+
+We developed the initial search strategy in consultation with a research
+librarian. We collected the data via systematic searches of databases.
+All authors were involved in reviewing the collected sources, from
+reviewing the titles, to abstracts, and finally to full-text documents.
+
+#### Information sources
+
+We used OpenAlex, after encountering the challenges described above,
+which is an open database with scholarly works from Microsoft Academic
+Graph, Crossref, ORCID, ROR, DOAJ, Unpaywall, Pubmed, Pubmed Central,
+the ISSN International Centre, Internet Archive, Web crawls,
+subject-area and institutional repositories from arXiv and Zenodo.
+
+#### Search terms
+
+We used the following search terms when searching for scholarly work:
+
+> `r search_terms_inline`
+
+#### Inclusion and exclusion criteria
+
+Inclusion criteria included any document where open collaboration
+practices are not the primary focus. We relied on the definition of open
+collaboration from [@Forte2013] in determining whether the records were
+relevant. Any published document with reporting on current open
+collaboration practices. Any published document with advice, guidance,
+tools, and/or recommendations for improving open collaboration. Article
+language in English. Exclusion criteria were documents that do not
+report on specific open collaboration practices.
 
@@
 
+#### Charting procedure
+
+At least two of us extracted data using a standardized and tested
+template. Data regarding the data source (e.g., author, title,
+publication year), open collaboration practices, and any other relevant
+information, will be extracted. Extracted data will be summarized with
+the descriptive analytical method described in [@Arksey2005], which is
+aimed at identifying and summarizing different open collaboration
+practices.
+
 #### Search period
@@
 
-### Formal sources
-
-We developed the initial search strategy in consultation with a research
-librarian. We will collect the data via systematic searches of
-databases, as well as some hand searches.
-
-We used OpenAlex is an open database with scholarly works from MAG,
-Crossref, ORCID, ROR, DOAJ, Unpaywall, Pubmed, Pubmed Central, The ISSN
-International Centre, Internet Archive, Web crawls, Subject-area and
-institutional repositories from arXiv and Zenodo.
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
-library(stringr)
-library(here)
-source(here("R/search-terms.R"))
-search_terms_inline <- str_replace_all(search_terms$general, "\\*", "\\\\\\*")
-```
-
-We used the following search terms:
-
-```         
-> `r search_terms_inline`
-```
-
-Inclusion criteria included any document where open collaboration
-practices are not the primary focus. We will be guided by the definition
-of open collaboration from Forte and Lampe (2013) mentioned above in
-determining whether the records are relevant. Any published document
-with reporting on current open collaboration practices. Any published
-document with advice, guidance, tools, and/or recommendations for
-improving open collaboration. Article language in English.
-
-Exclusion criteria were documents that do not report on specific open
-collaboration practices. Documents published \>5 years in the past
-(defined as before xxxx) to capture current/most recent practices.
-
-All data obtained from all searches in online databases will be exported
-into text files or CVS files for further processing including removal of
-duplicates.
-
-At least two of us will extract data using a standardized and tested
-template. Data regarding the data source (e.g., author, title,
-publication year), open collaboration practices, and any other relevant
-information, will be extracted. Extracted data will be summarized with
-the descriptive analytical method described by Arksey and O'Malley
-(2005). The descriptive analytical method is aimed at identifying and
-summarizing different open collaboration practices.
-
-### Informal sources
+The start date remained 5 years from our end date, which would have been
+approximately 2019-02-28.
 

### 2025-01-08 doc/charting/Niso-2022.qmd
created table of overall study characteristics and corrected some information in the charting forms

@@
 ---
-title: 'Charting for Niso et al 2022'
+title: 'Niso-2022'
 ---
 
-Review for  Niso-2022: Open and reproducible neuroimaging: From study inception to publication
-
-# Title of publication
+# Open and reproducible neuroimaging: From study inception to publication
 
@@
 
--   Type of paper (e.g., tips, example): guide (to conduct open science), review (of existing tools).
--   Themes (e.g., tools, organization): organization.
+-   Type of paper (e.g., tips, example): guide (to conduct open
+    science), review (of existing tools).
+-   Themes (e.g., tools, organization): tools, workflow
 -   Other keywords (e.g., newcomers): all science cycle
@@
 
-The provide tools for each step in workflow. Here I highlight those that I find the most relevant.
+The provide tools for each step in workflow. Here I highlight those that
+I find the most relevant.
 
-protocolexchange - public example of Standard Operating Procedures (SOPs)
-OSF preregistration (aspredicted.org)
-MRIQC (monitoring quality)
+protocolexchange - public example of Standard Operating Procedures
+(SOPs) OSF preregistration (aspredicted.org) MRIQC (monitoring quality)
 Hierarchical Event Descriptor (HED) - helps with naming conventions
-DataLad (similar to Github for handling data)
-Fuzzy: for multiverse analysis
-BrainLife: for derivatives that are a tad more complex in the field. Otherwise, other tools such as OSF.
-COBIDAS: pipelines for best practices of writing.
+DataLad (similar to Github for handling data) Fuzzy: for multiverse
+analysis BrainLife: for derivatives that are a tad more complex in the
+field. Otherwise, other tools such as OSF. COBIDAS: pipelines for best
+practices of writing.
 
@@
 
-None stated. This paper is purely focused on what researchers should do, but never states how it should be done with other people.
+None stated. This paper is purely focused on what researchers should do,
+but never states how it should be done with other people.
 
@@
 
-Study preparation (highlighting piloting, that is, reviewing all data and methods necessary for the studies are ready for the analysis).
-Pre-registration
-Ethics and sharing plan
-Monitoring quality
+Study preparation (highlighting piloting, that is, reviewing all data
+and methods necessary for the studies are ready for the analysis).
+Pre-registration Ethics and sharing plan Monitoring quality
 
@@
 
-Human Connectome Project establishes frameworks and protocols to make reproducible and comparable data ascquisition, to some extent. This is the most important part of them all.
+Human Connectome Project establishes frameworks and protocols to make
+reproducible and comparable data ascquisition, to some extent. This is
+the most important part of them all.
 
@@
 
-Set up organization standards: have the same framework (BIDS)
-Set up metadata and format conventions
-Set up format of saving the data and trace it back.
+Set up organization standards: have the same framework (BIDS) Set up
+metadata and format conventions Set up format of saving the data and
+trace it back.
 
@@
 
-With software and version control or desiging pipeline and workflows it all boils down to share clear code that ensures all of this is ensured.
+With software and version control or desiging pipeline and workflows it
+all boils down to share clear code that ensures all of this is ensured.
 
-They focus a lot on multiverse, that is, focus on the results that converge with different software or pipelines.
+They focus a lot on multiverse, that is, focus on the results that
+converge with different software or pipelines.
 
@@
 
-The paper tries to educate on best practices, but never focuses on the education per se.
+The paper tries to educate on best practices, but never focuses on the
+education per se.
 
@@
 
-Utilizing private devices for data acquisition, which leads to black boxes and difficults comparision.    
-Struggle with derivative data sharing.
-Which format should be the best for data that we generate from the available raw standardized data?
-Here they propose BrainLife as an example, but in other fields this is a very interesting topic!
+Utilizing private devices for data acquisition, which leads to black
+boxes and difficults comparision.\
+Struggle with derivative data sharing. Which format should be the best
+for data that we generate from the available raw standardized data? Here
+they propose BrainLife as an example, but in other fields this is a very
+interesting topic!

### 2025-01-08 doc/charting/TorresEspin-2021.qmd
created table of overall study characteristics and corrected some information in the charting forms

@@
 -   Type of paper (e.g., tips, example):
-    -   Case study
-    -   Example workflow
+    -   example
+    -   workflow
 -   Themes (e.g., tools, organization):
@@
 
-::: content-hidden
-For instance: "OSF; pre-registration; planning". You can mention
-multiple tools. Just make another bullet.
-
-The research process is: planning, conducting, analysing, disseminating.
-If a combination write several, if all write "all"
-:::
-
 -   GitHub?; Seems to use GitHub to at least build the website;
@@
 
-::: content-hidden
-For instance: "designing the project - preregistration - creating the
-experiment - recruitment and data collection - data analysis -
-dissemination".
-
-These are overall process highlights
-:::
-
 -   Took a multi-staged approach to establishing the group/community.
@@
 -   At each stage, it was slowly about introducing the concepts to a
-        broader and broader audience and getting feedback all along the
-        way.
+    broader and broader audience and getting feedback all along the way.
 
@@
 
-::: content-hidden
-For instance: "few resources for open collaboration, none were open and
-they were valued poorly compared to other practices"
-
-What does the paper write is the need for education in the field?
-:::
-
 -   No education or training was mentioned in this paper.
@@
 ### Barriers for open science
-
-::: content-hidden
-For instance: "lack of education"
-
-Which barriers do the paper indicate for implementation of open science?
-:::
 

### 2025-01-08 doc/charting/index.qmd
docs: :art: mostly formatting of docs to fit website

---
title: Charting plan
---

This is a short description of the charting plan.

1.  Each author is assigned specific papers to chart using the charting
    template
2.  The other authors reviews the charted form and updates if necessary
3.  If there are any disagreements, these will be resolved by discussion
4.  In the end, the data will be transferred to a data table

## Papers to chart

### Daniel

-   Lessons Learned: A Neuroimaging Research Center's Transition to Open
    and Reproducible Science
-   Ten strategies to foster open science in psychology and beyond
-   Accelerating addiction research via Open Science and Team Science
-   Open and reproducible practices in developmental psychology
    research: The workflow of the WomCogDev lab as an example

### Mario

-   Collaboration and Open Science Initiatives in Primate Research
-   Eleven Strategies for Making Reproducible Research and Open Science
    Training the Norm at Research Institutions
-   UKRN Open Research Training Resources and Priorities Working Paper
-   Open and reproducible neuroimaging: From study inception to
    publication

### Luke

-   Promoting FAIR Data Through Community-driven Agile Design: the Open
    Data Commons for Spinal Cord Injury (odc-sci.org)
-   Collaborative open science as a way to reproducibility and new
    insights in primate cognition research
-   Ten simple rules for helping newcomers become contributors to open
    projects

## Template to follow

::: {.callout-note appearance="minimal"}
{{< include _template.qmd >}}
:::

### 2025-01-08 doc/instructions/index.qmd
docs: :art: mostly formatting of docs to fit website

---
title: Instructions
---

## Steps to take for a scoping review

These are the steps to take in a scoping review, which was taken from
[Cochrane
Training](https://training.cochrane.org/resource/scoping-reviews-what-they-are-and-how-you-can-do-them)

1.  Develop a protocol (a priori)
2.  State your review question/objective clearly
3.  Establish your eligiblity criteria
4.  Search \>1 database
5.  Scan reference lists
6.  Search grey literature
7.  Screen titles and abstracts (by \>= 2 reviewers)
8.  Screen full-texts (by \>= 2 reviewers)
9.  Have a pre-defined charting form
10. Chart data (by \>=2 reviewers)

Additional Resources:

-   Joanna Briggs Institute, incl. scoping review protocol
    [template](https://jbi.global/scoping-review-network/resources)

## PRISMA-ScR Checklist

This is the PRISMA Scoping Review checklist we should follow and fill
in.

| section | subsection | item | description |
|:---|:---|:---|:---|
| Title | Title | 1 | Identify the report as a scoping review. |
| Abstract | Structured summary | 2 | Provide a structured summary that includes (as applicable): background, objectives, eligibility criteria, sources of evidence, charting methods, results, and conclusions that relate to the review questions and objectives. |
| Introduction | Rationale | 3 | Describe the rationale for the review in the context of what is already known. Explain why the review questions/objectives lend themselves to a scoping review approach. |
| Introduction | Objectives | 4 | Provide an explicit statement of the questions and objectives being addressed with reference to their key elements (e.g., population or participants, concepts, and context) or other relevant key elements used to conceptualize the review questions and/or objectives. |
| Methods | Protocol and registration | 5 | Indicate whether a review protocol exists; state if and where it can be accessed (e.g., a Web address); and if available, provide registration information, including the registration number. |
| Methods | Eligibility criteria | 6 | Specify characteristics of the sources of evidence used as eligibility criteria (e.g., years considered, language, and publication status), and provide a rationale. |
| Methods | Information sources\* | 7 | Describe all information sources in the search (e.g., databases with dates of coverage and contact with authors to identify additional sources), as well as the date the most recent search was executed. |
| Methods | Search | 8 | Present the full electronic search strategy for at least 1 database, including any limits used, such that it could be repeated. |
| Methods | Selection of sources of evidence† | 9 | State the process for selecting sources of evidence (i.e., screening and eligibility) included in the scoping review. |
| Methods | Data charting process‡ | 10 | Describe the methods of charting data from the included sources of evidence (e.g., calibrated forms or forms that have been tested by the team before their use, and whether data charting was done independently or in duplicate) and any processes for obtaining and confirming data from investigators. |
| Methods | Data items | 11 | List and define all variables for which data were sought and any assumptions and simplifications made. |
| Methods | Critical appraisal of individual sources of evidence§ | 12 | If done, provide a rationale for conducting a critical appraisal of included sources of evidence; describe the methods used and how this information was used in any data synthesis (if appropriate). |
| Methods | Synthesis of results | 13 | Describe the methods of handling and summarizing the data that were charted. |
| Results | Selection of sources of evidence | 14 | Give numbers of sources of evidence screened, assessed for eligibility, and included in the review, with reasons for exclusions at each stage, ideally using a flow diagram. |
| Results | Characteristics of sources of evidence | 15 | For each source of evidence, present characteristics for which data were charted and provide the citations. |
| Results | Critical appraisal within sources of evidence | 16 | If done, present data on critical appraisal of included sources of evidence (see item 12). |
| Results | Results of individual sources of evidence | 17 | For each included source of evidence, present the relevant data that were charted that relate to the review questions and objectives. |
| Results | Synthesis of results | 18 | Summarize and/or present the charting results as they relate to the review questions and objectives. |
| Discussion | Summary of evidence | 19 | Summarize the main results (including an overview of concepts, themes, and types of evidence available), link to the review questions and objectives, and consider the relevance to key groups. |
| Discussion | Limitations | 20 | Discuss the limitations of the scoping review process. |
| Discussion | Conclusions | 21 | Provide a general interpretation of the results with respect to the review questions and objectives, as well as potential implications and/or next steps. |
| Funding | Funding | 22 | Describe sources of funding for the included sources of evidence, as well as sources of funding for the scoping review. Describe the role of the funders of the scoping review. |

### 2025-01-08 doc/protocol.qmd
docs: :pencil2: small edit to title of protocol

@@
 ---
-title: "Towards open collaboration in biomedical and health research: A scoping review"
-shorttitle: "Scoping review of open collaboration"
+title: "Towards open collaboration in biomedical and health research: A protocol for a scoping review of open collaboration"
 date: "2022-11-04"
@@
 ## Study design
+
+<!-- TODO: Convert these to use the bib file -->
 

### 2025-01-08 doc/paper.qmd
Update paper.qmd
Vomited some small sections of the results just so that we can discuss about the voice and structure.

--- 2025-01-08 doc/paper.qmd
@@
 
+### Scoping review identifies only 11 papers discussing open collaboration
+
+### Practices of open collaboration
+
+Across the papers found in our literature search, X out of 11 discuss actual experiences on implementing open collaboration, albeit in different organizational levels.
+These range from lab level (Turoman et al) center level (Bush et al and Grange et al), multi-center level (ManyPrimates et al and Grange et al) and field level: psychology (Alessandorni et al), Spinal Cord injury (Torres-Espin et al) and neuroimaging (Niso et al).
+All of these share in common the need for an infrastructure that promotes open science and open collaboration via starting building a community of collaborators or making tools (usually online resources) that researchers can use to reach FAIR (Finndable, Accessible, Interoperable and Reusable) goals while doing research.
+Before delving in those, here we provide the specific needs for implementing open collaboration in each organizational level, as well as describing the differences in approaches among experiences between and across levels (Figure 2).
+
+#### Implementation of open collaboration practices at laboratory level
+
+#### Implementation of open collaboration practices at center level
+
+For center-level only one paper was identified (Bush et al), providing the example of a center of neuroimaging describing first how they identified the needs for open collaboration, then the individual-level practices that researchers should adapt and then the center-level changes to promote reaching FAIR goals.
+
+#### Implementation of open collaboration practices at multi-center level
+
+Interestingly, the level of organization with most papers is the multi-center level with two papers from ManyPrimates et al (ManyPrimates 2019 and ManyPrimates 2021) and Grange et al.
+In this organization level the most urgent needs are: 1) identifying the needs for open collaboration and 2) creating an infrastructure that allows those needs to be satisfied.
+Indeed, Grange et al describes a systematic review as an exploration of the needs for 11 UKRN centers to implement open collaborative practives.
+In this paper they specially focus on tools and resources among the 11 institutions and make clear the need for starting to utilize open resources as a first step to adapt open collaborative practices.
+The first paper from ManyPrimates et al [REF] describes the start of another multi-center collaboration, albeit from different institutions.
+It is interesting to observe that in this situation, the complex issue is to start the collaboration itself, which was ignited thanks to a symposium and an email chain among future collaborators.
+In contrast, ManyPrimates could quickly develop an open collaborative structure with relative ease in comparison to changing an already solid infrastructure, like in the case of Grange et al.
+
+#### Implementation of open collaboration practices at field level
+
+### Useful tools for open collaboration
+
 ## Discussions

### 2025-01-08 doc/paper.qmd
docs: :pencil2: small formatting fixes for website

--- 2025-01-08 doc/paper.qmd
@@
 date: last-modified
-author: 
-  - name: Hannah Chatwin
-    affiliations: 
-      - ref: au
-  - name: Mario Garcia
-    affiliations: 
-      - ref: ku
-  - name: Daniel B. Ibsen
-    affiliations: 
-      - ref: sdca
-      - ref: au
-  - name: Luke W. Johnston
-    affiliations: 
-      - ref: sdca
-      - ref: au
-affiliations:
-  - id: sdca
-    name: Steno Diabetes Center Aarhus
-    country: Denmark
-  - id: au
-    name: Aarhus University
-    country: Denmark
-  - id: ku
-    name: Copenhagen University
-    country: Denmark
-format: html
-bibliography: references.bib
-csl: vancouver.csl
 ---
@@
 The full protocol for this scoping review was uploaded to the Open
-Science Framework [@Johnston2022].
+Science Framework (DOI:
+[`10.17605/OSF.IO/K9DR5`](https://doi.org/10.17605/OSF.IO/K9DR5)).
 
-As with any research project, things evolve compared to what was
-originally intended or planned. In this section we describe what was
-changed from the original, uploaded protocol.
+<!-- TODO: convert this to reference -->
 
-### Document types
+### Formal sources
 
-We originally intended on searching websites, blogs, and other online
-resources, but it was very difficult to programmatically and
-systemtically achieve this. So we ended up only searching for scholarly
-work that was indexed in databases.
+### Informal sources
 
-### Source databases
-
-We originally aimed to review individual archives that included PubMed,
-bioRxiv, Scopus, and several others (the full list is in the protocol),
-and to use R packages with web API connections to each of these sources
-to programmatically extract the sources we wanted. However we
-encountered substantial issues that completely changed how we actually
-found and extracted the sources.
-
-The first challenge we encountered was that, while most of the source
-databases had (hypothetically) exposed APIs along with R packages
-available to access them, they didn't always work well or had
-complicated instructions for actually using them. For instance, the
-preprint repositories bioRxiv and medRxiv didn't have an up to date R
-package to access the preprints nor was the web API well described, nor
-well designed. In order to effectively use it, you need to download the
-entire database of preprints locally before being able to search for the
-preprints you want. This made it effectively impossible to use.
-
-The second challenge we encountered was a difference in results between
-using the web API compared to using the web search interface for some
-source databases. There were some small differences in search results
-between the API query compared to the web-based query. We couldn't
-identify or understand how these differences happened or way, though
-they were quite small differences (less than 10 out of thousands of
-scholarly works from the search results).
-
-The third challenge we had was that some source databases, like the Web
-of Science or Scopus, didn't work consistently between the authors. In
-order to use the web API with the R packages, you need to generate a
-token for authentication. However, for some authors, the token worked
-fine, and for others, it didn't work at all, with no explanation or
-error message. Given our interest in and aim for reproducibility, since
-the same code ran differently between authors, we decided to exclude
-these source databases.
-
-Given these challenges however, we unintentionally found
-[OpenAlex](https://openalex.org/), which is a public database of
-scholarly output that aggregates dozens of other source databases into
-one, easy interface. This resource also has an R package called
-`{openalexR}` [@Aria2024] with a very well designed interface, which
-simplified or made redundant much of our code we wrote. It also made it
-unnecessary to use the individual R packages for each source database
-that we originally listed in the protocol. By using this archive, it
-resolved all our challenges and barriers we had before. For a list of
-where they get their source data from, see their ["About the
-data"](https://help.openalex.org/hc/en-us/articles/24397285563671-About-the-data)
-page.
-
-### Inclusion and exlucion criteria
-
-While we didn't change our search terms for the initial search and
-extraction, we found that our search terms were not precise enough and
-got many irrelevant scholarly works. The full R code to filter down the
-search results is kept in the
-[`R/exlusions.R`](https://github.com/science-collective/scoping-review/blob/main/R/exclusions.R)
-file on the GitHub repository. For example, we extracted a large number
-of scholarly works describing surgery such as "open wound", electronics
-such as "open circuit", or environmental such as "open water" that we
-had to post-process and exclude.
-
-### Search period
-
-We were not able to dedicate as much time to this project as we had
-initially planned, so our "stopping rule" for end date didn't match with
-our actual search period. The actual end date for when we did the last
-search results extraction was
-[2024-02-29](https://github.com/science-collective/scoping-review/commit/f288d3f23d028e77ad1081e0cfe3583ce4dcb8b6).
+<!-- TODO: need to add how we searched online sources, like lab websites -->
 
@@
 
-### Scoping review identifies only 11 papers discussing open collaboration
+### Deviations from the protocol
 
-### Practices of open collaboration
-
-Across the papers found in our literature search, X out of 11 discuss actual experiences on implementing open collaboration, albeit in different organizational levels.
-These range from lab level (Turoman et al) center level (Bush et al and Grange et al), multi-center level (ManyPrimates et al and Grange et al) and field level: psychology (Alessandorni et al), Spinal Cord injury (Torres-Espin et al) and neuroimaging (Niso et al).
-All of these share in common the need for an infrastructure that promotes open science and open collaboration via starting building a community of collaborators or making tools (usually online resources) that researchers can use to reach FAIR (Finndable, Accessible, Interoperable and Reusable) goals while doing research.
-Before delving in those, here we provide the specific needs for implementing open collaboration in each organizational level, as well as describing the differences in approaches among experiences between and across levels (Figure 2).
-
-#### Implementation of open collaboration practices at laboratory level
-
-#### Implementation of open collaboration practices at center level
-
-For center-level only one paper was identified (Bush et al), providing the example of a center of neuroimaging describing first how they identified the needs for open collaboration, then the individual-level practices that researchers should adapt and then the center-level changes to promote reaching FAIR goals.
-
-#### Implementation of open collaboration practices at multi-center level
-
-Interestingly, the level of organization with most papers is the multi-center level with two papers from ManyPrimates et al (ManyPrimates 2019 and ManyPrimates 2021) and Grange et al.
-In this organization level the most urgent needs are: 1) identifying the needs for open collaboration and 2) creating an infrastructure that allows those needs to be satisfied.
-Indeed, Grange et al describes a systematic review as an exploration of the needs for 11 UKRN centers to implement open collaborative practives.
-In this paper they specially focus on tools and resources among the 11 institutions and make clear the need for starting to utilize open resources as a first step to adapt open collaborative practices.
-The first paper from ManyPrimates et al [REF] describes the start of another multi-center collaboration, albeit from different institutions.
-It is interesting to observe that in this situation, the complex issue is to start the collaboration itself, which was ignited thanks to a symposium and an email chain among future collaborators.
-In contrast, ManyPrimates could quickly develop an open collaborative structure with relative ease in comparison to changing an already solid infrastructure, like in the case of Grange et al.
-
-#### Implementation of open collaboration practices at field level
-
-### Useful tools for open collaboration
-
-## Discussions
-
-## Conclusions
+-   **Original timeline**: We were quite ambitious with the timeline for
+    completing this scoping review. We did not adhere to the timeline.
+-   **API vs web search results**: Almost all source databases had
+    exposed APIs, with R packages available to access them. We chose to
+    use these rather than using the web to extract the source data is
+    due to our secondary aim. However, we noticed that there were some
+    small differences in search results between the API query compared
+    to the web-based query. We can't explain these differences, though
+    they were quite minor.
+-   **Exclude Web of Science source**: We were unable to connect the Web
+    of Science source to R through the `{wosr}` package. Using the API
+    key did not as documented in the package did not work. We decided
+    that in the interest of reproducibility, that we exclude this
+    source.
+-   **Move all searching to using Open Alex**
 
@@
 
-We originally had another author involved, HC, who is on the protocol
-author list. Since the time we uploaded the protocol, she has moved out
-of academia and could no longer participate in any work.
-
-Otherwise, the remaining authors (MG, DBI, and LWJ) had the following
-contribution roles, following the [CRediT](https://credit.niso.org/)
-taxonomy of conceptualization, data curation, formal analysis,
-investigation, methodology, writing - original draft, writing -
-reviewing and editing, project administration, software, validation, and
-visualization.
+-   HC:
+-   MG:
+-   DBI: Conceptualization, Data curation, formal analysis,
+    investigation, methodology, writing
+-   LWJ:

### 2025-01-08 doc/protocol.qmd
chore: :wrench: move authors back into their paper or protocol files

@@
 date: "2022-11-04"
+author: 
+  - name: Hannah Chatwin
+    affiliations: 
+      - ref: au
+  - name: Mario Garcia
+    affiliations: 
+      - ref: ku
+  - name: Daniel B. Ibsen
+    affiliations: 
+      - ref: sdca
+      - ref: au
+  - name: Luke W. Johnston
+    affiliations: 
+      - ref: sdca
+      - ref: au
+affiliations:
+  - id: sdca
+    name: Steno Diabetes Center Aarhus
+    country: Denmark
+  - id: au
+    name: Aarhus University
+    country: Denmark
+  - id: ku
+    name: Copenhagen University
+    country: Denmark
 doi: 10.17605/OSF.IO/K9DR5

### 2025-01-08 R/exclusions.R
style: :art: ran styler formatter

@@ -7,7 +7,7 @@
 #' @examples
 #' readr::read_csv(here::here("data/records.csv")) |> exclude_from_title() |> dplyr::select(title) |> View()
 exclude_from_title <- function(data) {
-# TODO: Use ggcohort to track what is removed?
+  # TODO: Use ggcohort to track what is removed?
   data |>
     # Order so newest date is first, so distinct drops old duplicate titles.
     dplyr::arrange(dplyr::desc(publication_date)) |>
@@ -77,7 +77,7 @@ exclude_from_title <- function(data) {
 exclude <- function(data, variable, criteria) {
   data |>
     dplyr::filter(stringr::str_detect(
-      string = {{variable}},
+      string = {{ variable }},
       pattern = stringr::regex(criteria, ignore_case = TRUE),
       negate = TRUE
     ))

### 2025-01-08 R/openalex-search.R

@@ -56,13 +56,15 @@ openalex_retrieve_records <- function(ids) {
     identifier = ids,
     mailto = "lwjohnst@gmail.com"
   ) |>
-    dplyr::mutate(pdf_proj_path = stringr::str_replace(id, "https://openalex.org/", "oa-id-") |>
-                    fs::path_ext_set("pdf"),
-                  pdf_proj_path = fs::path("data/review/fulltext/", pdf_proj_path))
+    dplyr::mutate(
+      pdf_proj_path = stringr::str_replace(id, "https://openalex.org/", "oa-id-") |>
+        fs::path_ext_set("pdf"),
+      pdf_proj_path = fs::path("data/review/fulltext/", pdf_proj_path)
+    )
 }
 
 openalex_retrieve_pdf <- function(data) {
- urls <- data |>
+  urls <- data |>
     dplyr::select(pdf_proj_path, pdf_url) |>
     tidyr::drop_na()
 

### 2025-01-08 R/title-review.R

@@ -32,4 +32,3 @@ get_disagreed_on_titles <- function(title_list, agreed_on_titles) {
     purrr::list_rbind() |>
     dplyr::distinct()
 }
-

### 2025-01-08 doc/appendices.qmd

---
title: Appendices
---

This section lists additional files that we used or created in the
process of doing this scoping review project.

-   [Instructions](instructions/index.qmd): This docume has instructions
    for doing a scoping review as well as the PRISMA-ScR checklist.
-   [Full-text reviews](reviews/index.qmd): These documents contain each
    author's review of the full-text documents we selected after the
    title and abstract screening, as well as some grouping of them into
    themes and a listing of the titles of the documents we selected at
    each phase of the project.
-   [Charting](charting/index.qmd): This contains the structured
    charting documents we used for each full-text document we selected.
-   [Reflections](reflections/index.qmd): These are our informal
    reflections we wrote in to help us identify challenges and ways we
    improved on that.

### 2025-01-08 doc/paper.qmd

--- 2025-01-08 doc/paper.qmd
@@
 author:
-  - name: Hannah Chatwin
-    affiliations: 
-      - ref: au
   - name: Mario Garcia
@@
     country: Denmark
-format: html
-bibliography: references.bib
-csl: vancouver.csl
 ---
@@
 source(here("R/openalex-search.R"))
-# TODO: This doesn't work, Luke is fixing it in connection with making Quarto website
-# search_terms_inline <- str_replace_all(search_terms$general, "\\*", "\\\\\\*")
+search_terms_inline <- glue::glue("({search_terms()$title_search}[title]) AND {search_terms()$general_search}")
 ```
@@
 
-Across the papers found in our literature search, X out of 11 discuss actual experiences on implementing open collaboration, albeit in different organizational levels.
-These range from lab level (Turoman et al) center level (Bush et al and Grange et al), multi-center level (ManyPrimates et al and Grange et al) and field level: psychology (Alessandorni et al), Spinal Cord injury (Torres-Espin et al) and neuroimaging (Niso et al).
-All of these share in common the need for an infrastructure that promotes open science and open collaboration via starting building a community of collaborators or making tools (usually online resources) that researchers can use to reach FAIR (Finndable, Accessible, Interoperable and Reusable) goals while doing research.
-Before delving in those, here we provide the specific needs for implementing open collaboration in each organizational level, as well as describing the differences in approaches among experiences between and across levels (Figure 2).
+Across the papers found in our literature search, X out of 11 discuss
+actual experiences on implementing open collaboration, albeit in
+different organizational levels. These range from lab level (Turoman et
+al) center level (Bush et al and Grange et al), multi-center level
+(ManyPrimates et al and Grange et al) and field level: psychology
+(Alessandorni et al), Spinal Cord injury (Torres-Espin et al) and
+neuroimaging (Niso et al). All of these share in common the need for an
+infrastructure that promotes open science and open collaboration via
+starting building a community of collaborators or making tools (usually
+online resources) that researchers can use to reach FAIR (Finndable,
+Accessible, Interoperable and Reusable) goals while doing research.
+Before delving in those, here we provide the specific needs for
+implementing open collaboration in each organizational level, as well as
+describing the differences in approaches among experiences between and
+across levels (Figure 2).
 
@@
 
-For center-level only one paper was identified (Bush et al), providing the example of a center of neuroimaging describing first how they identified the needs for open collaboration, then the individual-level practices that researchers should adapt and then the center-level changes to promote reaching FAIR goals.
+For center-level only one paper was identified (Bush et al), providing
+the example of a center of neuroimaging describing first how they
+identified the needs for open collaboration, then the individual-level
+practices that researchers should adapt and then the center-level
+changes to promote reaching FAIR goals.
 
@@
 
-Interestingly, the level of organization with most papers is the multi-center level with two papers from ManyPrimates et al (ManyPrimates 2019 and ManyPrimates 2021) and Grange et al.
-In this organization level the most urgent needs are: 1) identifying the needs for open collaboration and 2) creating an infrastructure that allows those needs to be satisfied.
-Indeed, Grange et al describes a systematic review as an exploration of the needs for 11 UKRN centers to implement open collaborative practives.
-In this paper they specially focus on tools and resources among the 11 institutions and make clear the need for starting to utilize open resources as a first step to adapt open collaborative practices.
-The first paper from ManyPrimates et al [REF] describes the start of another multi-center collaboration, albeit from different institutions.
-It is interesting to observe that in this situation, the complex issue is to start the collaboration itself, which was ignited thanks to a symposium and an email chain among future collaborators.
-In contrast, ManyPrimates could quickly develop an open collaborative structure with relative ease in comparison to changing an already solid infrastructure, like in the case of Grange et al.
+Interestingly, the level of organization with most papers is the
+multi-center level with two papers from ManyPrimates et al (ManyPrimates
+2019 and ManyPrimates 2021) and Grange et al. In this organization level
+the most urgent needs are: 1) identifying the needs for open
+collaboration and 2) creating an infrastructure that allows those needs
+to be satisfied. Indeed, Grange et al describes a systematic review as
+an exploration of the needs for 11 UKRN centers to implement open
+collaborative practives. In this paper they specially focus on tools and
+resources among the 11 institutions and make clear the need for starting
+to utilize open resources as a first step to adapt open collaborative
+practices. The first paper from ManyPrimates et al \[REF\] describes the
+start of another multi-center collaboration, albeit from different
+institutions. It is interesting to observe that in this situation, the
+complex issue is to start the collaboration itself, which was ignited
+thanks to a symposium and an email chain among future collaborators. In
+contrast, ManyPrimates could quickly develop an open collaborative
+structure with relative ease in comparison to changing an already solid
+infrastructure, like in the case of Grange et al.
 
@@
 ## Conclusions
-
-## Discussion
 

### 2025-01-08 doc/protocol.qmd

@@
 
-This is a scoping review, so we are following the framework described by
-Arksey and O'Malley
-([DOI:10.1080/1364557032000119616](https://doi.org/10.1080/1364557032000119616))
-and by Levac, Colquhoun, and O'Brien
-([DOI:10.1186/1748-5908-5-69](https://doi.org/10.1186/1748-5908-5-69))
-as well as the guidelines outlined in the PRISMA-ScR
-([DOI:10.7326/M18-0850](https://doi.org/10.7326/M18-0850) statement.
+This is a scoping review, so we are following the framework described in
+[@Arksey2005, @Levac2010] as well as the guidelines outlined in the
+PRISMA-ScR statement [@Tricco2018].
 

### 2025-01-08 doc/paper.qmd
docs: :memo: expand on the introduction section of paper

@@
 
--   Open science and its role in research
+The time when a single scientist could work alone in a lab and make
+meaningful progress in their field is long gone. Scientific research in
+the modern era, especially in certain fields, almost requires working
+with other people, oftentimes a large number of people. Research
+questions are increasingly more challenging to answer as they require
+more time, resources, expertise, and personnel in order to meaningfully
+answer.
 
--   Collaboration and its role in modern research
+With the current needs and limitations such as resources when doing
+scientific research, collaborations range from those within a single
+group or lab, to a few researchers across different departments in the
+same institution, to many researchers and personnel spread across
+multiple research centers. Collaborations are needed to address basic
+limitations of working with small or constrained populations, to sharing
+valuable but expensive equipment, or to assisting with technical
+expertise or domain knowledge.
 
-    -   collaboration spanning from lab, to research center to multiple
-        centers
-    -   collaboration needed to tackle limitations: small populations,
-        lack of replication, etc
-    -   re-inventing discovery: a new way of working in science
+At the same time, there is also a higher need for science to be more
+open, higher quality, and more rigorous[@Cole2024, @Umbach2024], which
+necessitates that researchers collaborate with more researchers and with
+a more diverse group of researchers to fulfill these needs. Open
+scientific practices, such as open data, open source, and open
+materials, aim to improve the reliability and accessibility of
+scientific output to increase the societal impact of the results.
 
-Scientific research now almost always requires working with other
-people.
+There are many hypothetical benefits to openness in science, including
+in collaboration. For instance:
 
-With the growing complexity and specialization in scientific practices
-and methods, together with globalisation of health and environmental
-issues, there is a great need for a paradigm shift in research
-collaboration to be able to tackle these challenges.
+-   Greater transparency and accountability, because the built-in
+    openness makes it easy to see what was done, how, and why.
+-   Better reproducibility and inspectability, because everything can be
+    easily viewed and can be verified, which is a key tenet of science.
 
--   Open collaboration - a combination of two themes
+The intersection between greater collaboration and more openness
+highlights key challenges researchers face. How can we effectively
+collaborate together in a way that fulfills the demand for more
+openness, transparency, and accountability, while at the same time also
+not substantially impacting our productivity (or ideally improving it).
+How can we collaborate in an open and transparent way? What are the best
+practices and tools we can use? What is an ideal collaborative workflow
+and how close or how far are we from this ideal in reality?
 
-    -   definition
-    -   big potential in science
-    -   but there very few resources and examples of how to integrate
-        open science into collaborations
+From our own personal experience working in the field of health
+research, we have varied and diverse ways of collaborating. Often the
+most commonly used approach to collaboration is emailing Word documents
+around to get feedback and using meetings to discuss and agree on
+things. Rarely do we systematically examine whether we are following
+best practices for collaboration nor do we collaborate in an open way
+following the principles of open science. This lack of a clear standard
+or approach to collaborating effectively and openly can greatly impact
+productivity and quality of scientific research. It emphasizes a greater
+need for a paradigm shift in how we researchers collaborate to be able
+to effectively and efficiently tackle the challenges of the modern era.
 
-We define open collaboration using the definition as found in
-[@Forte2013]:
+For this scoping review, we define open collaboration using the
+definition as found in [@Forte2013]:
 
@@
 
-With the increasing emphasis on and demand for science to be more open,
-how we collaborate together is a key component to making science more
-open from the start of any project. But how do we collaborate in an open
-and transparent way? What are the best practices and tools we can use?
-What is an ideal collaborative workflow and how close or far are we from
-this ideal in reality?
+Open collaboration has a lot of potential benefits, many of which are
+the same benefits as seen with open science. For instance, open
+collaboration can lead to:
+
+-   Easier onboarding of new collaborators, since everything is open and
+    easily findable.
+-   Higher collaboration opportunities, because more openness means more
+    visibility as more parts of the scientific workflow are
+    disseminated.
+-   Faster time to dissemination, because the built-in openness makes it
+    easier to disseminate results.
+
+Unfortunately, there are, to our knowledge, very few resources and
+examples of how to integrate open science into collaborations and how to
+make collaboration be open.
 
@@
 
--   Provide an overview of current practices of or opinions about
+1.  Provide an overview of current practices of or opinions about
     research collaboration that follow basic open principles (e.g.,
@@
 
--   Summarize existing online tools and resources available to improve
+2.  Summarize existing online tools and resources available to improve
     open collaboration in research

### 2025-01-08 doc/charting/index.qmd

@@
 
--   Lessons Learned: A Neuroimaging Research Center's Transition to Open
-    and Reproducible Science
--   Ten strategies to foster open science in psychology and beyond
--   Accelerating addiction research via Open Science and Team Science
--   Open and reproducible practices in developmental psychology
-    research: The workflow of the WomCogDev lab as an example
+-   [Bush-2022](Bush-2022.qmd): Lessons Learned: A Neuroimaging Research
+    Center's Transition to Open and Reproducible Science
+-   [Alessandroni-2022](Allessandroni-2022.qmd): Ten strategies to
+    foster open science in psychology and beyond
+-   [Dora-2024](Dora-2024.qmd): Accelerating addiction research via Open
+    Science and Team Science
+-   [Turoman-2022](Turoman-2022.qmd): Open and reproducible practices in
+    developmental psychology research: The workflow of the WomCogDev lab
+    as an example
 
@@
 
--   Collaboration and Open Science Initiatives in Primate Research
--   Eleven Strategies for Making Reproducible Research and Open Science
-    Training the Norm at Research Institutions
--   UKRN Open Research Training Resources and Priorities Working Paper
--   Open and reproducible neuroimaging: From study inception to
-    publication
+-   [ManyPrimates-2021](ManyPrimates-2021.qmd): Collaboration and Open
+    Science Initiatives in Primate Research
+-   [Kohrs-2023](Kohrs-2023.qmd): Eleven Strategies for Making
+    Reproducible Research and Open Science Training the Norm at Research
+    Institutions
+-   [Grange-2023](Grange-2023.qmd): UKRN Open Research Training
+    Resources and Priorities Working Paper
+-   [Niso-2022](Niso-2022.qmd): Open and reproducible neuroimaging: From
+    study inception to publication
 
@@
 
--   Promoting FAIR Data Through Community-driven Agile Design: the Open
-    Data Commons for Spinal Cord Injury (odc-sci.org)
--   Collaborative open science as a way to reproducibility and new
-    insights in primate cognition research
--   Ten simple rules for helping newcomers become contributors to open
-    projects
+-   [TorresEspin-2021](TorresEspin-2021.qmd): Promoting FAIR Data
+    Through Community-driven Agile Design: the Open Data Commons for
+    Spinal Cord Injury (odc-sci.org)
+-   [ManyPrimates-2019](ManyPrimates-2019.qmd): Collaborative open
+    science as a way to reproducibility and new insights in primate
+    cognition research
+-   [Scholler-2019](Scholler-2019.qmd): Ten simple rules for helping
+    newcomers become contributors to open projects
 

### 2025-01-08 doc/reviews/mario.qmd

--- 2024-08-14 doc/reviews/luke.qmd
@@
 ---
-title: 'Full Article Review'
+title: 'Reviews by Mario'
 ---
@@
 
--   Onboarding
--   Documentation
--   Contributing
--   Centralization
--   Knowledge management
--   Communication
--   Guidelines
-
 ## Type of paper
@@
 :::
-
--   Guide
 
@@
 :::
-
-This paper seems more targeted to general open projects and not strictly
-about open collaboration within research. However, it is useful
-information contained within on some general steps to take to encourage
-and continue collaboration in open projects and in as open ways as
-possible.
-
-The rules that are more relevant to open collaboration are:
-
-1.  Be welcoming: Example, recognize when newcomers join and have an
-    onboarding process or document.
-2.  Make governance explicit: Example, how are decisions made?
-3.  Keep knowledge up to date and findable: Example, where are the
-    contributing guidelines?
-4.  Have a code of conduct that you enforce: Example, what are the
-    guidelines for communication and what happens if someone breaks
-    them?
-5.  Make it easy for contributors to get started: Example, like the
-    being welcome, have an onboarding document and/or roadmap for the
-    projects work.
-6.  Acknowledge all contributions: Any contribution can be meaningful if
-    it helps further the goal of the project.
 
@@
 
--   Data infrastructure
--   FAIR data
--   Case study
--   Agile design
--   Templates
--   Examples
--   Strategies
--   Software development
-
 ## Type of paper
@@
 :::
-
--   Case study
--   Example workflow
 
@@
 :::
-
--   While the project's output is a data sharing platform, the process
-    to get there required a high level of collaboration.
--   Seems to use GitHub to at least build the website.
--   Building up an open collaboration project takes years of continued
-    work and effort.
--   Took a multi-staged approach to establishing the group/community.
-    -   At each stage, it was slowly about introducing the concepts to a
-        broader and broader audience and getting feedback all along the
-        way.
--   Development follows principles of agile software development by
-    getting requirements from users, designing and developing those
-    requirements, seeking feedback from users on what was developed, and
-    testing the developed features.
--   Use of the iterative development helped them identify and respond to
-    issues that came up. This is something that could be something that
-    non-software projects could use to help with collaboration and
-    maintaining momentum and motivation.
 
@@
 
--   Large-scale collaboration
--   Data aggregation
--   Replications
--   Limited resources
--   Strategies
--   Case study
--   Communities of practice
-
 ## Type of paper
@@
 :::
-
--   Example workflow
--   Community building
--   Case study
 
@@
 :::
-
--   Mostly an example of what they did and why
--   Faced with limited resources and small sample sizes, but
-    wanting/needing more to make results generalizable, they put
-    together this collaboration project.
--   Outlines benefits of this collaboration, such as reducing the
-    efforts of individual researchers by distributing workload,
-    resources, and knowledge sharing/creation/management.
--   Challenges to this collaboration are less papers, lower ability to
-    cover more topics, less freedom of control and direction at the
-    individual researcher level (since they are part of a larger group
-    and need to have a consensus on a topic or standards of practice),
-    higher level of rules and processes for dealing with researchers who
-    try to take advantage of the community for their own benefit, as
-    well as how to decide on authorship/contributorship for scientific
-    publications.
-    -   A big challenge to these collaborations is sources of funding.
-        Who pays for whose salary? How are funds distributed?
--   Argues that any large-scale collaboration needs to use open
-    practices by default.
--   Something to consider when building large-scale collaboration is its
-    continuation. If its started by one or a few people and with
-    dedicated funding for it, what happens if that person or people
-    leave or move on to other things? Or when the funding ends? These
-    need to be considered at the start.
--   The ManyPrimates use GitHub, at least to host their website with
-    some general documentation and guidelines, as well as some analysis
-    code and data for some papers they've published.
--   The ManyPrimates project also set some basic standards for project
-    file and folder structure, for pre-registering the study, etc.
 

### 2025-01-08 doc/charting/Bush-2022.qmd

--- 2024-10-21 doc/charting/Bush-2022.qmd
@@
 -   OpenAlex ID: https://openalex.org/W4283836446
+
+## Characteristics of the paper
+
+-   Type of paper (e.g., tips, example): example
+-   Themes (e.g., tools, organization): tools, workflow
+-   Other keywords (e.g., newcomers):
 
@@
 -   clinicaltrials.gov - preregistration - planning
+-   FAIR (findability", "accessibility", "interoperability", and
+    "reusability") -principles to organize data, not a tool per se, but
+    I think they need to be emphasized - data collection, organization
+    and sharing -
+-   Brain imaging data structure (BIDS) - a common and standardized
+    framework all scientists can work on - data collection and sharing
+-   Containarized pipelines - code that allows easy reproduction - data
+    analysis
+-   ReproBIDS - dictionary with standardized terms for BIDS neuro data -
+    planning, data collection, data deposition
 
@@
 
-### Governance
+### Workflow
 
-### Workflow
+-   The steps below were identified after: 1) assessing the crisis of
+    reproducibility, 2) literature search (systematic review) #worth
+    noting since it pops up in so many papers as a previous step to
+    implementation.
 
@@
     reporting
+
+### Centre workflow of practices to become more open (the ones above are more on the individual level)
+
+-   publish code, publishing pre-prints, standardizing data to BIDS,
+    transition to containarized pipelines, publish data in repositories,
+    establish data dictionaries, pre-registration,
 

### 2025-01-08 doc/charting/ManyPrimates-2019.qmd

@@
 ---
-title: ManyPrimates-2019
+title: 'ManyPrimates-2019'
 ---
@@
     -   review
+    -   workflow
 -   Other keywords (e.g., newcomers):
@@
 
-::: content-hidden
-For instance: "Develop forms of legitimate peripheral participation."
-
-These are bit of information and recommendations for governance of the
-project.
-:::
-
 -   Started from symposium as part of regular major conference.
@@
 ### Workflow
-
-::: content-hidden
-For instance: "designing the project - preregistration - creating the
-experiment - recruitment and data collection - data analysis -
-dissemination".
-
-These are overall process highlights
-:::
 

### 2025-01-08 doc/charting/ManyPrimates-2021.qmd

@@
 
-# Collaborative open science as a way to reproducibility and new insights in primate cognition research
+# Collaboration and Open Science Initiatives in Primate Research
 
@@
 -   OpenAlex ID: W4251805646
+
+## Characteristics of the paper
+
+-   Type of paper (e.g., tips, example): example
+-   Themes (e.g., tools, organization): organization, tools
+-   Other keywords (e.g., newcomers):
 

### 2025-01-08 doc/paper.qmd
build: :wrench: move PDF linkage and generation into only protocol and paper

--- 2025-01-08 doc/paper.qmd
@@
     country: Denmark
+format:
+  html: default
+  typst:
+    columns: 2
+    papersize: a4
+    margin:
+      x: 2cm
+      y: 2cm
+format-links:
+  - html
+  - format: typst
+    text: PDF
+    icon: file-pdf
 ---

### 2025-01-08 doc/protocol.qmd
build: :wrench: move PDF linkage and generation into only protocol and paper

@@
   echo: false
+format:
+  html: default
+  typst:
+    columns: 2
+    papersize: a4
+    margin:
+      x: 2cm
+      y: 2cm
+format-links:
+  - html
+  - format: typst
+    text: PDF
+    icon: file-pdf
 ---

### 2025-02-10 doc/paper.qmd
updated results section and started to add reference to the bib-file

@@
 
-### Scoping review identifies only 11 papers discussing open collaboration
+```{r}
+library(targets)
 
-### Practices of open collaboration
+n_papers <- tar_read(records_title_only) %>% nrow() %>% as.numeric()
 
-Across the papers found in our literature search, X out of 11 discuss
-actual experiences on implementing open collaboration, albeit in
-different organizational levels. These range from lab level (Turoman et
-al) center level (Bush et al and Grange et al), multi-center level
-(ManyPrimates et al and Grange et al) and field level: psychology
-(Alessandorni et al), Spinal Cord injury (Torres-Espin et al) and
-neuroimaging (Niso et al). All of these share in common the need for an
-infrastructure that promotes open science and open collaboration via
-starting building a community of collaborators or making tools (usually
-online resources) that researchers can use to reach FAIR (Finndable,
-Accessible, Interoperable and Reusable) goals while doing research.
-Before delving in those, here we provide the specific needs for
-implementing open collaboration in each organizational level, as well as
-describing the differences in approaches among experiences between and
-across levels (Figure 2).
+n_papers_title_review <- tar_read(records_after_title_exclusion) %>% nrow() %>% as.numeric()
 
-#### Implementation of open collaboration practices at laboratory level
+n_papers_excluded_title_review <- n_papers - n_papers_title_review
 
-#### Implementation of open collaboration practices at center level
+n_titles_selected <- tar_read(titles_selected) %>% nrow() %>% as.numeric()
 
-For center-level only one paper was identified (Bush et al), providing
-the example of a center of neuroimaging describing first how they
-identified the needs for open collaboration, then the individual-level
-practices that researchers should adapt and then the center-level
-changes to promote reaching FAIR goals.
+n_paper_full_text <- tar_read(abstracts_selected) %>% nrow() %>% as.numeric()
 
-#### Implementation of open collaboration practices at multi-center level
+n_papers_selected_for_review <- read.csv(here("data", "article_characteristics.csv"), header = TRUE) %>% nrow() %>% as.numeric()
 
-Interestingly, the level of organization with most papers is the
-multi-center level with two papers from ManyPrimates et al (ManyPrimates
-2019 and ManyPrimates 2021) and Grange et al. In this organization level
-the most urgent needs are: 1) identifying the needs for open
-collaboration and 2) creating an infrastructure that allows those needs
-to be satisfied. Indeed, Grange et al describes a systematic review as
-an exploration of the needs for 11 UKRN centers to implement open
-collaborative practives. In this paper they specially focus on tools and
-resources among the 11 institutions and make clear the need for starting
-to utilize open resources as a first step to adapt open collaborative
-practices. The first paper from ManyPrimates et al \[REF\] describes the
-start of another multi-center collaboration, albeit from different
-institutions. It is interesting to observe that in this situation, the
-complex issue is to start the collaboration itself, which was ignited
-thanks to a symposium and an email chain among future collaborators. In
-contrast, ManyPrimates could quickly develop an open collaborative
-structure with relative ease in comparison to changing an already solid
-infrastructure, like in the case of Grange et al.
+#get table of study characteristics 
+article_characteristics <- read.csv(here("data", "article_characteristics.csv"))
 
-#### Implementation of open collaboration practices at field level
+n_guides <- article_characteristics %>% filter(paper_type == "guide") %>% nrow() %>% as.numeric()
+
+n_examples <- article_characteristics %>% filter(paper_type == "example") %>% nrow() %>% as.numeric()
+
+n_surveys <- article_characteristics %>% filter(paper_type == "survey") %>% nrow() %>% as.numeric()
+
+n_org <- article_characteristics %>% filter(str_detect(themes, "organization")) %>% nrow() %>% as.numeric()
+
+n_tools <- article_characteristics %>% filter(str_detect(themes, "tools")) %>% nrow() %>% as.numeric()
+
+n_education <- article_characteristics %>% filter(str_detect(themes, "education")) %>% nrow() %>% as.numeric()
+
+n_researcher <- article_characteristics %>% filter(relevant_for == "researcher") %>% nrow() %>% as.numeric()
+
+n_research_group <- article_characteristics %>% filter(relevant_for == "research group") %>% nrow() %>% as.numeric()
+
+n_research_center <- article_characteristics %>% filter(relevant_for == "research center") %>% nrow() %>% as.numeric()
+
+n_research_centers <- article_characteristics %>% filter(relevant_for == "multiple centers") %>% nrow() %>% as.numeric()
+
+n_research_field <- article_characteristics %>% filter(relevant_for == "research field") %>% nrow() %>% as.numeric()
+
+```
+
+The search yielded a total of `r n_papers` papers from which we filtered
+`r n_papers_excluded_title_review` based on key words. The remaining
+`r n_papers_title_review` titles were independently screened by three
+reviewers from which `r n_titles_selected` abstracts were screened. Of
+these, `r n_paper_full_text` papers were assessed in full-text and
+`r n_papers_selected_for_review` were included in the scoping review.
+
+The identified papers included `r n_guides` guides, `r n_examples`
+examples and `r n_surveys` surveys.
+
+`r n_org` of the `r n_papers_selected_for_review` papers included
+recommendations for organizational practices to improve open
+collaboration, `r n_tools` mentioned specific tools used for open
+collaboration and `r n_education` highlighted educational needs. The
+identified papers discussed open collaboration on different
+organizational levels. `r n_researcher` were mostly directed at the
+individual researcher, `r n_research_group` at a research group,
+`r n_research_center` at a research center, `r n_research_centers` at
+several research centers and `r n_research_field` at entire research
+fields.
+
+### Organizational practices of open collaboration
+
+A common theme across organizational levels was the need for
+infrastructure that promotes open collaboration, building a community of
+collaborators and using online tools in accordance with the FAIR
+(Finndable, Accessible, Interoperable and Reusable) principles.
+
+individual level - add text
+
+laboratory/research group level - add text
+
+For center-level one paper described how they transitioned their
+neuroimaging research center toward more open and collaborative
+practices. Their central focus was on creating more open code and data
+to improve open collaboration @bush_lessons_2022. First, they used
+open-source code, then standardized data formats, developed analysis
+pipelines, shared data openly and developed protocols for data
+documentation. While the organizational transition to improve open
+collaboration was described, little was mentioned about how this has
+improved collaborative work at the research center.
+
+Interestingly, the level of organization with most papers was the
+multi-center level with two papers from ManyPrimates et al
+(@manyprimates_collaborative_2019, @manyprimates_collaboration_2021) and
+Grange et al. (@grange_ukrn_2023). In this organization level the most
+urgent needs are: 1) identifying the needs for open collaboration and 2)
+creating an infrastructure that allows those needs to be satisfied.
+Indeed, Grange et al describes a systematic review as an exploration of
+the needs for 11 UKRN centers to implement open collaborative practives.
+In this paper they specially focus on tools and resources among the 11
+institutions and make clear the need for starting to utilize open
+resources as a first step to adapt open collaborative practices. The
+first paper from ManyPrimates et al @manyprimates_collaborative_2019
+describes the start of another multi-center collaboration, albeit from
+different institutions. It is interesting to observe that in this
+situation, the complex issue is to start the collaboration itself, which
+was ignited thanks to a symposium and an email chain among future
+collaborators. In contrast, ManyPrimates could quickly develop an open
+collaborative structure with relative ease in comparison to changing an
+already solid infrastructure, like in the case of Grange et al.
+
+research field level
+
+Here, we provide the specific needs for implementing open collaboration
+in each organizational level, as well as describing the differences in
+approaches among experiences between and across levels (Figure 2).
 
@@
 
-## Discussions
+### Educational needs
 
-## Conclusions
+## Discussion
+
+### Conclusions
 

### 2025-02-10 R/generate-bibtex-file.R
feat: :sparkles: add function to convert DOI to BibTeX file
Closes #97

@@ -1,0 +1,19 @@
+doi_to_bib <- function(doi, curl_handle) {
+  stopifnot(length(doi) == 1)
+  curl::curl(doi, handle = curl_handle) |>
+    readr::read_lines() |>
+    stringr::str_trim()
+}
+
+download_doi_to_bib <- function(doi, curl_handle) {
+  # This is to tell the website to give us the BibTeX format
+  h <- curl::new_handle()
+  curl::handle_setheaders(h, "accept" = "application/x-bibtex")
+
+  output_path <- here::here("doc/reviewed-records.bib")
+  doi |>
+    purrr::map_chr(\(doi) doi_to_bib(doi, curl_handle = h)) |>
+    readr::write_lines(output_path)
+  cli::cli_alert("Note: The created {.file {output_path}} file requires manual cleaning, ideally through JabRef.")
+  output_path
+}

### 2025-02-10 _build.R
fix: :adhesive_bandage: PDF can't have more than one bibliography, this is temp fix

@@ -1,0 +1,6 @@
+# This is to fix a bug that PDF can only use one bibliography file
+c(
+  readr::read_lines(here::here("doc/references.bib")),
+  readr::read_lines(here::here("doc/reviewed-records.bib"))
+) |>
+  readr::write_lines(here::here("doc/temp-combined.bib"))

### 2025-02-10 doc/paper.qmd
docs: :memo: add code to load in the reviewed records

--- 2025-01-08 doc/paper.qmd
@@
 search_terms_inline <- glue::glue("({search_terms()$title_search}[title]) AND {search_terms()$general_search}")
+reviewed_records <- targets::tar_read(reviewed_article_records)
+
+list_refs <- bib2df::bib2df(here("doc/reviewed-records.bib")) |>
+  dplyr::filter(CATEGORY != "COMMENT") |>
+  glue::glue_data("@{BIBTEXKEY}") |>
+  str_c(collapse = ";") |>
+  append("[", 0) |>
+  append("]") |>
+  str_c(collapse = "")
 ```

### 2025-02-10 doc/paper.qmd
docs: :memo: add intro to results indicating the refs, plus those we exclude

@@
 
-### Scoping review identifies only 11 papers discussing open collaboration
+We found `r nrow(reviewed_records)` source documents discussing open
+collaboration in some way. These were `r list_refs`. Two of the
+documents, while passed our abstract review, did not contain anything
+relevant when we reviewed the full text [@Network2023a; @Yordanov2022],
+so we did not continue with charting them.
 

### 2025-02-10 doc/paper.qmd
chore: :wrench: add ORCID and affiliation URLs
Closes #109, closes #110

--- 2025-02-10 doc/paper.qmd
@@
   - name: Mario Garcia
+    orcid: 
     affiliations:
@@
   - name: Daniel B. Ibsen
+    orcid: "0000-0002-7038-4770"
     affiliations:
@@
   - name: Luke W. Johnston
+    orcid: "0000-0003-4169-2616"
     affiliations:
@@
     country: Denmark
+    url: "https://www.stenoaarhus.dk/"
   - id: au
@@
     country: Denmark
+    url: "https://www.au.dk/"
   - id: ku
@@
     country: Denmark
+    url: "https://www.ku.dk/"
 format:
@@
 search_terms_inline <- glue::glue("({search_terms()$title_search}[title]) AND {search_terms()$general_search}")
-reviewed_records <- targets::tar_read(reviewed_article_records)
-
-list_refs <- bib2df::bib2df(here("doc/reviewed-records.bib")) |>
-  dplyr::filter(CATEGORY != "COMMENT") |>
-  glue::glue_data("@{BIBTEXKEY}") |>
-  str_c(collapse = ";") |>
-  append("[", 0) |>
-  append("]") |>
-  str_c(collapse = "")
 ```

### 2025-02-10 doc/paper.qmd

--- 2025-02-10 doc/paper.qmd
@@
 This is a scoping review, so we followed the framework described in
-[@Arksey2005, @Levac2010] as well as the guidelines outlined in the
+[@Arksey2005; @Levac2010] as well as the guidelines outlined in the
 PRISMA-ScR statement [@Tricco2018].
@@
 search results is kept in the
-[`R/exlusions.R`](https://github.com/science-collective/scoping-review/blob/main/R/exclusions.R)
+[`R/exclusions.R`](https://github.com/science-collective/scoping-review/blob/main/R/exclusions.R)
 file on the GitHub repository. For example, we extracted a large number
@@
 actual experiences on implementing open collaboration, albeit in
-different organizational levels. These range from lab level (Turoman et
-al) center level (Bush et al and Grange et al), multi-center level
-(ManyPrimates et al and Grange et al) and field level: psychology
-(Alessandorni et al), Spinal Cord injury (Torres-Espin et al) and
-neuroimaging (Niso et al). All of these share in common the need for an
+different organizational levels. These range from lab level
+[@Turoman2022], center level [@Bush2022; @Network2023], multi-center
+level [@ManyPrimates2021; @Network2023] and field level: psychology
+[@Alessandroni2022], spinal cord injury [@TorresEspin2021] and
+neuroimaging [@Niso2022]. All of these share in common the need for an
 infrastructure that promotes open science and open collaboration via
@@
 
-For center-level only one paper was identified (Bush et al), providing
+For center-level only one paper was identified [@Bush2022], providing
 the example of a center of neuroimaging describing first how they
@@
 Interestingly, the level of organization with most papers is the
-multi-center level with two papers from ManyPrimates et al (ManyPrimates
-2019 and ManyPrimates 2021) and Grange et al. In this organization level
-the most urgent needs are: 1) identifying the needs for open
-collaboration and 2) creating an infrastructure that allows those needs
-to be satisfied. Indeed, Grange et al describes a systematic review as
-an exploration of the needs for 11 UKRN centers to implement open
-collaborative practives. In this paper they specially focus on tools and
-resources among the 11 institutions and make clear the need for starting
-to utilize open resources as a first step to adapt open collaborative
-practices. The first paper from ManyPrimates et al \[REF\] describes the
-start of another multi-center collaboration, albeit from different
-institutions. It is interesting to observe that in this situation, the
-complex issue is to start the collaboration itself, which was ignited
-thanks to a symposium and an email chain among future collaborators. In
-contrast, ManyPrimates could quickly develop an open collaborative
-structure with relative ease in comparison to changing an already solid
-infrastructure, like in the case of Grange et al.
+multi-center level with two papers from ManyPrimates [@ManyPrimates2021;
+@Primates2019] and one from the Reproducibility Network [@Network2023].
+In this organization level the most urgent needs are: 1) identifying the
+needs for open collaboration and 2) creating an infrastructure that
+allows those needs to be satisfied. Indeed, the Reproducibility Network
+[@Network2023] describes a systematic review as an exploration of the
+needs for 11 UKRN centers to implement open collaborative practives. In
+this paper they specially focus on tools and resources among the 11
+institutions and make clear the need for starting to utilize open
+resources as a first step to adapt open collaborative practices. The
+first paper from ManyPrimates [@Primates2019] describes the start of
+another multi-center collaboration, albeit from different institutions.
+It is interesting to observe that in this situation, the complex issue
+is to start the collaboration itself, which was ignited thanks to a
+symposium and an email chain among future collaborators. In contrast,
+ManyPrimates could quickly develop an open collaborative structure with
+relative ease in comparison to changing an already solid infrastructure,
+like in the case of @Network2023.
 

### 2025-02-10 doc/paper.qmd

@@
 knitr::opts_chunk$set(echo = FALSE)
+library(targets)
+library(readr)
+library(dplyr)
+library(glue)
 library(stringr)
@@
 source(here("R/openalex-search.R"))
-search_terms_inline <- glue::glue("({search_terms()$title_search}[title]) AND {search_terms()$general_search}")
-reviewed_records <- targets::tar_read(reviewed_article_records)
+search_terms_inline <- glue("({search_terms()$title_search}[title]) AND {search_terms()$general_search}")
+reviewed_records <- tar_read(reviewed_article_records)
 
 list_refs <- bib2df::bib2df(here("doc/reviewed-records.bib")) |>
-  dplyr::filter(CATEGORY != "COMMENT") |>
-  glue::glue_data("@{BIBTEXKEY}") |>
+  filter(CATEGORY != "COMMENT") |>
+  glue_data("@{BIBTEXKEY}") |>
   str_c(collapse = ";") |>
@@
 
-We found `r nrow(reviewed_records)` source documents discussing open
-collaboration in some way. These were `r list_refs`. Two of the
-documents, while passed our abstract review, did not contain anything
-relevant when we reviewed the full text [@Network2023a; @Yordanov2022],
-so we did not continue with charting them.
+```{r}
+#| echo: false
+n_papers <- tar_read(records_title_only) |>
+  nrow()
 
-### Practices of open collaboration
+n_papers_title_review <- tar_read(records_after_title_exclusion) |>
+  nrow()
 
-Across the papers found in our literature search, X out of 11 discuss
-actual experiences on implementing open collaboration, albeit in
-different organizational levels. These range from lab level
-[@Turoman2022], center level [@Bush2022; @Network2023], multi-center
-level [@ManyPrimates2021; @Network2023] and field level: psychology
-[@Alessandroni2022], spinal cord injury [@TorresEspin2021] and
-neuroimaging [@Niso2022]. All of these share in common the need for an
-infrastructure that promotes open science and open collaboration via
-starting building a community of collaborators or making tools (usually
-online resources) that researchers can use to reach FAIR (Finndable,
-Accessible, Interoperable and Reusable) goals while doing research.
-Before delving in those, here we provide the specific needs for
-implementing open collaboration in each organizational level, as well as
-describing the differences in approaches among experiences between and
-across levels (Figure 2).
+n_papers_excluded_title_review <- n_papers - n_papers_title_review
 
-#### Implementation of open collaboration practices at laboratory level
+n_titles_selected <- tar_read(titles_selected) |>
+  nrow()
 
-#### Implementation of open collaboration practices at center level
+n_paper_full_text <- tar_read(abstracts_selected) |>
+  nrow()
 
-For center-level only one paper was identified [@Bush2022], providing
-the example of a center of neuroimaging describing first how they
-identified the needs for open collaboration, then the individual-level
-practices that researchers should adapt and then the center-level
-changes to promote reaching FAIR goals.
+n_papers_selected_for_review <- read_csv(here("data", "article_characteristics.csv")) |>
+  nrow()
 
-#### Implementation of open collaboration practices at multi-center level
+# get table of study characteristics
+article_characteristics <- read_csv(here("data", "article_characteristics.csv"))
 
-Interestingly, the level of organization with most papers is the
-multi-center level with two papers from ManyPrimates [@ManyPrimates2021;
-@Primates2019] and one from the Reproducibility Network [@Network2023].
-In this organization level the most urgent needs are: 1) identifying the
+n_guides <- article_characteristics |>
+  filter(paper_type == "guide") |>
+  nrow()
+
+n_examples <- article_characteristics |>
+  filter(paper_type == "example") |>
+  nrow()
+
+n_surveys <- article_characteristics |>
+  filter(paper_type == "survey") |>
+  nrow()
+
+n_org <- article_characteristics |>
+  filter(str_detect(themes, "organization")) |>
+  nrow()
+
+n_tools <- article_characteristics |>
+  filter(str_detect(themes, "tools")) |>
+  nrow()
+
+n_education <- article_characteristics |>
+  filter(str_detect(themes, "education")) |>
+  nrow()
+
+n_researcher <- article_characteristics |>
+  filter(relevant_for == "researcher") |>
+  nrow()
+
+n_research_group <- article_characteristics |>
+  filter(relevant_for == "research group") |>
+  nrow()
+
+n_research_center <- article_characteristics |>
+  filter(relevant_for == "research center") |>
+  nrow()
+
+n_research_centers <- article_characteristics |>
+  filter(relevant_for == "multiple centers") |>
+  nrow()
+
+n_research_field <- article_characteristics |>
+  filter(relevant_for == "research field") |>
+  nrow()
+```
+
+Our search yielded a total of `r n_papers` papers from which we filtered
+`r n_papers_excluded_title_review` based on key words. Three reviewers
+independently screened for the remaining `r n_papers_title_review`
+titles from which we screened `r n_titles_selected` abstracts. Of these,
+we assessed `r n_paper_full_text` full-text papers and we included
+`r n_papers_selected_for_review` in the scoping review. These were
+`r list_refs`. Two of the documents, while they passed our abstract
+review, did not contain anything relevant when we reviewed the full text
+[@Network2023a; @Yordanov2022], so we did not continue with charting
+them.
+
+The identified papers included `r n_guides` guides, `r n_examples`
+examples and `r n_surveys` surveys.
+
+`r n_org` of the `r n_papers_selected_for_review` papers included
+recommendations for organizational practices to improve open
+collaboration, `r n_tools` mentioned specific tools used for open
+collaboration and `r n_education` highlighted educational needs. The
+identified papers discussed open collaboration on different
+organizational levels. `r n_researcher` were mostly directed at the
+individual researcher, `r n_research_group` at a research group,
+`r n_research_center` at a research center, `r n_research_centers` at
+several research centers and `r n_research_field` at entire research
+fields.
+
+### Organizational practices of open collaboration
+
+A common theme across organizational levels was the need for
+infrastructure that promotes open collaboration, building a community of
+collaborators and using online tools in accordance with the FAIR
+(Findable, Accessible, Interoperable and Reusable) principles.
+
+individual level - add text
+
+laboratory/research group level - add text
+
+For center-level one paper described how they transitioned their
+neuroimaging research center toward more open and collaborative
+practices. Their central focus was on creating more open code and data
+to improve open collaboration [@Bush2022]. First, they used open-source
+code, then standardized data formats, developed analysis pipelines,
+shared data openly and developed protocols for data documentation. While
+the organizational transition to improve open collaboration was
+described, little was mentioned about how this has improved
+collaborative work at the research center.
+
+Interestingly, the level of organization with most papers was the
+multi-center level with two papers from ManyPrimates [@Primates2019;
+@ManyPrimates2021] and the Reproducibility Network [@Network2023]. In
+this organization level the most urgent needs are: 1) identifying the
 needs for open collaboration and 2) creating an infrastructure that
-allows those needs to be satisfied. Indeed, the Reproducibility Network
-[@Network2023] describes a systematic review as an exploration of the
-needs for 11 UKRN centers to implement open collaborative practives. In
-this paper they specially focus on tools and resources among the 11
-institutions and make clear the need for starting to utilize open
-resources as a first step to adapt open collaborative practices. The
-first paper from ManyPrimates [@Primates2019] describes the start of
-another multi-center collaboration, albeit from different institutions.
-It is interesting to observe that in this situation, the complex issue
-is to start the collaboration itself, which was ignited thanks to a
-symposium and an email chain among future collaborators. In contrast,
-ManyPrimates could quickly develop an open collaborative structure with
-relative ease in comparison to changing an already solid infrastructure,
-like in the case of @Network2023.
+allows those needs to be satisfied. Indeed, Grange et al describes a
+systematic review as an exploration of the needs for 11 UKRN centers to
+implement open collaborative practives. In this paper they specially
+focus on tools and resources among the 11 institutions and make clear
+the need for starting to utilize open resources as a first step to adapt
+open collaborative practices. The first paper from ManyPrimates
+[@Primates2019] describes the start of another multi-center
+collaboration, albeit from different institutions. It is interesting to
+observe that in this situation, the complex issue is to start the
+collaboration itself, which was ignited thanks to a symposium and an
+email chain among future collaborators. In contrast, ManyPrimates could
+quickly develop an open collaborative structure with relative ease in
+comparison to changing an already solid infrastructure, like in the case
+of @Network2023.
 
-#### Implementation of open collaboration practices at field level
+research field level
+
+Here, we provide the specific needs for implementing open collaboration
+in each organizational level, as well as describing the differences in
+approaches among experiences between and across levels (Figure 2).
 

### 2025-02-10 doc/paper.qmd
style: :lipstick: use a nicer looking PDF format (#117)
Closes #108

Doesn't need a review.

--- 2025-02-10 doc/paper.qmd
@@
   html: default
-  typst:
+  academic-typst:
+    section-numbering: "1.1.1"
     columns: 2
@@
   - html
-  - format: typst
+  - format: academic-typst
     text: PDF
     icon: file-pdf
+abstract: |
+  {{< lipsum 1 >}}
+execute: 
+  echo: false
+  message: false
+  warning: false
 ---

### 2025-02-11 doc/protocol.qmd

--- 2025-01-08 doc/protocol.qmd
@@
   - name: Daniel B. Ibsen
+    orcid: "0000-0002-7038-4770"
     affiliations: 
@@
   - name: Luke W. Johnston
+    orcid: "0000-0003-4169-2616"
     affiliations: 
@@
     country: Denmark
+    url: "https://www.ku.dk/"
 doi: 10.17605/OSF.IO/K9DR5

### 2025-02-11 doc/charting/index.qmd

@@
     Center's Transition to Open and Reproducible Science
--   [Alessandroni-2022](Allessandroni-2022.qmd): Ten strategies to
-    foster open science in psychology and beyond
+-   [Alessandroni-2022](Alessandroni-2022.qmd): Ten strategies to foster
+    open science in psychology and beyond
 -   [Dora-2024](Dora-2024.qmd): Accelerating addiction research via Open
@@
     cognition research
--   [Scholler-2019](Scholler-2019.qmd): Ten simple rules for helping
+-   [Sholler-2019](Sholler-2019.qmd): Ten simple rules for helping
     newcomers become contributors to open projects

### 2025-02-11 doc/instructions/index.qmd
style: :art: small formatting fixes

@@
 title: Instructions
+format:
+  html:
+    tbl-colwidths: [2, 10, 18, 3, 67]
 ---
@@
 
-| section | subsection | item | description |
-|:---|:---|:---|:---|
-| Title | Title | 1 | Identify the report as a scoping review. |
-| Abstract | Structured summary | 2 | Provide a structured summary that includes (as applicable): background, objectives, eligibility criteria, sources of evidence, charting methods, results, and conclusions that relate to the review questions and objectives.
+::: column-body-outset
+| Status | Section | Subsection | Item | Description |
+|:--------------|:--------------|:--------------|:--------------|:--------------|
+| :white_check_mark: | Title | Title | 1 | Identify the report as a scoping review. |
+| :construction: | Abstract | Structured summary | 2 | Provide a structured summary that includes (as applicable): background, objectives, eligibility criteria, sources of evidence, charting methods, results, and conclusions that relate to the review questions and objectives.
 |
-| Introduction | Rationale | 3 | Describe the rationale for the review in the context of what is already known.
+| :construction: | Introduction | Rationale | 3 | Describe the rationale for the review in the context of what is already known.
 Explain why the review questions/objectives lend themselves to a scoping review approach.
 |
-| Introduction | Objectives | 4 | Provide an explicit statement of the questions and objectives being addressed with reference to their key elements (e.g., population or participants, concepts, and context) or other relevant key elements used to conceptualize the review questions and/or objectives.
+| :construction: | Introduction | Objectives | 4 | Provide an explicit statement of the questions and objectives being addressed with reference to their key elements (e.g., population or participants, concepts, and context) or other relevant key elements used to conceptualize the review questions and/or objectives.
 |
-| Methods | Protocol and registration | 5 | Indicate whether a review protocol exists; state if and where it can be accessed (e.g., a Web address); and if available, provide registration information, including the registration number.
+| :construction: | Methods | Protocol and registration | 5 | Indicate whether a review protocol exists; state if and where it can be accessed (e.g., a Web address); and if available, provide registration information, including the registration number.
 |
-| Methods | Eligibility criteria | 6 | Specify characteristics of the sources of evidence used as eligibility criteria (e.g., years considered, language, and publication status), and provide a rationale.
+| :construction: | Methods | Eligibility criteria | 6 | Specify characteristics of the sources of evidence used as eligibility criteria (e.g., years considered, language, and publication status), and provide a rationale.
 |
-| Methods | Information sources\* | 7 | Describe all information sources in the search (e.g., databases with dates of coverage and contact with authors to identify additional sources), as well as the date the most recent search was executed.
+| :construction: | Methods | Information sources | 7 | Describe all information sources in the search (e.g., databases with dates of coverage and contact with authors to identify additional sources), as well as the date the most recent search was executed.
 |
-| Methods | Search | 8 | Present the full electronic search strategy for at least 1 database, including any limits used, such that it could be repeated. |
-| Methods | Selection of sources of evidence† | 9 | State the process for selecting sources of evidence (i.e., screening and eligibility) included in the scoping review. |
-| Methods | Data charting process‡ | 10 | Describe the methods of charting data from the included sources of evidence (e.g., calibrated forms or forms that have been tested by the team before their use, and whether data charting was done independently or in duplicate) and any processes for obtaining and confirming data from investigators.
+| :construction: | Methods | Search | 8 | Present the full electronic search strategy for at least 1 database, including any limits used, such that it could be repeated. |
+| :construction: | Methods | Selection of sources of evidence | 9 | State the process for selecting sources of evidence (i.e., screening and eligibility) included in the scoping review. |
+| :construction: | Methods | Data charting process | 10 | Describe the methods of charting data from the included sources of evidence (e.g., calibrated forms or forms that have been tested by the team before their use, and whether data charting was done independently or in duplicate) and any processes for obtaining and confirming data from investigators.
 |
-| Methods | Data items | 11 | List and define all variables for which data were sought and any assumptions and simplifications made. |
-| Methods | Critical appraisal of individual sources of evidence§ | 12 | If done, provide a rationale for conducting a critical appraisal of included sources of evidence; describe the methods used and how this information was used in any data synthesis (if appropriate).
+| :construction: | Methods | Data items | 11 | List and define all variables for which data were sought and any assumptions and simplifications made. |
+| :construction: | Methods | Critical appraisal of individual sources of evidence | 12 | If done, provide a rationale for conducting a critical appraisal of included sources of evidence; describe the methods used and how this information was used in any data synthesis (if appropriate).
 |
-| Methods | Synthesis of results | 13 | Describe the methods of handling and summarizing the data that were charted. |
-| Results | Selection of sources of evidence | 14 | Give numbers of sources of evidence screened, assessed for eligibility, and included in the review, with reasons for exclusions at each stage, ideally using a flow diagram.
+| :construction: | Methods | Synthesis of results | 13 | Describe the methods of handling and summarizing the data that were charted. |
+| :construction: | Results | Selection of sources of evidence | 14 | Give numbers of sources of evidence screened, assessed for eligibility, and included in the review, with reasons for exclusions at each stage, ideally using a flow diagram.
 |
-| Results | Characteristics of sources of evidence | 15 | For each source of evidence, present characteristics for which data were charted and provide the citations. |
-| Results | Critical appraisal within sources of evidence | 16 | If done, present data on critical appraisal of included sources of evidence (see item 12). |
-| Results | Results of individual sources of evidence | 17 | For each included source of evidence, present the relevant data that were charted that relate to the review questions and objectives. |
-| Results | Synthesis of results | 18 | Summarize and/or present the charting results as they relate to the review questions and objectives. |
-| Discussion | Summary of evidence | 19 | Summarize the main results (including an overview of concepts, themes, and types of evidence available), link to the review questions and objectives, and consider the relevance to key groups.
+| :construction: | Results | Characteristics of sources of evidence | 15 | For each source of evidence, present characteristics for which data were charted and provide the citations. |
+| :construction: | Results | Critical appraisal within sources of evidence | 16 | If done, present data on critical appraisal of included sources of evidence (see item 12). |
+| :construction: | Results | Results of individual sources of evidence | 17 | For each included source of evidence, present the relevant data that were charted that relate to the review questions and objectives.
 |
-| Discussion | Limitations | 20 | Discuss the limitations of the scoping review process. |
-| Discussion | Conclusions | 21 | Provide a general interpretation of the results with respect to the review questions and objectives, as well as potential implications and/or next steps. |
-| Funding | Funding | 22 | Describe sources of funding for the included sources of evidence, as well as sources of funding for the scoping review.
+| :construction: | Results | Synthesis of results | 18 | Summarize and/or present the charting results as they relate to the review questions and objectives. |
+| :construction: | Discussion | Summary of evidence | 19 | Summarize the main results (including an overview of concepts, themes, and types of evidence available), link to the review questions and objectives, and consider the relevance to key groups.
+|
+| :construction: | Discussion | Limitations | 20 | Discuss the limitations of the scoping review process. |
+| :construction: | Discussion | Conclusions | 21 | Provide a general interpretation of the results with respect to the review questions and objectives, as well as potential implications and/or next steps.
+|
+| :construction: | Funding | Funding | 22 | Describe sources of funding for the included sources of evidence, as well as sources of funding for the scoping review.
 Describe the role of the funders of the scoping review.
 |
+:::

### 2025-02-11 doc/paper.qmd

--- 2025-02-10 doc/paper.qmd
@@
 
+In Turoman et al the authors describe in detail how the have set up a laboratory whose members collaborate in an open way from study design to dissemination.
+Here we highlight the role of group meetings as opportunities to propose ideas and have an initial study design proposed.
+These group meetings are usually started with a section of interesting mistakes, which allows to share the issues, troubleshoot and make the laboratory members comfortable with the fact that errors are unavoidable in science.
+The feedback from these meetings might lead to updates to a lab manual, which is a great tool for new members to start engaging with the open practices of the lab.
+This coupled with a support system by senior members of the laboratory allows, in theory, to ease the learning curve of new members to adapt to open practices and collaboration.
+
+In the paper, authors describe their implementation of open practices in each step of the scientific production.
+Here we focus on the aspects in pre-registration, data analysis and dissemination that improve collaboration between memebers of the labortory and of the same field.
+For pre-registration they combine slack channels and Trello to communicate between members and OSF for data reposition and uploading pre-registered studies.
+They put special emphasis on folder structure, which is consistent for all projects, and assigning the authorship in this stage.
+For data analysis, the authors highlight the figure of the data partner, a member of the laboratory not originally included in the analyses that runs the analyses described in the pre-registered study independently.
+If the results mismatch with the original ones meetings with the lead analyst or all collaborators are organized to assess what the issue might be.
+Additionally, this allows for insights that might result in deviations of the original pre-registered study, which should be included and noted in the final manuscript.
+Importantly, the role of the data partner is described in the final manuscript.
+Finally, in the dissemination step, they highlight that they might incorporate feedback from presenting their analyses in conferences, which are often included as additional non-preregistered analyses.
+
+Finally, in the paper they also highlight relevant open practices that might not enhance collaboration, but that we consider interesting reviewing too.
+First, during pre-registration, they allow for papers to contain defined confirmatory and exploratory sections to avoid the usual rigidness of pre-registered studies.
+Second, in exploratory analyses they included soundness checks whenever possible.
+Third, the perform sequential hypothesis testing to assess within the limits of a maximum sample size which hypothesis fits the data better without induling in p-hacking.
+Finally, they collaborate with schools and with universities to disemminate their results.
+
 #### Implementation of open collaboration practices at center level

### 2025-02-11 doc/paper.qmd
docs: :memo: revised introduction based on feedback from Mario

--- 2025-02-11 doc/paper.qmd
@@
 meaningful progress in their field is long gone. Scientific research in
-the modern era, especially in certain fields, almost requires working
-with other people, oftentimes a large number of people. Research
-questions are increasingly more challenging to answer as they require
-more time, resources, expertise, and personnel in order to meaningfully
-answer.
+the modern era, especially in certain fields, requires working with
+other people, oftentimes a large number of people [@Forscher2022].
+Research questions are increasingly more challenging to answer as they
+require more time, resources, expertise, and personnel in order to
+meaningfully answer them.
 
-With the current needs and limitations such as resources when doing
-scientific research, collaborations range from those within a single
-group or lab, to a few researchers across different departments in the
-same institution, to many researchers and personnel spread across
-multiple research centers. Collaborations are needed to address basic
-limitations of working with small or constrained populations, to sharing
-valuable but expensive equipment, or to assisting with technical
-expertise or domain knowledge.
+With the current needs and limitations when doing scientific research,
+collaborations range from those within a single group or lab, to a few
+researchers across different departments in the same institution, to
+many researchers and personnel spread across multiple research centers.
+Collaborations are needed to address basic limitations of working with
+small or constrained populations, to sharing valuable but expensive
+equipment, or to assisting with technical expertise or domain knowledge.
 
 At the same time, there is also a higher need for science to be more
-open, higher quality, and more rigorous[@Cole2024, @Umbach2024], which
-necessitates that researchers collaborate with more researchers and with
-a more diverse group of researchers to fulfill these needs. Open
-scientific practices, such as open data, open source, and open
-materials, aim to improve the reliability and accessibility of
+open, higher quality, and more rigorous [@Cole2024; @Umbach2024;
+@Korbmacher2023], which necessitates that researchers collaborate with
+more researchers and with a more diverse group of researchers to fulfill
+these needs. Open scientific practices, such as open data, open source,
+and open materials, aim to improve the reliability and accessibility of
 scientific output to increase the societal impact of the results.
+There's greater attention and scrutiny towards verification of results,
+a core tenet of science, through replication and reproducibility. In
+many ways, the "replication crisis" in science has been a driving force
+behind the push for more open science and "team science" practices that
+necessitate more collaboration [@Korbmacher2023].
 
-There are many hypothetical benefits to openness in science, including
-in collaboration. For instance:
+There are many claimed benefits to openness in science, including in
+collaboration [@Forscher2022; @Kavanagh2021]. For instance:
 
@@
 From our own personal experience working in the field of health
-research, we have varied and diverse ways of collaborating. Often the
-most commonly used approach to collaboration is emailing Word documents
-around to get feedback and using meetings to discuss and agree on
-things. Rarely do we systematically examine whether we are following
-best practices for collaboration nor do we collaborate in an open way
-following the principles of open science. This lack of a clear standard
-or approach to collaborating effectively and openly can greatly impact
-productivity and quality of scientific research. It emphasizes a greater
-need for a paradigm shift in how we researchers collaborate to be able
-to effectively and efficiently tackle the challenges of the modern era.
+research, we have varied and diverse ways of collaborating and of being
+open. Often the most commonly used approach to collaboration is emailing
+Word documents around to get feedback and using meetings to discuss and
+agree on things. Rarely do we systematically examine whether we are
+following best practices for collaboration nor do we collaborate in an
+open way following the principles of open science. As for open science,
+while it was first introduced in 1985 [@Chubin1985] and discussed in
+academic outputs regularly since then, the actual practices of being
+open in science have been minimal or largely confined to specific
+sub-branches of openness like open access.
 
-For this scoping review, we define open collaboration using the
-definition as found in [@Forte2013]:
+This lack of visible role-models or standards of practice for
+effectively collaborating and actively working openly presents a clear
+barrier to uptake of these practices. This has real consequences to
+continued productivity and quality of scientific research, which is
+increasingly apparent in the modern era. These consequences are even
+more apparent when comparing to more technically-inclined communities
+such as those in open source software. These communities have massively
+benefitted from integrating more openness into their workflows, to the
+extent that the vast majority of the world's digital infrastructure is
+built on and runs open source software. This highlights a greater need
+for a paradigm shift in how we researchers collaborate to be able to
+effectively and efficiently tackle the challenges of the modern era.
 
-> "*an online environment that (a) supports the collective production of
-> an artifact (b) through a technologically mediated collaboration
-> platform (c) that presents a low barrier to entry and exit and (d)
-> supports the emergence of persistent but malleable social
-> structures.*"
-
-Open collaboration has a lot of potential benefits, many of which are
-the same benefits as seen with open science. For instance, open
-collaboration can lead to:
+Open collaboration has many potential benefits, of which most overlap
+with the benefits of open science. For instance, open collaboration can
+lead to:
 
@@
 examples of how to integrate open science into collaborations and how to
-make collaboration be open.
+make collaboration be open [@Korbmacher2023].
 
@@
 
-This scoping review will focus on current practices of open
-collaboration and open science in relation to collaboration in the field
-of biomedical and health research.
+Our aim is to conduct a scoping review to provide an overview of current
+practices of open collaboration in the academic world. For this scoping
+review, we define open collaboration using the definition as found in
+[@Forte2013]:
+
+> "*an online environment that (a) supports the collective production of
+> an artifact (b) through a technologically mediated collaboration
+> platform (c) that presents a low barrier to entry and exit and (d)
+> supports the emergence of persistent but malleable social
+> structures.*"
 

### 2025-02-11 doc/paper.qmd
docs: :memo: add a draft abstract (not results and conclusion)
Closes #95

--- 2025-02-11 doc/paper.qmd
@@
 abstract: |
-  {{< lipsum 1 >}}
+  **Background**: Greater, more extensive collaboration is increasingly needed
+  in the modern research environment, often to the level of team-based science.
+  Combined with this need is the emphasize on doing more open science. However,
+  there seems to be less attention on the overlap between open science and
+  collaboration.
+
+  **Objectives**: To conduct a scoping review on open collaborative practices used 
+  across academia, including methods, tools, and resources.
+
+  **Eligibility criteria**: We included any document that discussed, in any way,
+  open collaboration practices, only those in English, and only those that were
+  open access. We searched 5 years from whenever we ran a search.
+
+  **Sources of evidence**: We used the OpenAlex database to search for scholarly
+  works, which includes a large number of sources. Our search period was
+  between 2019-02-28 to 2024-02-29.
+
+  **Charting methods**: All three authors participated in the search, extraction,
+  and charting process. As no standard charting form exists for our purposes,
+  we developed our own template.
+
+  **Results**: TBD
+
+  **Conclusions**: TBD
 execute: 
@@
 
-In Turoman et al the authors describe in detail how the have set up a laboratory whose members collaborate in an open way from study design to dissemination.
-Here we highlight the role of group meetings as opportunities to propose ideas and have an initial study design proposed.
-These group meetings are usually started with a section of interesting mistakes, which allows to share the issues, troubleshoot and make the laboratory members comfortable with the fact that errors are unavoidable in science.
-The feedback from these meetings might lead to updates to a lab manual, which is a great tool for new members to start engaging with the open practices of the lab.
-This coupled with a support system by senior members of the laboratory allows, in theory, to ease the learning curve of new members to adapt to open practices and collaboration.
-
-In the paper, authors describe their implementation of open practices in each step of the scientific production.
-Here we focus on the aspects in pre-registration, data analysis and dissemination that improve collaboration between memebers of the labortory and of the same field.
-For pre-registration they combine slack channels and Trello to communicate between members and OSF for data reposition and uploading pre-registered studies.
-They put special emphasis on folder structure, which is consistent for all projects, and assigning the authorship in this stage.
-For data analysis, the authors highlight the figure of the data partner, a member of the laboratory not originally included in the analyses that runs the analyses described in the pre-registered study independently.
-If the results mismatch with the original ones meetings with the lead analyst or all collaborators are organized to assess what the issue might be.
-Additionally, this allows for insights that might result in deviations of the original pre-registered study, which should be included and noted in the final manuscript.
-Importantly, the role of the data partner is described in the final manuscript.
-Finally, in the dissemination step, they highlight that they might incorporate feedback from presenting their analyses in conferences, which are often included as additional non-preregistered analyses.
-
-Finally, in the paper they also highlight relevant open practices that might not enhance collaboration, but that we consider interesting reviewing too.
-First, during pre-registration, they allow for papers to contain defined confirmatory and exploratory sections to avoid the usual rigidness of pre-registered studies.
-Second, in exploratory analyses they included soundness checks whenever possible.
-Third, the perform sequential hypothesis testing to assess within the limits of a maximum sample size which hypothesis fits the data better without induling in p-hacking.
-Finally, they collaborate with schools and with universities to disemminate their results.
-
 #### Implementation of open collaboration practices at center level

### 2025-02-11 doc/instructions/index.qmd

@@
 | :white_check_mark: | Title | Title | 1 | Identify the report as a scoping review. |
-| :construction: | Abstract | Structured summary | 2 | Provide a structured summary that includes (as applicable): background, objectives, eligibility criteria, sources of evidence, charting methods, results, and conclusions that relate to the review questions and objectives.
+| :white_check_mark: | Abstract | Structured summary | 2 | Provide a structured summary that includes (as applicable): background, objectives, eligibility criteria, sources of evidence, charting methods, results, and conclusions that relate to the review questions and objectives.
 |

### 2025-03-18 doc/paper.qmd
docs: :memo: add a draft abstract (not results and conclusion) (#119)
Closes #95

Started a draft of the abstract, following the PRISMA guidelines.

--- 2025-02-11 doc/paper.qmd
@@
 
-## Introduction
+## Background
 
@@
 
-### Aim
+### Objectives
 

### 2025-03-18 doc/paper.qmd
style: :art: small edits, plus reformat Markdown

@@
 online resources, but it was very difficult to programmatically and
-systemtically achieve this. So we ended up only searching for scholarly
+systematically achieve this. So we ended up only searching for scholarly
 work that were indexed in databases.
@@
 starting building a community of collaborators or making tools (usually
-online resources) that researchers can use to reach FAIR (Finndable,
+online resources) that researchers can use to reach FAIR (Findable,
 Accessible, Interoperable and Reusable) goals while doing research.
@@
 
-In Turoman et al the authors describe in detail how the have set up a laboratory whose members collaborate in an open way from study design to dissemination.
-Here we highlight the role of group meetings as opportunities to propose ideas and have an initial study design proposed.
-These group meetings are usually started with a section of interesting mistakes, which allows to share the issues, troubleshoot and make the laboratory members comfortable with the fact that errors are unavoidable in science.
-The feedback from these meetings might lead to updates to a lab manual, which is a great tool for new members to start engaging with the open practices of the lab.
-This coupled with a support system by senior members of the laboratory allows, in theory, to ease the learning curve of new members to adapt to open practices and collaboration.
+In @Turoman2022 the authors describe in detail how the have set up a
+laboratory whose members collaborate in an open way from study design to
+dissemination. Here we highlight the role of group meetings as
+opportunities to propose ideas and have an initial study design
+proposed. These group meetings are usually started with a section of
+interesting mistakes, which allows to share the issues, troubleshoot and
+make the laboratory members comfortable with the fact that errors are
+unavoidable in science. The feedback from these meetings might lead to
+updates to a lab manual, which is a great tool for new members to start
+engaging with the open practices of the lab. This coupled with a support
+system by senior members of the laboratory allows, in theory, to ease
+the learning curve of new members to adapt to open practices and
+collaboration.
 
-In the paper, authors describe their implementation of open practices in each step of the scientific production.
-Here we focus on the aspects in pre-registration, data analysis and dissemination that improve collaboration between memebers of the labortory and of the same field.
-For pre-registration they combine slack channels and Trello to communicate between members and OSF for data reposition and uploading pre-registered studies.
-They put special emphasis on folder structure, which is consistent for all projects, and assigning the authorship in this stage.
-For data analysis, the authors highlight the figure of the data partner, a member of the laboratory not originally included in the analyses that runs the analyses described in the pre-registered study independently.
-If the results mismatch with the original ones meetings with the lead analyst or all collaborators are organized to assess what the issue might be.
-Additionally, this allows for insights that might result in deviations of the original pre-registered study, which should be included and noted in the final manuscript.
-Importantly, the role of the data partner is described in the final manuscript.
-Finally, in the dissemination step, they highlight that they might incorporate feedback from presenting their analyses in conferences, which are often included as additional non-preregistered analyses.
+In the paper, authors describe their implementation of open practices in
+each step of the scientific production. Here we focus on the aspects in
+pre-registration, data analysis and dissemination that improve
+collaboration between members of the laboratory and of the same field.
+For pre-registration they combine slack channels and Trello to
+communicate between members and OSF for data deposition and uploading
+pre-registered studies. They put special emphasis on folder structure,
+which is consistent for all projects, and assigning the authorship in
+this stage. For data analysis, the authors highlight the figure of the
+data partner, a member of the laboratory not originally included in the
+analyses that runs the analyses described in the pre-registered study
+independently. If the results mismatch with the original ones meetings
+with the lead analyst or all collaborators are organized to assess what
+the issue might be. Additionally, this allows for insights that might
+result in deviations of the original pre-registered study, which should
+be included and noted in the final manuscript. Importantly, the role of
+the data partner is described in the final manuscript. Finally, in the
+dissemination step, they highlight that they might incorporate feedback
+from presenting their analyses in conferences, which are often included
+as additional non-preregistered analyses.
 
-Finally, in the paper they also highlight relevant open practices that might not enhance collaboration, but that we consider interesting reviewing too.
-First, during pre-registration, they allow for papers to contain defined confirmatory and exploratory sections to avoid the usual rigidness of pre-registered studies.
-Second, in exploratory analyses they included soundness checks whenever possible.
-Third, the perform sequential hypothesis testing to assess within the limits of a maximum sample size which hypothesis fits the data better without induling in p-hacking.
-Finally, they collaborate with schools and with universities to disemminate their results.
+Finally, in the paper they also highlight relevant open practices that
+might not enhance collaboration, but that we consider interesting
+reviewing too. First, during pre-registration, they allow for papers to
+contain defined confirmatory and exploratory sections to avoid the usual
+rigidness of pre-registered studies. Second, in exploratory analyses
+they included soundness checks whenever possible. Third, the perform
+sequential hypothesis testing to assess within the limits of a maximum
+sample size which hypothesis fits the data better without indulging in
+p-hacking. Finally, they collaborate with schools and with universities
+to disseminate their results.
 
@@
 [@Network2023] describes a systematic review as an exploration of the
-needs for 11 UKRN centers to implement open collaborative practives. In
+needs for 11 UKRN centers to implement open collaborative practices. In
 this paper they specially focus on tools and resources among the 11

### 2025-03-18 doc/paper.qmd
Write results section - laboratory-level practices (#118)
Added implementation of open collaboration practices at laboratory level

---------

Co-authored-by: Luke W. Johnston <lwjohnst@gmail.com>

@@
 
-In @Turoman2022 the authors describe in detail how the have set up a
-laboratory whose members collaborate in an open way from study design to
-dissemination. Here we highlight the role of group meetings as
-opportunities to propose ideas and have an initial study design
-proposed. These group meetings are usually started with a section of
-interesting mistakes, which allows to share the issues, troubleshoot and
-make the laboratory members comfortable with the fact that errors are
-unavoidable in science. The feedback from these meetings might lead to
-updates to a lab manual, which is a great tool for new members to start
-engaging with the open practices of the lab. This coupled with a support
-system by senior members of the laboratory allows, in theory, to ease
-the learning curve of new members to adapt to open practices and
-collaboration.
+In @Turoman2022, the authors describe in detail how they set up a
+laboratory where members collaborate in an open way, from study design
+to dissemination. Here we highlight the role of group meetings as
+opportunities to propose ideas and discuss an initial study design.
+These group meetings usually start with some time to reflect on and
+discuss interesting mistakes, which allows members to share the issues
+and potential troubleshoot the problems. This helps make the laboratory
+members feel more comfortable with experiencing and managing errors, as
+they are unavoidable in science. The feedback from these meetings might
+lead to updating a lab manual, which is a great tool for new members to
+start engaging with the open practices of the lab. This, coupled with a
+support system by senior laboratory members allows, at least in theory,
+a smoother on-boarding experience for new members to adapt to open
+practices and collaboration.
 
-In the paper, authors describe their implementation of open practices in
-each step of the scientific production. Here we focus on the aspects in
-pre-registration, data analysis and dissemination that improve
+In they paper they describe how they implement open practices in each
+step of the scientific production. We will focus on the aspects on
+pre-registration, data analysis, and dissemination that improve
 collaboration between members of the laboratory and of the same field.
-For pre-registration they combine slack channels and Trello to
-communicate between members and OSF for data deposition and uploading
+For pre-registration they combine Slack channels and Trello to
+communicate within the group and use OSF to deposit data and upload
 pre-registered studies. They put special emphasis on folder structure,
-which is consistent for all projects, and assigning the authorship in
-this stage. For data analysis, the authors highlight the figure of the
-data partner, a member of the laboratory not originally included in the
-analyses that runs the analyses described in the pre-registered study
-independently. If the results mismatch with the original ones meetings
-with the lead analyst or all collaborators are organized to assess what
-the issue might be. Additionally, this allows for insights that might
-result in deviations of the original pre-registered study, which should
-be included and noted in the final manuscript. Importantly, the role of
-the data partner is described in the final manuscript. Finally, in the
-dissemination step, they highlight that they might incorporate feedback
-from presenting their analyses in conferences, which are often included
-as additional non-preregistered analyses.
+which is consistent for all projects, and assigning the authorship at
+this stage. For data analysis, they incorporate a "data partner" role,
+who is a member of the laboratory not originally included in the study.
+This data partner independently runs the analyses described in the
+pre-registered study. If there is a mismatch in results with the
+original results, meetings with the lead analyst or all collaborators
+are organized to assess what the issue might be. This allows for
+insights that may result in deviations in the original pre-registered
+study, which should be included and noted in the final manuscript. The
+role of the data partner is, importantly, included and described in the
+final manuscript. In the final dissemination step, they highlight that
+they may incorporate feedback given after presenting their analyses in
+conferences, which are often included as additional non-preregistered
+analyses.
 
-Finally, in the paper they also highlight relevant open practices that
-might not enhance collaboration, but that we consider interesting
-reviewing too. First, during pre-registration, they allow for papers to
+The group also highlights that relevant open practices may not always
+enhance collaboration, but have other benefits that we want to also
+highlight. First, during pre-registration, they allow for papers to
 contain defined confirmatory and exploratory sections to avoid the usual
 rigidness of pre-registered studies. Second, in exploratory analyses
-they included soundness checks whenever possible. Third, the perform
+they included soundness checks whenever possible. Third, they perform
 sequential hypothesis testing to assess within the limits of a maximum

### 2025-03-18 doc/paper.qmd
chore: :wrench: add Mario's ORCID

--- 2025-03-18 doc/paper.qmd
@@
   - name: Mario Garcia
+    orcid: "0000-0002-3376-9460"
     affiliations:
@@
     country: Denmark
+    url: "https://www.ku.dk/"
 format:
   html: default
-  academic-typst:
-    section-numbering: "1.1.1"
+  typst:
     columns: 2
@@
   - html
-  - format: academic-typst
+  - format: typst
     text: PDF
     icon: file-pdf
-abstract: |
-  **Background**: Greater, more extensive collaboration is increasingly needed
-  in the modern research environment, often to the level of team-based science.
-  Combined with this need is the emphasize on doing more open science. However,
-  there seems to be less attention on the overlap between open science and
-  collaboration.
-
-  **Objectives**: To conduct a scoping review on open collaborative practices used 
-  across academia, including methods, tools, and resources.
-
-  **Eligibility criteria**: We included any document that discussed, in any way,
-  open collaboration practices, only those in English, and only those that were
-  open access. We searched 5 years from whenever we ran a search.
-
-  **Sources of evidence**: We used the OpenAlex database to search for scholarly
-  works, which includes a large number of sources. Our search period was
-  between 2019-02-28 to 2024-02-29.
-
-  **Charting methods**: All three authors participated in the search, extraction,
-  and charting process. As no standard charting form exists for our purposes,
-  we developed our own template.
-
-  **Results**: TBD
-
-  **Conclusions**: TBD
-execute: 
-  echo: false
-  message: false
-  warning: false
 ---
@@
 search_terms_inline <- glue::glue("({search_terms()$title_search}[title]) AND {search_terms()$general_search}")
-reviewed_records <- targets::tar_read(reviewed_article_records)
-
-list_refs <- bib2df::bib2df(here("doc/reviewed-records.bib")) |>
-  dplyr::filter(CATEGORY != "COMMENT") |>
-  glue::glue_data("@{BIBTEXKEY}") |>
-  str_c(collapse = ";") |>
-  append("[", 0) |>
-  append("]") |>
-  str_c(collapse = "")
 ```
 
-## Background
+## Introduction
 
-The time when a single scientist could work alone in a lab and make
-meaningful progress in their field is long gone. Scientific research in
-the modern era, especially in certain fields, requires working with
-other people, oftentimes a large number of people [@Forscher2022].
-Research questions are increasingly more challenging to answer as they
-require more time, resources, expertise, and personnel in order to
-meaningfully answer them.
+-   Open science and its role in research
 
-With the current needs and limitations when doing scientific research,
-collaborations range from those within a single group or lab, to a few
-researchers across different departments in the same institution, to
-many researchers and personnel spread across multiple research centers.
-Collaborations are needed to address basic limitations of working with
-small or constrained populations, to sharing valuable but expensive
-equipment, or to assisting with technical expertise or domain knowledge.
+-   Collaboration and its role in modern research
 
-At the same time, there is also a higher need for science to be more
-open, higher quality, and more rigorous [@Cole2024; @Umbach2024;
-@Korbmacher2023], which necessitates that researchers collaborate with
-more researchers and with a more diverse group of researchers to fulfill
-these needs. Open scientific practices, such as open data, open source,
-and open materials, aim to improve the reliability and accessibility of
-scientific output to increase the societal impact of the results.
-There's greater attention and scrutiny towards verification of results,
-a core tenet of science, through replication and reproducibility. In
-many ways, the "replication crisis" in science has been a driving force
-behind the push for more open science and "team science" practices that
-necessitate more collaboration [@Korbmacher2023].
+    -   collaboration spanning from lab, to research center to multiple
+        centers
+    -   collaboration needed to tackle limitations: small populations,
+        lack of replication, etc
+    -   re-inventing discovery: a new way of working in science
 
-There are many claimed benefits to openness in science, including in
-collaboration [@Forscher2022; @Kavanagh2021]. For instance:
+Scientific research now almost always requires working with other
+people.
 
--   Greater transparency and accountability, because the built-in
-    openness makes it easy to see what was done, how, and why.
--   Better reproducibility and inspectability, because everything can be
-    easily viewed and can be verified, which is a key tenet of science.
+With the growing complexity and specialization in scientific practices
+and methods, together with globalisation of health and environmental
+issues, there is a great need for a paradigm shift in research
+collaboration to be able to tackle these challenges.
 
-The intersection between greater collaboration and more openness
-highlights key challenges researchers face. How can we effectively
-collaborate together in a way that fulfills the demand for more
-openness, transparency, and accountability, while at the same time also
-not substantially impacting our productivity (or ideally improving it).
-How can we collaborate in an open and transparent way? What are the best
-practices and tools we can use? What is an ideal collaborative workflow
-and how close or how far are we from this ideal in reality?
+-   Open collaboration - a combination of two themes
 
-From our own personal experience working in the field of health
-research, we have varied and diverse ways of collaborating and of being
-open. Often the most commonly used approach to collaboration is emailing
-Word documents around to get feedback and using meetings to discuss and
-agree on things. Rarely do we systematically examine whether we are
-following best practices for collaboration nor do we collaborate in an
-open way following the principles of open science. As for open science,
-while it was first introduced in 1985 [@Chubin1985] and discussed in
-academic outputs regularly since then, the actual practices of being
-open in science have been minimal or largely confined to specific
-sub-branches of openness like open access.
+    -   definition
+    -   big potential in science
+    -   but there very few resources and examples of how to integrate
+        open science into collaborations
 
-This lack of visible role-models or standards of practice for
-effectively collaborating and actively working openly presents a clear
-barrier to uptake of these practices. This has real consequences to
-continued productivity and quality of scientific research, which is
-increasingly apparent in the modern era. These consequences are even
-more apparent when comparing to more technically-inclined communities
-such as those in open source software. These communities have massively
-benefitted from integrating more openness into their workflows, to the
-extent that the vast majority of the world's digital infrastructure is
-built on and runs open source software. This highlights a greater need
-for a paradigm shift in how we researchers collaborate to be able to
-effectively and efficiently tackle the challenges of the modern era.
-
-Open collaboration has many potential benefits, of which most overlap
-with the benefits of open science. For instance, open collaboration can
-lead to:
-
--   Easier onboarding of new collaborators, since everything is open and
-    easily findable.
--   Higher collaboration opportunities, because more openness means more
-    visibility as more parts of the scientific workflow are
-    disseminated.
--   Faster time to dissemination, because the built-in openness makes it
-    easier to disseminate results.
-
-Unfortunately, there are, to our knowledge, very few resources and
-examples of how to integrate open science into collaborations and how to
-make collaboration be open [@Korbmacher2023].
-
-### Objectives
-
-Our aim is to conduct a scoping review to provide an overview of current
-practices of open collaboration in the academic world. For this scoping
-review, we define open collaboration using the definition as found in
+We define open collaboration using the definition as found in
 [@Forte2013]:
@@
 
+With the increasing emphasis on and demand for science to be more open,
+how we collaborate together is a key component to making science more
+open from the start of any project. But how do we collaborate in an open
+and transparent way? What are the best practices and tools we can use?
+What is an ideal collaborative workflow and how close or far are we from
+this ideal in reality?
+
+### Aim
+
+This scoping review will focus on current practices of open
+collaboration and open science in relation to collaboration in the field
+of biomedical and health research.
+
 The specific aims of this scoping review are to:
 
-1.  Provide an overview of current practices of or opinions about
+-   Provide an overview of current practices of or opinions about
     research collaboration that follow basic open principles (e.g.,
@@
 
-2.  Summarize existing online tools and resources available to improve
+-   Summarize existing online tools and resources available to improve
     open collaboration in research
@@
 This is a scoping review, so we followed the framework described in
-[@Arksey2005; @Levac2010] as well as the guidelines outlined in the
+[@Arksey2005, @Levac2010] as well as the guidelines outlined in the
 PRISMA-ScR statement [@Tricco2018].
@@
 search results is kept in the
-[`R/exclusions.R`](https://github.com/science-collective/scoping-review/blob/main/R/exclusions.R)
+[`R/exlusions.R`](https://github.com/science-collective/scoping-review/blob/main/R/exclusions.R)
 file on the GitHub repository. For example, we extracted a large number
@@
 
-We found `r nrow(reviewed_records)` source documents discussing open
-collaboration in some way. These were `r list_refs`. Two of the
-documents, while passed our abstract review, did not contain anything
-relevant when we reviewed the full text [@Network2023a; @Yordanov2022],
-so we did not continue with charting them.
+### Scoping review identifies only 11 papers discussing open collaboration
 
@@
 actual experiences on implementing open collaboration, albeit in
-different organizational levels. These range from lab level
-[@Turoman2022], center level [@Bush2022; @Network2023], multi-center
-level [@ManyPrimates2021; @Network2023] and field level: psychology
-[@Alessandroni2022], spinal cord injury [@TorresEspin2021] and
-neuroimaging [@Niso2022]. All of these share in common the need for an
+different organizational levels. These range from lab level (Turoman et
+al) center level (Bush et al and Grange et al), multi-center level
+(ManyPrimates et al and Grange et al) and field level: psychology
+(Alessandorni et al), Spinal Cord injury (Torres-Espin et al) and
+neuroimaging (Niso et al). All of these share in common the need for an
 infrastructure that promotes open science and open collaboration via
@@
 
-In Turoman et al the authors describe in detail how the have set up a laboratory whose members collaborate in an open way from study design to dissemination.
-Here we highlight the role of group meetings as opportunities to propose ideas and have an initial study design proposed.
-These group meetings are usually started with a section of interesting mistakes, which allows to share the issues, troubleshoot and make the laboratory members comfortable with the fact that errors are unavoidable in science.
-The feedback from these meetings might lead to updates to a lab manual, which is a great tool for new members to start engaging with the open practices of the lab.
-This coupled with a support system by senior members of the laboratory allows, in theory, to ease the learning curve of new members to adapt to open practices and collaboration.
-
-In the paper, authors describe their implementation of open practices in each step of the scientific production.
-Here we focus on the aspects in pre-registration, data analysis and dissemination that improve collaboration between memebers of the labortory and of the same field.
-For pre-registration they combine slack channels and Trello to communicate between members and OSF for data reposition and uploading pre-registered studies.
-They put special emphasis on folder structure, which is consistent for all projects, and assigning the authorship in this stage.
-For data analysis, the authors highlight the figure of the data partner, a member of the laboratory not originally included in the analyses that runs the analyses described in the pre-registered study independently.
-If the results mismatch with the original ones meetings with the lead analyst or all collaborators are organized to assess what the issue might be.
-Additionally, this allows for insights that might result in deviations of the original pre-registered study, which should be included and noted in the final manuscript.
-Importantly, the role of the data partner is described in the final manuscript.
-Finally, in the dissemination step, they highlight that they might incorporate feedback from presenting their analyses in conferences, which are often included as additional non-preregistered analyses.
-
-Finally, in the paper they also highlight relevant open practices that might not enhance collaboration, but that we consider interesting reviewing too.
-First, during pre-registration, they allow for papers to contain defined confirmatory and exploratory sections to avoid the usual rigidness of pre-registered studies.
-Second, in exploratory analyses they included soundness checks whenever possible.
-Third, the perform sequential hypothesis testing to assess within the limits of a maximum sample size which hypothesis fits the data better without induling in p-hacking.
-Finally, they collaborate with schools and with universities to disemminate their results.
-
 #### Implementation of open collaboration practices at center level
 
-For center-level only one paper was identified [@Bush2022], providing
+For center-level only one paper was identified (Bush et al), providing
 the example of a center of neuroimaging describing first how they
@@
 Interestingly, the level of organization with most papers is the
-multi-center level with two papers from ManyPrimates [@ManyPrimates2021;
-@Primates2019] and one from the Reproducibility Network [@Network2023].
-In this organization level the most urgent needs are: 1) identifying the
-needs for open collaboration and 2) creating an infrastructure that
-allows those needs to be satisfied. Indeed, the Reproducibility Network
-[@Network2023] describes a systematic review as an exploration of the
-needs for 11 UKRN centers to implement open collaborative practives. In
-this paper they specially focus on tools and resources among the 11
-institutions and make clear the need for starting to utilize open
-resources as a first step to adapt open collaborative practices. The
-first paper from ManyPrimates [@Primates2019] describes the start of
-another multi-center collaboration, albeit from different institutions.
-It is interesting to observe that in this situation, the complex issue
-is to start the collaboration itself, which was ignited thanks to a
-symposium and an email chain among future collaborators. In contrast,
-ManyPrimates could quickly develop an open collaborative structure with
-relative ease in comparison to changing an already solid infrastructure,
-like in the case of @Network2023.
+multi-center level with two papers from ManyPrimates et al (ManyPrimates
+2019 and ManyPrimates 2021) and Grange et al. In this organization level
+the most urgent needs are: 1) identifying the needs for open
+collaboration and 2) creating an infrastructure that allows those needs
+to be satisfied. Indeed, Grange et al describes a systematic review as
+an exploration of the needs for 11 UKRN centers to implement open
+collaborative practives. In this paper they specially focus on tools and
+resources among the 11 institutions and make clear the need for starting
+to utilize open resources as a first step to adapt open collaborative
+practices. The first paper from ManyPrimates et al \[REF\] describes the
+start of another multi-center collaboration, albeit from different
+institutions. It is interesting to observe that in this situation, the
+complex issue is to start the collaboration itself, which was ignited
+thanks to a symposium and an email chain among future collaborators. In
+contrast, ManyPrimates could quickly develop an open collaborative
+structure with relative ease in comparison to changing an already solid
+infrastructure, like in the case of Grange et al.
 

### 2025-03-18 doc/protocol.qmd
chore: :wrench: add ORCID and affiliation URLs (#114)
Closes #109, closes #110

@@
   - name: Mario Garcia
+    orcid: "0000-0002-3376-9460"
     affiliations: 
